---
title: "Create Codebooks for the Deidentifed Versions of Data"
html:
  embed-resources: true
format: html
---

# ⭐️ Overview

## This File

This file creates codebooks for the de-identified version of the APS, MedStar, and Record Linkage data sets.

# 📥 Load

## Packages

## Library Imports

```{r, warning = FALSE}
suppressPackageStartupMessages({
  library(tidyverse)
  library(here)
  library(codebookr)
})
```

### Versioning

This file was created with:

-   R version 4.4.1 ("Race for Your Life").
-   tidyverse version 2.0.0, including all attached packages
-   here version 1.0.1
-   codebookr version 0.1.8

## Functions

```{r}
#| label: imports-functions
# Function to reduce code repetition in informative imports of data
source(here::here("r", "informative_df_import.R"))
# Function to use a CSV to add column attributes for Codebookr
source(here::here("r", "cb_add_col_attributes_from_csv_file.R"))
```

# Create Codebooks

## MedStar Data

### "Participants.RDS" (Encounter/Record Level, Pre-Cleaned)

We loaded and processed the MedStar Participant data (record level).

```{r}
#| label: codebook-medstar-records
# MedStar Response Records
## Paths
### Data of interest
data_path <- here::here(
  "data", "deidentified", "medstar", "01_medstar_records.rds"
  )

### Codebook Labels (CSV)
labels_path <- here::here(
  "data", "codebook_values", "deidentified_sets", "medstar", 
  "01_medstar_records_labels.csv"
  )
labels_path2 <- labels_path

### Export Path
export_path <- here::here(
  "data", "deidentified", "docs", "codebooks", "medstar", 
  "cb_01_medstar_records.docx"
)

## Process Codebook
### Load Data
informative_df_import(
  "codebook_df", data_path, overwrite = T
  )

### Load Labels
informative_df_import(
  "cb_labels", labels_path, overwrite = T, show_col_types = F
  )

### Order columns to match labels
codebook_df <- codebook_df |>
  dplyr::relocate(cb_labels$variable)

### Label Data
codebook_df <- cb_add_column_attributes_from_csv_file(
  df = codebook_df,
  attr_csv_path = labels_path2
)

### Generate codebook
codebook_df <- codebookr::codebook(
 df = codebook_df,
 title = paste0(
   "DETECT 5-Year Data: MedStar (EMS) Participant Records, ", 
   "Record-Level, Deidentified"
   ),
 description = paste0(
   "From pre-processing of 'participant_import.csv' file from FileMaker Pro"
   ),
 no_summary_stats = c('x_primary_key')
)

## Export Codebook
print(codebook_df, export_path)
```

### "Participants.RDS" (Subject Level, Pre-Cleaned)

We loaded and processed the MedStar Participant data (subject level).

```{r}
#| label: codebook-medstar-subjects
# MedStar Response Subject Data
## Paths
### Data of interest
data_path <- here::here(
  "data", "deidentified", "medstar", "02_medstar_subjects.rds"
  )

### Codebook Labels (CSV)
labels_path <- here::here(
  "data", "codebook_values", "deidentified_sets", "medstar", 
  "02_medstar_subjects_labels.csv"
  )
labels_path2 <- labels_path

### Export Path
export_path <- here::here(
  "data", "deidentified", "docs", "codebooks", "medstar", 
  "cb_02_medstar_subjects.docx"
)

## Process Codebook
### Load Data
informative_df_import(
  "codebook_df", data_path, overwrite = T
  )

### Load Labels
informative_df_import(
  "cb_labels", labels_path, overwrite = T, show_col_types = F
  )

### Order columns to match labels
codebook_df <- codebook_df |>
  dplyr::relocate(cb_labels$variable)

### Label Data
codebook_df <- cb_add_column_attributes_from_csv_file(
  df = codebook_df,
  attr_csv_path = labels_path2
)

### Generate codebook
codebook_df <- codebookr::codebook(
 df = codebook_df,
 title = paste0(
   "DETECT 5-Year Data: MedStar (EMS) Participant Records, ", 
   "Subject-Level, Deidentified"
   ),
 description = paste0(
   "From pre-processing of 'participant_import.csv' file from",
   " FileMaker Pro, aggregated to subject level"
   ),
 no_summary_stats = c('x_primary_key')
)

## Export Codebook
print(codebook_df, export_path)
```

### "Observational Measures"

We loaded and processed the MedStar Follow-up Interview Observational Measures data.

```{r}
#| label: codebook-medstar-obs
# MedStar Observational Measures
## Paths
### Data of interest
data_path <- here::here(
  "data", "deidentified", "medstar", "03_medstar_observational.rds"
  )

### Codebook Labels (CSV)
labels_path <- here::here(
  "data", "codebook_values", "deidentified_sets", "medstar", 
  "03_medstar_observational_labels.csv"
  )
labels_path2 <- labels_path

### Export Path
export_path <- here::here(
  "data", "deidentified", "docs", "codebooks", "medstar", 
  "cb_03_medstar_observational.docx"
)

## Process Codebook
### Load Data
informative_df_import(
  "codebook_df", data_path, overwrite = T
  )

### Load Labels
informative_df_import(
  "cb_labels", labels_path, overwrite = T, show_col_types = F
  )

### Order columns to match labels
codebook_df <- codebook_df |>
  dplyr::relocate(cb_labels$variable)

### Label Data
codebook_df <- cb_add_column_attributes_from_csv_file(
  df = codebook_df,
  attr_csv_path = labels_path2
)

### Generate codebook
codebook_df <- codebookr::codebook(
 df = codebook_df,
 title = "DETECT 5-Year Data: Follow-Up Interviews: Observational Measures",
 description = paste0(
   "From 'observational_measures_import.csv' file from FileMaker Pro"
   ),
 no_summary_stats = c(
   'x_primary_key', 'at_self_why', 'at_fina_why', 'at_neg_why', 
   'at_emot_why', 'at_sex_why', 'at_phys_why', 'abuse_indicators_comments', 
   'general_assessment_comments', 'summary_comments', 'abandonment_comments', 
   'exploitation_comments', 'neglect_comments'
   )
)

## Export Codebook
print(codebook_df, export_path)
```

### "Sociodemographic Measures"

We loaded and processed the MedStar Follow-up Interview Sociodemographic Data.

```{r}
#| label: codebook-medstar-sdi
# MedStar Follow-Up Interview Sociodemographic Measures
## Paths
### Data of interest
data_path <- here::here(
  "data", "deidentified", "medstar", "04_medstar_sociodemographics.rds"
  )

### Codebook Labels (CSV)
labels_path <- here::here(
  "data", "codebook_values", "deidentified_sets", "medstar", 
  "04_medstar_sociodemographics_labels.csv"
  )
labels_path2 <- labels_path

### Export Path
export_path <- here::here(
  "data", "deidentified", "docs", "codebooks", "medstar", 
  "cb_04_medstar_sociodemographics.docx"
)

## Process Codebook
### Load Data
informative_df_import(
  "codebook_df", data_path, overwrite = T
  )

### Load Labels
informative_df_import(
  "cb_labels", labels_path, overwrite = T, show_col_types = F
  )

### Order columns to match labels
codebook_df <- codebook_df |>
  dplyr::relocate(cb_labels$variable)

### Label Data
codebook_df <- cb_add_column_attributes_from_csv_file(
  df = codebook_df,
  attr_csv_path = labels_path2
)

### Generate codebook
codebook_df <- codebookr::codebook(
 df = codebook_df,
 title = "DETECT 5-Year Data: Follow-Up Interviews: Sociodemographics",
 description = paste0(
   "From 'sociodemographic_information_import.csv' file from FileMaker Pro"
   ),
 no_summary_stats = c('x_primary_key')
)

## Export Codebook
print(codebook_df, export_path)
```

### "General Health"

We loaded and processed the MedStar Follow-up Interview General Health Data.

```{r}
#| label: codebook-medstar-gh
# MedStar Follow-up Interview General Health Measures
## Paths
### Data of interest
data_path <- here::here(
  "data", "deidentified", "medstar", "05_medstar_general_health.rds"
  )

### Codebook Labels (CSV)
labels_path <- here::here(
  "data", "codebook_values", "deidentified_sets", "medstar", 
  "05_medstar_general_health_labels.csv"
  )
labels_path2 <- labels_path

### Export Path
export_path <- here::here(
  "data", "deidentified", "docs", "codebooks", "medstar", 
  "cb_05_medstar_general_health.docx"
)

## Process Codebook
### Load Data
informative_df_import(
  "codebook_df", data_path, overwrite = T
  )

### Load Labels
informative_df_import(
  "cb_labels", labels_path, overwrite = T, show_col_types = F
  )

### Order columns to match labels
codebook_df <- codebook_df |>
  dplyr::relocate(cb_labels$variable)

### Label Data
codebook_df <- cb_add_column_attributes_from_csv_file(
  df = codebook_df,
  attr_csv_path = labels_path2
)

### Generate codebook
codebook_df <- codebookr::codebook(
 df = codebook_df,
 title = "DETECT 5-Year Data: Follow-Up Interviews: General Health Measures",
 description = paste0(
   "From 'general_health_import.csv' file from FileMaker Pro"
   ),
 no_summary_stats = c('x_primary_key')
)

## Export Codebook
print(codebook_df, export_path)
```

### "Self Report"

We loaded and processed the MedStar Follow-up Interview Self Report Data.

```{r}
#| label: codebook-medstar-sr
# MedStar Follow-up Interview Self Report Measures
## Paths
### Data of interest
data_path <- here::here(
  "data", "deidentified", "medstar", "06_medstar_self_report.rds"
  )

### Codebook Labels (CSV)
labels_path <- here::here(
  "data", "codebook_values", "deidentified_sets", "medstar", 
  "06_medstar_self_report_labels.csv"
  )
labels_path2 <- labels_path

### Export Path
export_path <- here::here(
  "data", "deidentified", "docs", "codebooks", "medstar", 
  "cb_06_medstar_self_report.docx"
)

## Process Codebook
### Load Data
informative_df_import(
  "codebook_df", data_path, overwrite = T
  )

### Load Labels
informative_df_import(
  "cb_labels", labels_path, overwrite = T, show_col_types = F
  )

### Order columns to match labels
codebook_df <- codebook_df |>
  dplyr::relocate(cb_labels$variable)

### Label Data
codebook_df <- cb_add_column_attributes_from_csv_file(
  df = codebook_df,
  attr_csv_path = labels_path2
)

### Generate codebook
codebook_df <- codebookr::codebook(
 df = codebook_df,
 title = "DETECT 5-Year Data: Follow-Up Interviews: Self-Report",
 description = paste0(
   "From 'self_report_import.csv' file from FileMaker Pro"
   ),
 no_summary_stats = c('x_primary_key')
)

## Export Codebook
print(codebook_df, export_path)
```

### "LEAD Panel Assessment"

We loaded and processed the MedStar LEAD Panel Assessment Data.

```{r}
#| label: codebook-medstar-lead
# MedStar LEAD Panel Measures
## Paths
### Data of interest
data_path <- here::here(
  "data", "deidentified", "medstar", "07_medstar_lead.rds"
  )

### Codebook Labels (CSV)
labels_path <- here::here(
  "data", "codebook_values", "deidentified_sets", "medstar", 
  "07_medstar_lead_labels.csv"
  )
labels_path2 <- labels_path

### Export Path
export_path <- here::here(
  "data", "deidentified", "docs", "codebooks", "medstar", 
  "cb_07_medstar_lead.docx"
)

## Process Codebook
### Load Data
informative_df_import(
  "codebook_df", data_path, overwrite = T
  )

### Load Labels
informative_df_import(
  "cb_labels", labels_path, overwrite = T, show_col_types = F
  )

### Order columns to match labels
codebook_df <- codebook_df |>
  dplyr::relocate(cb_labels$variable)

### Label Data
codebook_df <- cb_add_column_attributes_from_csv_file(
  df = codebook_df,
  attr_csv_path = labels_path2
)

### Generate codebook
codebook_df <- codebookr::codebook(
 df = codebook_df,
 title = "DETECT 5-Year Data: Lead Panel Assessment",
 description = paste0(
   "From 'lead_panel_assessment_import.csv' file from FileMaker Pro"
   ),
 no_summary_stats = c('x_primary_key')
)

## Export Codebook
print(codebook_df, export_path)
```

## APS Data

### Clients.xlsx

We loaded and processed the APS Client Data.

```{r}
#| label: codebook-aps-clients
# APS Clients.xlsx
## Paths
### Data of interest
data_path <- here::here(
  "data", "deidentified", "aps", "01_aps_clients.rds"
  )

### Codebook Labels (CSV)
labels_path <- here::here(
  "data", "codebook_values", "deidentified_sets", "aps", 
  "01_aps_clients_labels.csv"
  )
labels_path2 <- labels_path

### Export Path
export_path <- here::here(
  "data", "deidentified", "docs", "codebooks", "aps", 
  "cb_01_aps_clients.docx"
)

## Process Codebook
### Load Data
informative_df_import(
  "codebook_df", data_path, overwrite = T
  )

### Load Labels
informative_df_import(
  "cb_labels", labels_path, overwrite = T, show_col_types = F
  )

### Order columns to match labels
codebook_df <- codebook_df |>
  dplyr::relocate(cb_labels$variable)

### Label Data
codebook_df <- cb_add_column_attributes_from_csv_file(
  df = codebook_df,
  attr_csv_path = labels_path2
)

### Generate codebook
codebook_df <- codebookr::codebook(
 df = codebook_df,
 title = "Texas APS: Client Data",
 description = paste0(
   "From pre-processed 'Clients.xlsx' file from Texas APS"
   )
)

## Export Codebook
print(codebook_df, export_path)
```

### Investigations.xlsx

We loaded and processed the APS Investigation Data.

```{r}
#| label: codebook-aps-investigations
# APS Investigations.xlsx
## Paths
### Data of interest
data_path <- here::here(
  "data", "deidentified", "aps", "02_aps_investigations.rds"
  )

### Codebook Labels (CSV)
labels_path <- here::here(
  "data", "codebook_values", "deidentified_sets", "aps", 
  "02_aps_investigations_labels.csv"
  )
labels_path2 <- labels_path

### Export Path
export_path <- here::here(
  "data", "deidentified", "docs", "codebooks", "aps", 
  "cb_02_aps_investigations.docx"
)

## Process Codebook
### Load Data
informative_df_import(
  "codebook_df", data_path, overwrite = T
  )

### Load Labels
informative_df_import(
  "cb_labels", labels_path, overwrite = T, show_col_types = F
  )

### Order columns to match labels
codebook_df <- codebook_df |>
  dplyr::relocate(cb_labels$variable)

### Label Data
codebook_df <- cb_add_column_attributes_from_csv_file(
  df = codebook_df,
  attr_csv_path = labels_path2
)

### Generate codebook
codebook_df <- codebookr::codebook(
 df = codebook_df,
 title = "Texas APS: Investigation Data",
 description = paste0(
   "From 'Investigations.xlsx' file from Texas APS"
   )
)

## Export Codebook
print(codebook_df, export_path)
```

### Allegations.xlsx

We loaded and processed the APS Allegations Data.

```{r}
#| label: codebook-aps-allegs
# APS Allegations.xlsx
## Paths
### Data of interest
data_path <- here::here(
  "data", "deidentified", "aps", "03_aps_allegations.rds"
  )

### Codebook Labels (CSV)
labels_path <- here::here(
  "data", "codebook_values", "deidentified_sets", "aps", 
  "03_aps_allegations_labels.csv"
  )
labels_path2 <- labels_path

### Export Path
export_path <- here::here(
  "data", "deidentified", "docs", "codebooks", "aps", 
  "cb_03_aps_allegations.docx"
)

## Process Codebook
### Load Data
informative_df_import(
  "codebook_df", data_path, overwrite = T
  )

### Load Labels
informative_df_import(
  "cb_labels", labels_path, overwrite = T, show_col_types = F
  )

### Order columns to match labels
codebook_df <- codebook_df |>
  dplyr::relocate(cb_labels$variable)

### Label Data
codebook_df <- cb_add_column_attributes_from_csv_file(
  df = codebook_df,
  attr_csv_path = labels_path2
)

### Generate codebook
codebook_df <- codebookr::codebook(
 df = codebook_df,
 title = "Texas APS: Allegations Data",
 description = paste0(
   "From 'Allegations.xlsx' file from Texas APS"
   )
)

## Export Codebook
print(codebook_df, export_path)
```

### Subsequent Intakes.xlsx

We loaded and processed the APS Intakes Data.

```{r}
#| label: codebook-aps-intakes
# APS Subsequent Intakes.xlsx
## Paths
### Data of interest
data_path <- here::here(
  "data", "deidentified", "aps", "04_aps_intakes.rds"
  )

### Codebook Labels (CSV)
labels_path <- here::here(
  "data", "codebook_values", "deidentified_sets", "aps", 
  "04_aps_intakes_labels.csv"
  )
labels_path2 <- labels_path

### Export Path
export_path <- here::here(
  "data", "deidentified", "docs", "codebooks", "aps", 
  "cb_04_aps_intakes.docx"
)

## Process Codebook
### Load Data
informative_df_import(
  "codebook_df", data_path, overwrite = T
  )

### Load Labels
informative_df_import(
  "cb_labels", labels_path, overwrite = T, show_col_types = F
  )

### Order columns to match labels
codebook_df <- codebook_df |>
  dplyr::relocate(cb_labels$variable)

### Label Data
codebook_df <- cb_add_column_attributes_from_csv_file(
  df = codebook_df,
  attr_csv_path = labels_path2
)

### Generate codebook
codebook_df <- codebookr::codebook(
 df = codebook_df,
 title = "Texas APS: Intakes Data",
 description = paste0(
   "From 'Subsequent Intakes.xlsx' file from Texas APS"
   )
)

## Export Codebook
print(codebook_df, export_path)
```

## Record Linkage Maps

### Subject Linkage

We loaded and processed the Record Linkage Map connecting MedStar Subjects to APS Subjects.

```{r}
#| label: codebook-rec-link-subj
# Record Linkage Map: Subjects
## Paths
### Data of interest
data_path <- here::here(
  "data", "deidentified", "record_linkage", "01_medstar_to_aps-subjs.rds"
  )

### Codebook Labels (CSV)
labels_path <- here::here(
  "data", "codebook_values", "deidentified_sets", "record_linkage", 
  "01_medstar_to_aps-subjs_labels.csv"
  )
labels_path2 <- labels_path

### Export Path
export_path <- here::here(
  "data", "deidentified", "docs", "codebooks", "record_linkage", 
  "cb_01_medstar_to_aps-subjs.docx"
)

## Process Codebook
### Load Data
informative_df_import(
  "codebook_df", data_path, overwrite = T
  )

### Load Labels
informative_df_import(
  "cb_labels", labels_path, overwrite = T, show_col_types = F
  )

### Order columns to match labels
codebook_df <- codebook_df |>
  dplyr::relocate(cb_labels$variable)

### Label Data
codebook_df <- cb_add_column_attributes_from_csv_file(
  df = codebook_df,
  attr_csv_path = labels_path2
)

### Generate codebook
codebook_df <- codebookr::codebook(
 df = codebook_df,
 title = "Record Linkage Map: MedStar Subjects to APS Subjects"
)

## Export Codebook
print(codebook_df, export_path)
```

### Response-Investigation Linkage

We loaded and processed the Record Linkage Map connecting MedStar Subjects to APS Investigations.

```{r}
#| label: codebook-rec-link-invs
# Record Linkage Map: Responses to Investigations
## Paths
### Data of interest
data_path <- here::here(
  "data", "deidentified", "record_linkage", 
  "02_medstar_to_aps-investigation.rds"
  )

### Codebook Labels (CSV)
labels_path <- here::here(
  "data", "codebook_values", "deidentified_sets", "record_linkage", 
  "02_medstar_to_aps-investigation_labels.csv"
  )
labels_path2 <- labels_path

### Export Path
export_path <- here::here(
  "data", "deidentified", "docs", "codebooks", "record_linkage", 
  "cb_02_medstar_to_aps-investigation.docx"
)

## Process Codebook
### Load Data
informative_df_import(
  "codebook_df", data_path, overwrite = T
  )

### Load Labels
informative_df_import(
  "cb_labels", labels_path, overwrite = T, show_col_types = F
  )

### Order columns to match labels
codebook_df <- codebook_df |>
  dplyr::relocate(cb_labels$variable)

### Label Data
codebook_df <- cb_add_column_attributes_from_csv_file(
  df = codebook_df,
  attr_csv_path = labels_path2
)

### Generate codebook
codebook_df <- codebookr::codebook(
 df = codebook_df,
 title = "Record Linkage Map: MedStar Responses to APS Investigations"
)

## Export Codebook
print(codebook_df, export_path)
```

### Response-Intake Linkage

We loaded and processed the Record Linkage Map connecting MedStar Subjects to APS Intakes.

```{r}
#| label: codebook-rec-link-intakes
# Record Linkage Map: Responses to Intakes
## Paths
### Data of interest
data_path <- here::here(
  "data", "deidentified", "record_linkage", 
  "03_medstar_to_aps-intake.rds"
  )

### Codebook Labels (CSV)
labels_path <- here::here(
  "data", "codebook_values", "deidentified_sets", "record_linkage", 
  "03_medstar_to_aps-intake_labels.csv"
  )
labels_path2 <- labels_path

### Export Path
export_path <- here::here(
  "data", "deidentified", "docs", "codebooks", "record_linkage", 
  "cb_03_medstar_to_aps-intake.docx"
)

## Process Codebook
### Load Data
informative_df_import(
  "codebook_df", data_path, overwrite = T
  )

### Load Labels
informative_df_import(
  "cb_labels", labels_path, overwrite = T, show_col_types = F
  )

### Order columns to match labels
codebook_df <- codebook_df |>
  dplyr::relocate(cb_labels$variable)

### Label Data
codebook_df <- cb_add_column_attributes_from_csv_file(
  df = codebook_df,
  attr_csv_path = labels_path2
)

### Generate codebook
codebook_df <- codebookr::codebook(
 df = codebook_df,
 title = "Record Linkage Map: MedStar Responses to APS Intakes"
)

## Export Codebook
print(codebook_df, export_path)
```

# 🧹 Clean up

```{r}
rm(list=ls())
```
