---
title: De-Identify Phone Recruitment Data
author: Rachit Sabharwal
date: 08-23-25
format:
    html
---

# Data Exploration

```{r}
#| label: load libraries and data
#| echo: false
#| output: false
library(here)
library(tidyverse)

raw_data <- read_csv(
    here("data/Phone Recruitment.csv"),
    col_types = cols(
        RecruitmentMethod = col_character(),
        PhoneVerifyNumber = col_character(),
        PhoneVerifyWrongNumber = col_character(),
        PhoneConfirmFollowUp = col_character(),
        AssignedInterviewer = col_character()
    )
)
```

Take a look at the underlying structure of the data

```{r}
#| label: data exploration

str(raw_data)

glimpse(raw_data)
```

# Identify Potential PHI Columns

These include (generally): 

- Columns with names
- Columns with contact information (emails, phone numbers, etc.)
- Columns with addresses
- Columns with dates
- Columns with information that can be linked to identify a single individual

## Date Columns
```{r}
#| label: get all datetime columns

date_cols <- raw_data |>
    select(contains(c("date", "time", "day", "month", "year")))

print(colnames(date_cols))
```

## Name Columns
```{r}
#| label: get all name columns

name_cols <- raw_data |>
    select(contains(c("name", "by", "recruiter", "interviewer")))

print(colnames(name_cols))
```

## Contact Information Columns
```{r}
#| label: get all contact information columns

contact_cols <- raw_data |>
    select(contains(c("mail", "phone")))

print(colnames(contact_cols))
```

## ID Columns
```{r}
#| label: get all id columns

id_cols <- raw_data |>
    select(contains("id"))

print(colnames(id_cols))
```

## Remove Medstar ID Column

Join medstar id with the proxy map generated by Morri found at `01_medstar_01_responses.rds`.

```{r}
#| label: join medstar id

medstar_id_proxy_map <- read_rds(here("data/proxy_maps/01_medstar_01_responses.rds"))

clean_data <- raw_data |>
    rename(medstar_id = MedstarID) |>
    left_join(
        medstar_id_proxy_map[c("medstar_id", "ms_record_num")],
        by = "medstar_id"
    ) |>
    select(-medstar_id)
```

## Name Removal

Remove columns containing names

```{r}
#| label: name removal

name_cols <- name_cols |>
    select(-cMocaOrientationDayName)

clean_data <- clean_data |>
    select(-colnames(name_cols))
```

## Date Compliance

Ensure that temporal data complies with HIPAA Safe Harbor regulation

```{r}
#| label: HIPAA Safe Harbor dates

date_cols <- date_cols |>
    select(-PhoneBetterTime)

safe_harbor_deid <- function(df) {
  df |>
    mutate(
      # Parse dates (mm/dd/yyyy) and keep ONLY the year
      EntryDate              = year(mdy(EntryDate)),
      AppointmentDate        = year(mdy(AppointmentDate)),

      # Parse timestamps and keep ONLY the year
      xCreatedTimestamp      = year(mdy_hms(xCreatedTimestamp, tz = "UTC")),
      xModifiedTimestamp     = year(mdy_hms(xModifiedTimestamp, tz = "UTC")),

      # Remove fine-grained time information
      AppointmentTime        = NA,             # drop
      AppointmentTimeMilitary= NA,             # drop

      # Drop day names and day-of-month; keep only year-level fields
      cMocaOrientationDay       = NA,
      cMocaOrientationDayName   = NA,
      xRecordMonth              = NA,
      cMocaOrientationMonth     = NA,

      # Year fields are already OK
      xRecordYear            = as.integer(xRecordYear),
      cMocaOrientationYear   = as.integer(cMocaOrientationYear)
    )
}

clean_data <- safe_harbor_deid(clean_data)
```

<!--
- Drop records xCreatedBy "mcannell" which were created in 2024
- Drop test records 
- Perform common sense null checks
    - Expand if necessary to ensure quality
- Email sunil asking about codebook for phone recruitment data
!-->

# Save Clean Data

```{r}
#| label: save data

write_csv(clean_data, here("data/Phone Recruitment Cleaned.csv"))
```