---
title: De-Identify Phone Recruitment Data
author: Rachit Sabharwal
date: 08-23-25
format:
    html
---

# Data Exploration

```{r}
#| label: load libraries and data
#| echo: false
#| output: false
library(here)
library(tidyverse)
library(validate)

raw_data <- read_csv(
    here("data/Phone Recruitment.csv"),
    col_types = cols(
        RecruitmentMethod = col_character(),
        PhoneVerifyNumber = col_character(),
        PhoneVerifyWrongNumber = col_character(),
        PhoneConfirmFollowUp = col_character(),
        AssignedInterviewer = col_character()
    )
)
```

Take a look at the underlying structure of the data

```{r}
#| label: data exploration

str(raw_data)

glimpse(raw_data)
```

# Identify Potential PHI Columns

These include (generally): 

- Columns with names
- Columns with contact information (emails, phone numbers, etc.)
- Columns with addresses
- Columns with dates
- Columns with information that can be linked to identify a single individual

## Date Columns
```{r}
#| label: get all datetime columns

date_cols <- raw_data |>
    select(contains(c("date", "time", "day", "month", "year")))

print(colnames(date_cols))
```

## Name Columns
```{r}
#| label: get all name columns

name_cols <- raw_data |>
    select(contains(c("name", "by", "recruiter", "interviewer")))

print(colnames(name_cols))
```

## Contact Information Columns
```{r}
#| label: get all contact information columns

contact_cols <- raw_data |>
    select(contains(c("mail", "phone")))

print(colnames(contact_cols))
```

## ID Columns
```{r}
#| label: get all id columns

id_cols <- raw_data |>
    select(contains("id"))

print(colnames(id_cols))
```

## Remove Medstar ID Column

Join medstar id with the proxy map generated by Morri found at `01_medstar_01_responses.rds`.

```{r}
#| label: join medstar id

medstar_id_proxy_map <- read_rds(here("data/proxy_maps/01_medstar_01_responses.rds"))

clean_data <- raw_data |>
    rename(medstar_id = MedstarID) |>
    left_join(
        medstar_id_proxy_map[c("medstar_id", "ms_record_num")],
        by = "medstar_id"
    ) |>
    select(-medstar_id)
```

## Name Removal

Remove columns containing names

```{r}
# Drop unnecessary records

# Drop records xCreatedBy "mcannell"
clean_data <- clean_data |>
    filter(xCreatedBy != "uthouston\\mcannell")

# Drop records with name full "test" or NA
clean_data <- clean_data |>
    filter(!stringr::str_detect(NameFull, "Test"), !is.na(NameFull))
```

```{r}
#| label: name removal

name_cols <- name_cols |>
    select(-cMocaOrientationDayName)

clean_data <- clean_data |>
    select(-colnames(name_cols))
```

## Date Compliance

Ensure that temporal data complies with HIPAA Safe Harbor regulation

```{r}
#| label: HIPAA Safe Harbor dates

date_cols <- date_cols |>
    select(-PhoneBetterTime)

safe_harbor_deid <- function(df) {
  df |>
    mutate(
      # Parse dates (mm/dd/yyyy) and keep ONLY the year
      EntryDate              = year(mdy(EntryDate)),
      AppointmentDate        = year(mdy(AppointmentDate)),

      # Parse timestamps and keep ONLY the year
      xCreatedTimestamp      = year(mdy_hms(xCreatedTimestamp, tz = "UTC")),
      xModifiedTimestamp     = year(mdy_hms(xModifiedTimestamp, tz = "UTC")),

      # Remove fine-grained time information
      AppointmentTime        = NA,             # drop
      AppointmentTimeMilitary= NA,             # drop

      # Drop day names and day-of-month; keep only year-level fields
      cMocaOrientationDay       = NA,
      cMocaOrientationDayName   = NA,
      xRecordMonth              = NA,
      cMocaOrientationMonth     = NA,

      # Year fields are already OK
      xRecordYear            = as.integer(xRecordYear),
      cMocaOrientationYear   = as.integer(cMocaOrientationYear)
    )
}

clean_data <- safe_harbor_deid(clean_data)
```

<!--
- Email sunil asking about codebook for phone recruitment data
!-->

# Tests

## Basic Structural Checks

```{r}
#| label: basic structural checks

rules <- validator(
  # Each record must have a proxy ms_record_num after join
  !is.na(ms_record_num),

  # Key identifiers (like MedstarID originally) should not persist
  !("MedstarID" %in% colnames(.)),

  # Drop records with missing NameFull already handled,
  # but verify again after cleaning
  !is.na(NameFull)
)
```

## Null and Completeness Checks

```{r}
#| label: null and completeness checks

rules <- rules + validator(
  # Record status must be present
  !is.na(xRecordStatus),

  # EntryDate should be converted to year, not missing
  !is.na(EntryDate),

  # AppointmentDate year available if Appointment scheduled
  if (!is.na(AppointmentDate)) AppointmentDate >= 1900
)
```

## Value Domain Checks

```{r}
#| label: value domain checks

rules <- rules + validator(
  # Record status only in defined set
  xRecordStatus %in% c("Incomplete","Unverified","Participant not eligible",
                       "Complete","Other"),

  # PhoneEligibleConsent should be "Yes" or "No" if present
  PhoneEligibleConsent %in% c(NA, "Yes", "No"),

  # RecruitmentMethod constrained to known methods (adjust list as needed)
  RecruitmentMethod %in% c(NA, "Phone", "Postcard", "In-person", "Other")
)
```

## Logical Consistency Checks
```{r}
#| label: logical consistency checks

rules <- rules + validator(
  # If PhoneConfirmFollowUp is "Yes", then PhoneWantFollowUp should also be "Yes"
  !(PhoneConfirmFollowUp == "Yes" & PhoneWantFollowUp != "Yes"),

  # If MocaReady is "Yes", then at least one MoCA test item should be non-missing
  !(MocaReady == "Yes" & is.na(cMocaDigitForward) & is.na(cMocaSerial7) &
    is.na(cMocaSentenceRep) & is.na(cMocaOrientationYear))
)
```

## Numeric Range Checks
```{r}
#| label: numeric range checks

rules <- rules + validator(
  # MoCA component scores typically range 0–5
  cMocaDigitForward >= 0 & cMocaDigitForward <= 5,
  cMocaDigitBackward >= 0 & cMocaDigitBackward <= 5,
  cMocaSerial7 >= 0 & cMocaSerial7 <= 5,
  cMocaOrientation >= 0 & cMocaOrientation <= 6,

  # Total scores (cScore, MDScore) within 0–30
  cScore >= 0 & cScore <= 30,
  MDScore >= 0 & MDScore <= 30
)
```

## De-identification Checks
```{r}
#| label: deidentification checks

rules <- rules + validator(
  # No columns should contain "name", "phone", "recruiter", "interviewer"
  all(!grepl("name|phone|recruiter|interviewer", tolower(colnames(.)))),

  # All date fields reduced to year only
  EntryDate <= lubridate::year(Sys.Date()),
  AppointmentDate <= lubridate::year(Sys.Date()),
  xCreatedTimestamp <= lubridate::year(Sys.Date()),
  xModifiedTimestamp <= lubridate::year(Sys.Date())
)
```

## Report
```{r}
#| label: apply validation rules

out <- confront(clean_data, rules)
validation_results <- summary(out)

knitr::kable(validation_results)
```

```{r}
#| label: validation plot

plot(out)
```

# Save Clean Data

```{r}
#| label: save data

write_csv(clean_data, here("data/Phone Recruitment Cleaned.csv"))
```