---
title: "Data Check: Recruiting Calls"
author: "Brad Cannell"
date: "2025-08-18"
format: 
  html:
    embed-resources: true
---

# Overview

I'm trying to download all of the scheduling call log data. Early in the study, MedStar had their own internal person doing the scheduling for the follow-up interviews, and then logging the call dispositions in FileMaker Pro. Later, we hired a call center, M Davis and Company (MDAC), to do the calls. MDAC sent us csv call logs every month, but I think we uploaded them all into FileMaker Pro too. 

I emailed Sunil about this. Here was his response: "Yes, I remember we were working with MDavis for call center recruitment. Please see attached. If I recall, the data is merged into Phone Recruitment.csv. I've also included the call logs file, but I don't think that has MDavis data in there. Just let me know if this is not what you needed."

I am checking the contents of those files below.

# Load packages

```{r}
#| message: false

library(here)
library(readr)
library(dplyr, warn.conflicts = FALSE)
library(lubridate, warn.conflicts = FALSE)
```

# Import Phone Recruitment.csv

## Get the spec for amending column types

```{r}
spec <- spec_csv(here("data", "filemaker_pro_exports", "Phone Recruitment.csv"))
# spec
```

## Read in the data, amending column types as needed

```{r}
phone_recruitment <- read_csv(
  here("data", "filemaker_pro_exports", "Phone Recruitment.csv"),
  col_types = cols(
    RecruitmentMethod = col_character(),
    PhoneVerifyNumber = col_character(),
    PhoneVerifyWrongNumber = col_character(),
    PhoneConfirmFollowUp = col_character(),
    AssignedInterviewer = col_character()
  )
)

dim(phone_recruitment) # 41202    67
```

# Data management ----

## Parse dates

```{r}
phone_recruitment <- phone_recruitment |> 
  mutate(x_created_timestamp = mdy_hms(xCreatedTimestamp)) |> 
  arrange(x_created_timestamp) |> 
  # Remove the redundant record created time stamp
  select(-xCreatedTimestamp)
```

## Create separate date and time record created columns

```{r}
phone_recruitment <- phone_recruitment |> 
  mutate(
    created_date = as_date(x_created_timestamp),
    created_time = hms::as_hms(x_created_timestamp)
  ) 

dim(phone_recruitment) # 41202    69
```

## Remove rows

There are 3 rows all dated 4/16/24 that need to be removed. These records weren't created when a recruiting call was made. They were created when I was viewing data in FileMaker Pro. We need to remove these rows. Let's check for any other rows in the data created by me.

```{r}
check_brad_rows <- phone_recruitment |> 
  filter(stringr::str_detect(xCreatedBy, "mcannell"))
# check_brad_rows
```

There are other rows completed by me, but they appear to be valid rows based on the values of `xRecordStatus`. So, I will filter by date only.

```{r}
phone_recruitment <- phone_recruitment |> 
  filter(created_date <= "2024-01-01")

dim(phone_recruitment) # 41199    69
```

Are there any other rows that need to be removed?

Remove rows without a record status?

```{r}
no_record_status <- phone_recruitment |> 
  filter(is.na(xRecordStatus))
```

I can't rule out that these were legitimate recruiting calls. I'm leaving them in the data for now.

# EDA

What is the earliest date?

```{r}
min(phone_recruitment$x_created_timestamp) # "2019-08-15 09:48:29 UTC"
```

What is the latest date?
```{r}
max(phone_recruitment$x_created_timestamp) # "2023-05-30 08:22:10 UTC"
```

How many total calls?

```{r}
nrow(phone_recruitment) # 41199
```
