---
title: "Analyses Section 1: Demographics and Associations"
html:
  embed-resources: true
format: html
---

# ⭐️ Overview

## This File

This file performs the initial explorations and analyses of demographics within the MedStar 5-year follow-up data, internally referred to as "Section 1: Demographics and Associations".

## MedStar Data Background

The MedStar records were originally recorded in Filemaker Pro. Processing of this data was extensive and across multiple data files. These files are documented in the [wiki](https://github.com/brad-cannell/detect_fu_interviews_public/wiki).

The primary files of interest for subject-level interest included participant demographic data in the `participant_import.rds` file [created in a separate Quarto file](https://github.com/brad-cannell/detect_fu_interviews_public/blob/main/data_management/data_01_participant_import.qmd), and the original within-set unique subject ID assignment in `participant_unique_ids.rds` file [created in a separate Quarto file](https://github.com/brad-cannell/detect_fu_interviews_public/blob/main/data_management/unique_person_identification/data_02_unique_person_detect_fu_data.qmd).

These files originally contained 92,160 observations of approximately 30 demographic variables. Refinement of unique subject ID assignments in subject-linkage to APS resulted in 41,955 values of `ms_id`.

## Internal Files

This document was created as part of the DETECT project, specifically the merger of APS and MedStar data for analysis using the full follow-up period data. Internal documents relating to these files, which contain PHI, are securely stored on the research group's SharePoint in the [task notes folder](https://uthtmc.sharepoint.com/:f:/r/sites/SPHDETECT-RPC/Shared%20Documents/DETECT%20R01%202018/02%20Shared%20Folders/DETECT%20Follow-up%20Interview%20Data%20Shared/data/notes_documents?csf=1&web=1&e=gLWUzJ).

Notes for the MedStar data are located in the [notes_00_data_medstar.docx](https://uthtmc.sharepoint.com/:w:/r/sites/SPHDETECT-RPC/Shared%20Documents/DETECT%20R01%202018/02%20Shared%20Folders/DETECT%20Follow-up%20Interview%20Data%20Shared/data/notes_documents/notes_00_data_medstar.docx?d=w7367b418df5644fbb3ff5117908f27d9&csf=1&web=1&e=gueXsZ) file.

Please note: as these files contain PHI and proprietary information, they are not publicly available. Links are internal to the research team.

# 📦 Load Packages and Functions

## Library Imports

```{r}
#| label: imports-libraries
#| warning: FALSE
suppressPackageStartupMessages({
  library(tidyverse)
  library(here)
  library(janitor, include.only = "clean_names")
})
```

### Versioning

This file was created with:

-   R version 4.4.1 ("Race for Your Life").
-   tidyverse version 2.0.0, including all attached packages
-   here version 1.0.1
-   janitor version 2.2.0
-   stats version 4.4.1

## Functions

```{r}
#| label: imports-functions
# Function to reduce code repetition in informative imports of data
source(here::here("r", "informative_df_import.R"))

# Function that creates a modified version of table output, allowing
# simplified manual review of unique values in a given column or set of
# columns
source(here::here("r", "get_unique_value_summary.R"))

# Function that creates a text-based, human-legible summary statistic table
# for a numeric column
source(here::here("r", "get_cont_summary.R"))
# Function that wraps "get_cont_summary()" to process multiple groups at once.
source(here::here("r", "get_group_cont_summary.R"))

# Function that creates a text-based, human-legible summary statistic table
# for a categorical column
source(here::here("r", "get_cat_summary.R"))
# Function that wraps "get_cat_summary()" to process multiple groups at once.
source(here::here("r", "get_group_cat_summary.R"))

## Function that performs 2-Category Chi-Square and Fisher Exact and produces
## a human-legible summary table
source(here::here("r", "get_chi_fisher.R"))

## Function that performs 2-category T-Test and Wilcox Rank-Sum test and 
## produces a human-legible summary table
source(here::here("r", "get_twos_num_stats.R"))
```

# 📥 Load Data

## MedStar Data

We loaded our MedStar record-level data.

```{r}
#| label: load-ms-records
# Load MedStar Record Level Data
## Path to data
path <- here::here(
    "data", "cleaned_rds_files", "analysis", 
    "medstar_01_record-lvl.rds"
    )

## Load
informative_df_import(
    "ms_records", path, overwrite = T
  )

 # 2025-03-05: MS RECORDS data imported with 91,700 rows and 126 columns.
 # Data last modified on OneDrive: 2025-03-05 12:27:24 
```

We loaded our MedStar subject-level data.

```{r}
#| label: load-ms-records
# Load MedStar Subject Level Data
## Path to data
path <- here::here(
    "data", "cleaned_rds_files", "analysis", 
    "medstar_02_subj-lvl.rds"
    )

## Load
informative_df_import(
    "ms_subjs", path, overwrite = T
  )

 # 2025-03-05: MS SUBJS data imported with 41,612 rows and 75 columns.
 # Data last modified on OneDrive: 2025-03-05 12:27:24 
```

# Analyses

We set the order we wanted to present Sex, Race, and Hispanic Ethnicity Values in our summary tables.

```{r}
#| label: set-value-orders
# Set order of values when presented in summary table functions
## Sex value order
sex_val_list = list(
    male = 'Male', female = 'Female', uta = 'Unable to Assess', 
    missing = 'Missing (NA)'
    )

## Race value order
race_val_list = list(
  white = "White", black = "Black or African American", asian = "Asian", 
  nhpi = "Native Hawaiian or Other Pacific Islander", 
  aian = "American Indian or Alaska Native", 
  mena = "Middle Eastern or North African", 
  other = "Other Race", multiracial = "Multiracial", missing = "Missing (NA)"
  )

## Hispanic Ethnicity value order
hispanic_val_list = list(
  hispanic = 'Hispanic or Latino', nonhispanic = 'Not Hispanic or Latino', 
  missing = 'Missing (NA)'
  )
```

## Section 1: Demographics and Associations

### Overall Demographics

#### Table 1.1: Response-Level (#sec1-t1-demo-overall-resp)

We wished to examine overall demographics within our data at the response level. We stored this internally as Table 1.1. We performed statistical tests for in comparison with [US Census data for Fort Worth, 2022](https://www.census.gov/quickfacts/fact/table/fortworthcitytexas/POP060210).

```{r}
#| label: sec1-t1-demo-overall-resp-subset
# Take response-level subset for the following analyses
t_df <- ms_records |>
  ## Drop "Duplicate" flagged records
  dplyr::filter(!dup_drop)
```

We briefly examined the screening performance, positive screen counts, and screens with recorded intent to report in this section.

```{r}
#| label: sec1-t1-demo-overall-resp-overview
# Present Screened, Positive Screen, and Report Intent Counts for Section
## Name columns of interest
t_vars <- c('dt_screened', 'dt_positive', 'dt_aps_reported')

## Generate table counting TRUE/FALSE values
count_table <- tibble::tibble(
  ### Start with the variable names 
  var_name = t_vars
  ) |>
  ### Add counts of the True, False, and Missing values
  dplyr::bind_cols(
    t_df |>
      dplyr::select(dplyr::all_of(t_vars)) |>
      #### Convert boolean/logical values to character, so NA is not omitted
      dplyr::mutate(dplyr::across(
        dplyr::everything(), 
        ~dplyr::case_when(
          is.na(.x) ~ "Missing",
          .x ~ "True",
          TRUE ~ "False"
        ))
      ) |>
      #### Get counts of the values into the table
      purrr::map_df(table)
  ) |>
  ### Add a row-wise total
  dplyr::rowwise() |>
  dplyr::mutate(
    total = sum(dplyr::c_across(False:Missing), na.rm = T)
    ) |>
  dplyr::ungroup()

## Present table
count_table
```

##### Age

We calculated summary statistics for calculated age.

```{r}
#| label: sec1-t1-demo-all-resp-age-summ
# Get Summary Statistics for Age, Response-Level
get_cont_summary(t_df$age_calc) |>
  dplyr::rename_at('summary_text', ~'Overall (All Responses)')
```

We used a histogram to broadly examine the distribution of values for age. Values demonstrated a significant left skew, and were not approximately normally distributed

```{r}
#| label: sec1-t1-demo-all-resp-age-hist-f0-1
# Figure 0.1: Distribution of Age, Overall, Response-Level
## Create Histogram
plot <- ggplot2::ggplot(
  t_df, 
  ggplot2::aes(
    x = age_calc, y = ggplot2::after_stat(density),
  )) +
  ggplot2::scale_alpha(guide = "none") +
  ggplot2::geom_histogram(binwidth = 1, position = 'identity') +
  ### Convert y-axis scale to a percent
  ggplot2::scale_y_continuous(labels = scales::percent) +
  ### Labels
  ggplot2::labs(
    title="Distribution of Age, Overall, Response-Level",
    x= "Calculated Age at Encounter (Years)", 
    y = "Frequency (%)") +
  ### Colors
  ggplot2::scale_fill_brewer(palette="Spectral")

## Save plot
ggplot2::ggsave(
  filename = here::here(
    "data", "figs", 
    "f0-1_age-overall-resp-hist.png"
    ),
  plot = plot
  )

## Display plot
plot
```

There was no subset of the US Census that provided age values for those above 65, which would be required for statistical testing.

##### Sex

We calculated summary statistics for sex.

```{r}
#| label: sec1-t1-demo-all-resp-sex-summ
# Get Summary Statistics for Sex, Response-Level
## Calculate summary statistics
obs <- get_cat_summary(
  .df = t_df |>
    dplyr::mutate(
      sex_cat = ifelse(is.na(sex_cat), 'missing', sex_cat)
    ),
  "sex_cat",
  .val_order = sex_val_list
  )

## Display table
obs |>
  dplyr::select(value_name, text)
```

We performed Chi-Square and Fisher's Exact test to compare these values to the US Census Data.

```{r}
#| label: sec1-t1-demo-all-resp-sex-stats
# Chi-Square and Fisher's Exact test, Census Comparison
get_chi_fisher(
  .df = obs |> 
  dplyr::select(value_name, n) |>
  dplyr::filter(value_name != "TOTAL") |>
  ## Add Census Percentages:
  ## Male, Female, UTA, Missing
  dplyr::mutate(
    ## Percentages from US Census: 
    ## (Male, Female, UTA, Missing)
    probs = c(0.512, (1-0.512), 0, 0),
    ## Predicted counts from percentages
    preds = sum(n) * probs),
  .counts_a_var = 'n',
  .counts_b_var = 'preds',
  .probs_b_var = 'probs',
  .value_var = 'value_name',
  .omit_vals = c('Unable to Assess', 'Missing (NA)')
  )
```


##### Race

We calculated summary statistics for race.

```{r}
#| label: sec1-t1-demo-all-resp-race-summ
# Get Summary Statistics for Race, Response-Level
## Calculate summary statistics
obs <- get_cat_summary(
  .df = t_df |>
    dplyr::mutate(
      race_cat = ifelse(is.na(race_cat), 'missing', race_cat)
    ),
  "race_cat",
  .val_order = race_val_list
  )

## Display table
obs |>
  dplyr::select(value_name, text)
```

We performed Chi-Square and Fisher's Exact test to compare these values to the US Census Data.

```{r}
#| label: sec1-t1-demo-all-resp-race-stats
# Chi-Square and Fisher's Exact test, Census Comparison
get_chi_fisher(
  .df = obs |> 
  dplyr::select(value_name, n) |>
  dplyr::filter(value_name != "TOTAL") |>
  ## Add Census Percentages:
  ## White, Black, Asian, NHPI, AIAN, MENA, Other, Multiracial, Missing
  dplyr::mutate(
    ## Percentages from US Census: 
    ## (White, Black, Asian, NHPI, AIAN, MENA, Other, Multiracial, Missing)
    probs = c(0.558, 0.188, 0.049, 0.001, 0.005, 0, 0.113, 0.086, 0),
    ## Predicted counts from percentages
    preds = sum(n) * probs),
  .counts_a_var = 'n',
  .counts_b_var = 'preds',
  .probs_b_var = 'probs',
  .value_var = 'value_name',
  .omit_vals = c('Missing (NA)')
  )
```

Of note, "Middle Eastern or North African" was not provided in Census Data. We performed additional sensitivity testing when combining this category into "Other Race".

```{r}
#| label: sec1-t1-demo-all-resp-race-stats-menaomit
# Chi-Square and Fisher's Exact test, Census Comparison, MENA/Other Combined
get_chi_fisher(
  .df = obs |> 
    dplyr::select(value_name, n) |>
    ## Combine MENA into Other
    dplyr::mutate(
      n = ifelse(
        value_name == "Other Race",
        obs[obs$value_name == "Other Race",]$n + 
          obs[obs$value_name == "Middle Eastern or North African",]$n,
        n
      )
    ) |>
    dplyr::filter(
      !value_name %in% c("TOTAL", "Middle Eastern or North African")
      ) |>
    ## Add Census Percentages:
    ### White, Black, Asian, NHPI, AIAN, MENA/Other, Multiracial, Missing
    dplyr::mutate(
      ### Percentages from US Census: 
      ### (White, Black, Asian, NHPI, AIAN, MENA/Other, Multiracial, Missing)
      probs = c(0.558, 0.188, 0.049, 0.001, 0.005, 0.113, 0.086, 0),
      ### Predicted counts from percentages
      preds = sum(n) * probs
      ),
  .counts_a_var = 'n',
  .counts_b_var = 'preds',
  .probs_b_var = 'probs',
  .value_var = 'value_name',
  .omit_vals = c('Missing (NA)')
  )
```

##### Ethnicity

We calculated summary statistics for ethnicity.

```{r}
#| label: sec1-t1-demo-all-resp-ethn-summ
# Get Summary Statistics for Ethnicity, Response-Level
## Calculate summary statistics
obs <- get_cat_summary(
  .df = t_df |>
    dplyr::mutate(
      hispanic = dplyr::case_when(
        is.na(hispanic) ~ 'missing',
        hispanic ~ 'hispanic',
        !hispanic ~ 'nonhispanic'
      )
    ),
  "hispanic",
  .val_order = hispanic_val_list
  )

## Display table
obs |>
  dplyr::select(value_name, text)
```

We performed Chi-Square and Fisher's Exact test to compare these values to the US Census Data.

```{r}
#| label: sec1-t1-demo-all-resp-ethn-stats
# Chi-Square and Fisher's Exact test, Census Comparison
get_chi_fisher(
  .df = obs |> 
  dplyr::select(value_name, n) |>
  dplyr::filter(value_name != "TOTAL") |>
  ## Add Census Percentages:
  ## Hispanic, Non-Hispanic, Missing
  dplyr::mutate(
    ## Percentages from US Census: 
    ## (Hispanic, Non-Hispanic, Missing)
    probs = c(0.353, (1-0.353), 0),
    ## Predicted counts from percentages
    preds = sum(n) * probs),
  .counts_a_var = 'n',
  .counts_b_var = 'preds',
  .probs_b_var = 'probs',
  .value_var = 'value_name',
  .omit_vals = c('Missing (NA)')
  )
```

#### Table 1.2: Subject-Level (#sec1-t2-demo-overall-subj)

We wished to examine overall demographics within our data at the subject level. We stored this internally as Table 1.2. We performed statistical tests for in comparison with [US Census data for Fort Worth, 2022](https://www.census.gov/quickfacts/fact/table/fortworthcitytexas/POP060210).

```{r}
#| label: sec1-t2-demo-overall-subj-subset
# Take response-level subset for the following analyses
t_df <- ms_subjs
```

We briefly examined the screening performance, positive screen counts, and screens with recorded intent to report in this section.

```{r}
#| label: sec1-t2-demo-overall-subj-overview
# Present Screened, Positive Screen, and Report Intent Counts for Section
## Name columns of interest
t_vars <- c('dt_screened', 'dt_positive', 'dt_aps_reported')

## Generate table counting TRUE/FALSE values
count_table <- tibble::tibble(
  ### Start with the variable names 
  var_name = t_vars
  ) |>
  ### Add counts of the True, False, and Missing values
  dplyr::bind_cols(
    t_df |>
      dplyr::select(dplyr::all_of(t_vars)) |>
      #### Convert boolean/logical values to character, so NA is not omitted
      dplyr::mutate(dplyr::across(
        dplyr::everything(), 
        ~dplyr::case_when(
          is.na(.x) ~ "Missing",
          .x ~ "True",
          TRUE ~ "False"
        ))
      ) |>
      #### Get counts of the values into the table
      purrr::map_df(table)
  ) |>
  ### Add a row-wise total
  dplyr::rowwise() |>
  dplyr::mutate(
    total = sum(dplyr::c_across(False:Missing), na.rm = T)
    ) |>
  dplyr::ungroup()

## Present table
count_table
```

We also calculated summary statistics for the number of responses for each subject.

```{r}
#| label: sec1-t2-demo-overall-subj-numresps
get_cont_summary(t_df$num_resps) |>
  dplyr::rename_at('summary_text', ~'Responses per Subject')
```

##### Age

We calculated summary statistics for calculated age.

```{r}
#| label: sec1-t2-demo-all-subj-age-summ
# Get Summary Statistics for Age, Subject-Level
get_cont_summary(t_df$age_avg) |>
  dplyr::rename_at('summary_text', ~'Overall (All Responses)')
```

We used a histogram to broadly examine the distribution of values for age. Values demonstrated a significant left skew, and were not approximately normally distributed

```{r}
#| label: sec1-t2-demo-all-subj-age-hist-f0-2
# Figure 0.2: Distribution of Age, Overall, Subject-Level
## Create Histogram
plot <- ggplot2::ggplot(
  t_df, 
  ggplot2::aes(
    x = age_avg, y = ggplot2::after_stat(density),
  )) +
  ggplot2::scale_alpha(guide = "none") +
  ggplot2::geom_histogram(binwidth = 1, position = 'identity') +
  ### Convert y-axis scale to a percent
  ggplot2::scale_y_continuous(labels = scales::percent) +
  ### Labels
  ggplot2::labs(
    title="Distribution of Age, Overall, Subject-Level",
    x= "Average Calculated Age at Encounter (Years)", 
    y = "Frequency (%)") +
  ### Colors
  ggplot2::scale_fill_brewer(palette="Spectral")

## Save plot
ggplot2::ggsave(
  filename = here::here(
    "data", "figs", 
    "f0-2_age-overall-subj-hist.png"
    ),
  plot = plot
  )

## Display plot
plot
```

There was no subset of the US Census that provided age values for those above 65, which would be required for statistical testing.

##### Sex

We calculated summary statistics for sex.

```{r}
#| label: sec1-t2-demo-all-subj-sex-summ
# Get Summary Statistics for Sex, Subject-Level
## Calculate summary statistics
obs <- get_cat_summary(
  .df = t_df |>
    dplyr::mutate(
      sex_cat = ifelse(is.na(sex_cat), 'missing', sex_cat)
    ),
  "sex_cat",
  .val_order = sex_val_list
  )

## Display table
obs |>
  dplyr::select(value_name, text)
```

We performed Chi-Square and Fisher's Exact test to compare these values to the US Census Data.

```{r}
#| label: sec1-t2-demo-all-subj-sex-stats
# Chi-Square and Fisher's Exact test, Census Comparison
get_chi_fisher(
  .df = obs |> 
  dplyr::select(value_name, n) |>
  dplyr::filter(value_name != "TOTAL") |>
  ## Add Census Percentages:
  ## Male, Female, UTA, Missing
  dplyr::mutate(
    ## Percentages from US Census: 
    ## (Male, Female, UTA, Missing)
    probs = c(0.512, (1-0.512), 0, 0),
    ## Predicted counts from percentages
    preds = sum(n) * probs),
  .counts_a_var = 'n',
  .counts_b_var = 'preds',
  .probs_b_var = 'probs',
  .value_var = 'value_name',
  .omit_vals = c('Unable to Assess', 'Missing (NA)')
  )
```


##### Race

We calculated summary statistics for race.

```{r}
#| label: sec1-t2-demo-all-subj-race-summ
# Get Summary Statistics for Race, Subject-Level
## Calculate summary statistics
obs <- get_cat_summary(
  .df = t_df |>
    dplyr::mutate(
      race_cat = ifelse(is.na(race_cat), 'missing', race_cat)
    ),
  "race_cat",
  .val_order = race_val_list
  )

## Display table
obs |>
  dplyr::select(value_name, text)
```

We performed Chi-Square and Fisher's Exact test to compare these values to the US Census Data.

```{r}
#| label: sec1-t2-demo-all-subj-race-stats
# Chi-Square and Fisher's Exact test, Census Comparison
get_chi_fisher(
  .df = obs |> 
  dplyr::select(value_name, n) |>
  dplyr::filter(value_name != "TOTAL") |>
  ## Add Census Percentages:
  ## White, Black, Asian, NHPI, AIAN, MENA, Other, Multiracial, Missing
  dplyr::mutate(
    ## Percentages from US Census: 
    ## (White, Black, Asian, NHPI, AIAN, MENA, Other, Multiracial, Missing)
    probs = c(0.558, 0.188, 0.049, 0.001, 0.005, 0, 0.113, 0.086, 0),
    ## Predicted counts from percentages
    preds = sum(n) * probs),
  .counts_a_var = 'n',
  .counts_b_var = 'preds',
  .probs_b_var = 'probs',
  .value_var = 'value_name',
  .omit_vals = c('Missing (NA)')
  )
```

Of note, "Middle Eastern or North African" was not provided in Census Data. We performed additional sensitivity testing when combining this category into "Other Race".

```{r}
#| label: sec1-t2-demo-all-subj-race-stats-menaomit
# Chi-Square and Fisher's Exact test, Census Comparison, MENA/Other Combined
get_chi_fisher(
  .df = obs |> 
    dplyr::select(value_name, n) |>
    ## Combine MENA into Other
    dplyr::mutate(
      n = ifelse(
        value_name == "Other Race",
        obs[obs$value_name == "Other Race",]$n + 
          obs[obs$value_name == "Middle Eastern or North African",]$n,
        n
      )
    ) |>
    dplyr::filter(
      !value_name %in% c("TOTAL", "Middle Eastern or North African")
      ) |>
    ## Add Census Percentages:
    ### White, Black, Asian, NHPI, AIAN, MENA/Other, Multiracial, Missing
    dplyr::mutate(
      ### Percentages from US Census: 
      ### (White, Black, Asian, NHPI, AIAN, MENA/Other, Multiracial, Missing)
      probs = c(0.558, 0.188, 0.049, 0.001, 0.005, 0.113, 0.086, 0),
      ### Predicted counts from percentages
      preds = sum(n) * probs
      ),
  .counts_a_var = 'n',
  .counts_b_var = 'preds',
  .probs_b_var = 'probs',
  .value_var = 'value_name',
  .omit_vals = c('Missing (NA)')
  )
```

##### Ethnicity

We calculated summary statistics for ethnicity.

```{r}
#| label: sec1-t2-demo-all-subj-ethn-summ
# Get Summary Statistics for Ethnicity, Subject-Level
## Calculate summary statistics
obs <- get_cat_summary(
  .df = t_df |>
    dplyr::mutate(
      hispanic = dplyr::case_when(
        is.na(hispanic) ~ 'missing',
        hispanic ~ 'hispanic',
        !hispanic ~ 'nonhispanic'
      )
    ),
  "hispanic",
  .val_order = hispanic_val_list
  )

## Display table
obs |>
  dplyr::select(value_name, text)
```

We performed Chi-Square and Fisher's Exact test to compare these values to the US Census Data.

```{r}
#| label: sec1-t2-demo-all-subj-ethn-stats
# Chi-Square and Fisher's Exact test, Census Comparison
get_chi_fisher(
  .df = obs |> 
  dplyr::select(value_name, n) |>
  dplyr::filter(value_name != "TOTAL") |>
  ## Add Census Percentages:
  ## Hispanic, Non-Hispanic, Missing
  dplyr::mutate(
    ## Percentages from US Census: 
    ## (Hispanic, Non-Hispanic, Missing)
    probs = c(0.353, (1-0.353), 0),
    ## Predicted counts from percentages
    preds = sum(n) * probs),
  .counts_a_var = 'n',
  .counts_b_var = 'preds',
  .probs_b_var = 'probs',
  .value_var = 'value_name',
  .omit_vals = c('Missing (NA)')
  )
```

### By Screening Performance

#### Table 1.3: Response-Level (#sec1-t3-demo-screen-resp)

We wished to examine demographic differences between responses that did and did not receive a DETECT screening. We stored this internally as Table 1.3.

```{r}
#| label: sec1-t3-demo-screen-resp-subset
# Take response-level subset for the following analyses
t_df <- ms_records |>
  ## Drop "Duplicate" flagged records
  dplyr::filter(!dup_drop) |>
  ## Convert grouping variable to text for table functions
  dplyr::mutate(
    dt_screened = dplyr::case_when(
      dt_screened ~ 't',
      !dt_screened ~ 'f'
    )
  )

## Subset-specific group order for tables
t_group_order = list(t = 'Screened', f = 'Not Screened')
```


##### Age

We calculated summary statistics for calculated age.

```{r}
#| label: sec1-t3-demo-screen-resp-age-summ
# Get Summary Statistics for Age by Screening Status, Response-Level
get_group_cont_summary(
  .df = t_df,
  .var_name = "age_calc",
  .group_var = "dt_screened",
  .group_order = t_group_order
  ) 
```

We used a histogram to broadly examine the distribution of values for age. Values demonstrated a significant left skew, and were not approximately normally distributed

```{r}
#| label: sec1-t3-demo-screen-resp-age-hist-f0-3
# Figure 0.3: Distribution of Age by Screening Status, Response-Level
## Create Histogram
plot <- ggplot2::ggplot(
  t_df |>
    dplyr::mutate(
      dt_screened = factor(
        dt_screened, levels = names(t_group_order),
        labels = as.character(t_group_order), ordered = T
        )
    ), 
  ggplot2::aes(
    x = age_calc, fill = dt_screened, y = ggplot2::after_stat(density),
    alpha = 0.5
  )) +
  ggplot2::scale_alpha(guide = "none") +
  ggplot2::geom_histogram(binwidth = 1, position = 'identity') +
  ### Convert y-axis scale to a percent
  ggplot2::scale_y_continuous(labels = scales::percent) +
  ### Labels
  ggplot2::labs(
    title="Distribution of Age by Screening Status, Response-Level",
    x= "Calculated Age at Encounter (Years)", 
    y = "Frequency (%)",
    fill = "Screening Status"
    ) +
  ### Colors
  ggplot2::scale_fill_brewer(palette="Spectral")

## Save plot
ggplot2::ggsave(
  filename = here::here(
    "data", "figs",
    "f0-3_age-screen-resp-hist.png"
    ),
  plot = plot
  )

## Display plot
plot
```

We performed Student T-Test and Wilcox Rank-Sum testing to assess for a statistical association.

```{r}
#| label: sec1-t3-demo-screen-resp-age-stats
# T-Test and Wilcox Rank-Sum for Age, by Screening Status
get_twos_num_stats(
  .df = t_df |>
    dplyr::mutate(
      dt_screened = dplyr::case_when(
        dt_screened == 't' ~ T,
        dt_screened == 'f' ~ F
      )
    ),
  .var_name = 'age_calc',
  .binary_var = 'dt_screened'
)
```

##### Sex

We calculated summary statistics for sex.

```{r}
#| label: sec1-t3-demo-screen-resp-sex-summ
# Get Summary Statistics for Sex, Response-Level
## Calculate summary statistics
obs <- get_group_cat_summary(
  .df = t_df |>
    dplyr::mutate(
      sex_cat = ifelse(is.na(sex_cat), 'missing', sex_cat)
    ),
  "sex_cat",
  .val_order = sex_val_list,
  .group_var = "dt_screened",
  .group_order = t_group_order
  )

## Display Table - Text columns only
obs |>
  dplyr::select(
    !dplyr::all_of(c(dplyr::ends_with("_n"), dplyr::ends_with("_perc")))
    )
```

We performed Chi-Square and Fisher's Exact test to assess for an association.

```{r}
#| label: sec1-t3-demo-screen-resp-sex-stats
# Chi-Square and Fisher's Exact test
get_chi_fisher(
  .df = obs |> 
  dplyr::select(value_name, t_n, f_n) |>
  dplyr::filter(value_name != "TOTAL"),
  .counts_a_var = 't_n',
  .counts_b_var = 'f_n',
  .value_var = 'value_name',
  .omit_vals = c('Unable to Assess', 'Missing (NA)')
  )
```

##### Race

We calculated summary statistics for race.

```{r}
#| label: sec1-t3-demo-screen-resp-race-summ
# Get Summary Statistics for Race, Response-Level
## Calculate summary statistics
obs <- get_group_cat_summary(
  .df = t_df |>
    dplyr::mutate(
      race_cat = ifelse(is.na(race_cat), 'missing', race_cat)
    ),
  "race_cat",
  .val_order = race_val_list,
  .group_var = "dt_screened",
  .group_order = t_group_order
  )

## Display Table - Text columns only
obs |>
  dplyr::select(
    !dplyr::all_of(c(dplyr::ends_with("_n"), dplyr::ends_with("_perc")))
    )
```

We performed Chi-Square and Fisher's Exact test to assess for an association.

```{r}
#| label: sec1-t3-demo-screen-resp-race-stats
# Chi-Square and Fisher's Exact test
get_chi_fisher(
  .df = obs |> 
  dplyr::select(value_name, t_n, f_n) |>
  dplyr::filter(value_name != "TOTAL"),
  .counts_a_var = 't_n',
  .counts_b_var = 'f_n',
  .value_var = 'value_name',
  .omit_vals = c('Missing (NA)')
  )
```


##### Ethnicity

We calculated summary statistics for ethnicity.

```{r}
#| label: sec1-t3-demo-screen-resp-ethn-summ
# Get Summary Statistics for Ethnicity, Response-Level
## Calculate summary statistics
obs <- get_group_cat_summary(
  .df = t_df |>
    dplyr::mutate(
      hispanic = dplyr::case_when(
        is.na(hispanic) ~ 'missing',
        hispanic ~ 'hispanic',
        !hispanic ~ 'nonhispanic'
      )
    ),
  "hispanic",
  .val_order = hispanic_val_list,
  .group_var = "dt_screened",
  .group_order = t_group_order
  )

## Display Table - Text columns only
obs |>
  dplyr::select(
    !dplyr::all_of(c(dplyr::ends_with("_n"), dplyr::ends_with("_perc")))
    )
```

We performed Chi-Square and Fisher's Exact test to assess for an association.

```{r}
#| label: sec1-t3-demo-screen-resp-ethn-stats
# Chi-Square and Fisher's Exact test
get_chi_fisher(
  .df = obs |> 
  dplyr::select(value_name, t_n, f_n) |>
  dplyr::filter(value_name != "TOTAL"),
  .counts_a_var = 't_n',
  .counts_b_var = 'f_n',
  .value_var = 'value_name',
  .omit_vals = c('Missing (NA)')
  )
```

#### Table 1.4: Subject-Level (#sec1-t4-demo-screen-subj)

We wished to examine demographic differences between subjects that did and did not receive a DETECT screening. We stored this internally as Table 1.4.

```{r}
#| label: sec1-t4-demo-screen-subj-subset
# Take response-level subset for the following analyses
t_df <- ms_subjs |>
  ## Convert grouping variable to text for table functions
  dplyr::mutate(
    dt_screened = dplyr::case_when(
      dt_screened ~ 't',
      !dt_screened ~ 'f'
    )
  )

## Subset-specific group order for tables
t_group_order = list(t = 'Screened', f = 'Not Screened')
```


##### Age

We calculated summary statistics for calculated age.

```{r}
#| label: sec1-t4-demo-screen-subj-age-summ
# Get Summary Statistics for Age by Screening Status, Subject-Level
get_group_cont_summary(
  .df = t_df,
  .var_name = "age_avg",
  .group_var = "dt_screened",
  .group_order = t_group_order
  ) 
```

We used a histogram to broadly examine the distribution of values for age. Values demonstrated a significant left skew, and were not approximately normally distributed

```{r}
#| label: sec1-t4-demo-screen-subj-age-hist-f0-4
# Figure 0.4: Distribution of Age by Screening Status, Subject-Level
## Create Histogram
plot <- ggplot2::ggplot(
  t_df |>
    dplyr::mutate(
      dt_screened = factor(
        dt_screened, levels = names(t_group_order),
        labels = as.character(t_group_order), ordered = T
        )
    ), 
  ggplot2::aes(
    x = age_avg, fill = dt_screened, y = ggplot2::after_stat(density),
    alpha = 0.5
  )) +
  ggplot2::scale_alpha(guide = "none") +
  ggplot2::geom_histogram(binwidth = 1, position = 'identity') +
  ### Convert y-axis scale to a percent
  ggplot2::scale_y_continuous(labels = scales::percent) +
  ### Labels
  ggplot2::labs(
    title="Distribution of Age by Screening Status, Subject-Level",
    x= "Average Calculated Age at Encounter (Years)", 
    y = "Frequency (%)",
    fill = "Screening Status"
    ) +
  ### Colors
  ggplot2::scale_fill_brewer(palette="Spectral")

## Save plot
ggplot2::ggsave(
  filename = here::here(
    "data", "figs",
    "f0-4_age-screen-subj-hist.png"
    ),
  plot = plot
  )

## Display plot
plot
```

We performed Student T-Test and Wilcox Rank-Sum testing to assess for a statistical association.

```{r}
#| label: sec1-t4-demo-screen-subj-age-stats
# T-Test and Wilcox Rank-Sum for Age, by Screening Status
get_twos_num_stats(
  .df = t_df |>
    dplyr::mutate(
      dt_screened = dplyr::case_when(
        dt_screened == 't' ~ T,
        dt_screened == 'f' ~ F
      )
    ),
  .var_name = 'age_avg',
  .binary_var = 'dt_screened'
)
```

##### Sex

We calculated summary statistics for sex.

```{r}
#| label: sec1-t4-demo-screen-subj-sex-summ
# Get Summary Statistics for Sex, Subject-Level
## Calculate summary statistics
obs <- get_group_cat_summary(
  .df = t_df |>
    dplyr::mutate(
      sex_cat = ifelse(is.na(sex_cat), 'missing', sex_cat)
    ),
  "sex_cat",
  .val_order = sex_val_list,
  .group_var = "dt_screened",
  .group_order = t_group_order
  )

## Display Table - Text columns only
obs |>
  dplyr::select(
    !dplyr::all_of(c(dplyr::ends_with("_n"), dplyr::ends_with("_perc")))
    )
```

We performed Chi-Square and Fisher's Exact test to assess for an association.

```{r}
#| label: sec1-t4-demo-screen-subj-sex-stats
# Chi-Square and Fisher's Exact test
get_chi_fisher(
  .df = obs |> 
  dplyr::select(value_name, t_n, f_n) |>
  dplyr::filter(value_name != "TOTAL"),
  .counts_a_var = 't_n',
  .counts_b_var = 'f_n',
  .value_var = 'value_name',
  .omit_vals = c('Unable to Assess', 'Missing (NA)')
  )
```

##### Race

We calculated summary statistics for race.

```{r}
#| label: sec1-t4-demo-screen-subj-race-summ
# Get Summary Statistics for Race, Subject-Level
## Calculate summary statistics
obs <- get_group_cat_summary(
  .df = t_df |>
    dplyr::mutate(
      race_cat = ifelse(is.na(race_cat), 'missing', race_cat)
    ),
  "race_cat",
  .val_order = race_val_list,
  .group_var = "dt_screened",
  .group_order = t_group_order
  )

## Display Table - Text columns only
obs |>
  dplyr::select(
    !dplyr::all_of(c(dplyr::ends_with("_n"), dplyr::ends_with("_perc")))
    )
```

We performed Chi-Square and Fisher's Exact test to assess for an association.

```{r}
#| label: sec1-t4-demo-screen-subj-race-stats
# Chi-Square and Fisher's Exact test
get_chi_fisher(
  .df = obs |> 
  dplyr::select(value_name, t_n, f_n) |>
  dplyr::filter(value_name != "TOTAL"),
  .counts_a_var = 't_n',
  .counts_b_var = 'f_n',
  .value_var = 'value_name',
  .omit_vals = c('Missing (NA)')
  )
```

##### Ethnicity

We calculated summary statistics for ethnicity.

```{r}
#| label: sec1-t4-demo-screen-subj-ethn-summ
# Get Summary Statistics for Ethnicity, Subject-Level
## Calculate summary statistics
obs <- get_group_cat_summary(
  .df = t_df |>
    dplyr::mutate(
      hispanic = dplyr::case_when(
        is.na(hispanic) ~ 'missing',
        hispanic ~ 'hispanic',
        !hispanic ~ 'nonhispanic'
      )
    ),
  "hispanic",
  .val_order = hispanic_val_list,
  .group_var = "dt_screened",
  .group_order = t_group_order
  )

## Display Table - Text columns only
obs |>
  dplyr::select(
    !dplyr::all_of(c(dplyr::ends_with("_n"), dplyr::ends_with("_perc")))
    )
```

We performed Chi-Square and Fisher's Exact test to assess for an association.

```{r}
#| label: sec1-t4-demo-screen-subj-ethn-stats
# Chi-Square and Fisher's Exact test
get_chi_fisher(
  .df = obs |> 
  dplyr::select(value_name, t_n, f_n) |>
  dplyr::filter(value_name != "TOTAL"),
  .counts_a_var = 't_n',
  .counts_b_var = 'f_n',
  .value_var = 'value_name',
  .omit_vals = c('Missing (NA)')
  )
```

### By Screening Result (Positive/Negative)

#### Table 1.5: Response-Level (#sec1-t5-demo-result-resp)

We wished to examine demographic differences between responses that received positive and negative DETECT screening outcomes, with a "positive" outcome defined as a "yes" response to at least one DETECT Tool question item. We stored this internally as Table 1.5.

```{r}
#| label: sec1-t5-demo-result-resp-subset
# Take response-level subset for the following analyses
t_df <- ms_records |>
  ## Drop "Duplicate" flagged records
  dplyr::filter(!dup_drop) |>
  ## Select only records with a DETECT screening
  dplyr::filter(dt_screened) |>
  ## Convert grouping variable to text for table functions
  dplyr::mutate(
    dt_positive = dplyr::case_when(
      dt_positive ~ 't',
      !dt_positive ~ 'f'
    )
  )

## Subset-specific group order for tables
t_group_order = list(t = 'Positive Screen', f = 'Negative Screen')
```


##### Age

We calculated summary statistics for calculated age.

```{r}
#| label: sec1-t5-demo-result-resp-age-summ
# Get Summary Statistics for Age by Screening Result, Response-Level
get_group_cont_summary(
  .df = t_df,
  .var_name = "age_calc",
  .group_var = "dt_positive",
  .group_order = t_group_order
  ) 
```

We used a histogram to broadly examine the distribution of values for age. Values demonstrated a significant left skew, and were not approximately normally distributed

```{r}
#| label: sec1-t5-demo-result-resp-age-hist-f0-5
# Figure 0.5: Distribution of Age by Screening Result, Response-Level
## Create Histogram
plot <- ggplot2::ggplot(
  t_df |>
    dplyr::mutate(
      dt_positive = factor(
        dt_positive, levels = names(t_group_order),
        labels = as.character(t_group_order), ordered = T
        )
    ), 
  ggplot2::aes(
    x = age_calc, fill = dt_positive, y = ggplot2::after_stat(density),
    alpha = 0.5
  )) +
  ggplot2::scale_alpha(guide = "none") +
  ggplot2::geom_histogram(binwidth = 1, position = 'identity') +
  ### Convert y-axis scale to a percent
  ggplot2::scale_y_continuous(labels = scales::percent) +
  ### Labels
  ggplot2::labs(
    title="Distribution of Age by Screening Result, Response-Level",
    x= "Calculated Age at Encounter (Years)", 
    y = "Frequency (%)",
    fill = "Screening Result"
    ) +
  ### Colors
  ggplot2::scale_fill_brewer(palette="Spectral")

## Save plot
ggplot2::ggsave(
  filename = here::here(
    "data", "figs",
    "f0-5_age-result-resp-hist.png"
    ),
  plot = plot
  )

## Display plot
plot
```

We performed Student T-Test and Wilcox Rank-Sum testing to assess for a statistical association.

```{r}
#| label: sec1-t5-demo-result-resp-age-stats
# T-Test and Wilcox Rank-Sum for Age, by Screening Result
get_twos_num_stats(
  .df = t_df |>
    dplyr::mutate(
      dt_positive = dplyr::case_when(
        dt_positive == 't' ~ T,
        dt_positive == 'f' ~ F
      )
    ),
  .var_name = 'age_calc',
  .binary_var = 'dt_positive'
)
```

##### Sex

We calculated summary statistics for sex.

```{r}
#| label: sec1-t5-demo-result-resp-sex-summ
# Get Summary Statistics for Sex, Response-Level
## Calculate summary statistics
obs <- get_group_cat_summary(
  .df = t_df |>
    dplyr::mutate(
      sex_cat = ifelse(is.na(sex_cat), 'missing', sex_cat)
    ),
  "sex_cat",
  .val_order = sex_val_list,
  .group_var = "dt_positive",
  .group_order = t_group_order
  )

## Display Table - Text columns only
obs |>
  dplyr::select(
    !dplyr::all_of(c(dplyr::ends_with("_n"), dplyr::ends_with("_perc")))
    )
```

We performed Chi-Square and Fisher's Exact test to assess for an association.

```{r}
#| label: sec1-t5-demo-result-resp-sex-stats
# Chi-Square and Fisher's Exact test
get_chi_fisher(
  .df = obs |> 
  dplyr::select(value_name, t_n, f_n) |>
  dplyr::filter(value_name != "TOTAL"),
  .counts_a_var = 't_n',
  .counts_b_var = 'f_n',
  .value_var = 'value_name',
  .omit_vals = c('Unable to Assess', 'Missing (NA)')
  )
```

##### Race

We calculated summary statistics for race.

```{r}
#| label: sec1-t5-demo-result-resp-race-summ
# Get Summary Statistics for Race, Response-Level
## Calculate summary statistics
obs <- get_group_cat_summary(
  .df = t_df |>
    dplyr::mutate(
      race_cat = ifelse(is.na(race_cat), 'missing', race_cat)
    ),
  "race_cat",
  .val_order = race_val_list,
  .group_var = "dt_positive",
  .group_order = t_group_order
  )

## Display Table - Text columns only
obs |>
  dplyr::select(
    !dplyr::all_of(c(dplyr::ends_with("_n"), dplyr::ends_with("_perc")))
    )
```

We performed Chi-Square and Fisher's Exact test to assess for an association.

```{r}
#| label: sec1-t5-demo-result-resp-race-stats
# Chi-Square and Fisher's Exact test
get_chi_fisher(
  .df = obs |> 
  dplyr::select(value_name, t_n, f_n) |>
  dplyr::filter(value_name != "TOTAL"),
  .counts_a_var = 't_n',
  .counts_b_var = 'f_n',
  .value_var = 'value_name',
  .omit_vals = c('Missing (NA)')
  )
```

##### Ethnicity

We calculated summary statistics for ethnicity.

```{r}
#| label: sec1-t5-demo-result-resp-ethn-summ
# Get Summary Statistics for Ethnicity, Response-Level
## Calculate summary statistics
obs <- get_group_cat_summary(
  .df = t_df |>
    dplyr::mutate(
      hispanic = dplyr::case_when(
        is.na(hispanic) ~ 'missing',
        hispanic ~ 'hispanic',
        !hispanic ~ 'nonhispanic'
      )
    ),
  "hispanic",
  .val_order = hispanic_val_list,
  .group_var = "dt_positive",
  .group_order = t_group_order
  )

## Display Table - Text columns only
obs |>
  dplyr::select(
    !dplyr::all_of(c(dplyr::ends_with("_n"), dplyr::ends_with("_perc")))
    )
```

We performed Chi-Square and Fisher's Exact test to assess for an association.

```{r}
#| label: sec1-t5-demo-result-resp-ethn-stats
# Chi-Square and Fisher's Exact test
get_chi_fisher(
  .df = obs |> 
  dplyr::select(value_name, t_n, f_n) |>
  dplyr::filter(value_name != "TOTAL"),
  .counts_a_var = 't_n',
  .counts_b_var = 'f_n',
  .value_var = 'value_name',
  .omit_vals = c('Missing (NA)')
  )
```

#### Table 1.6: Subject-Level (#sec1-t6-demo-result-subj)

We wished to examine demographic differences between subjects that received positive and negative DETECT screening outcomes, with a "positive" outcome defined as a "yes" response to at least one DETECT Tool question item at at least one screening. We stored this internally as Table 1.6.

```{r}
#| label: sec1-t6-demo-result-subj-subset
# Take response-level subset for the following analyses
t_df <- ms_subjs |>
  ## Filter to only subjects with at least one screening
  dplyr::filter(dt_screened) |>
  ## Convert grouping variable to text for table functions
  dplyr::mutate(
    dt_positive = dplyr::case_when(
      dt_positive ~ 't',
      !dt_positive ~ 'f'
    )
  )

## Subset-specific group order for tables
t_group_order = list(t = 'Positive Screen', f = 'Negative Screen')
```


##### Age

We calculated summary statistics for calculated age.

```{r}
#| label: sec1-t6-demo-result-subj-age-summ
# Get Summary Statistics for Age by Screening Result, Subject-Level
get_group_cont_summary(
  .df = t_df,
  .var_name = "age_avg",
  .group_var = "dt_positive",
  .group_order = t_group_order
  ) 
```

We used a histogram to broadly examine the distribution of values for age. Values demonstrated a significant left skew, and were not approximately normally distributed

```{r}
#| label: sec1-t6-demo-result-subj-age-hist-f0-6
# Figure 0.6: Distribution of Age by Screening Result, Subject-Level
## Create Histogram
plot <- ggplot2::ggplot(
  t_df |>
    dplyr::mutate(
      dt_positive = factor(
        dt_positive, levels = names(t_group_order),
        labels = as.character(t_group_order), ordered = T
        )
    ), 
  ggplot2::aes(
    x = age_avg, fill = dt_positive, y = ggplot2::after_stat(density),
    alpha = 0.5
  )) +
  ggplot2::scale_alpha(guide = "none") +
  ggplot2::geom_histogram(binwidth = 1, position = 'identity') +
  ### Convert y-axis scale to a percent
  ggplot2::scale_y_continuous(labels = scales::percent) +
  ### Labels
  ggplot2::labs(
    title="Distribution of Age by Screening Result, Subject-Level",
    x= "Average Calculated Age at Encounter (Years)", 
    y = "Frequency (%)",
    fill = "Screening Result"
    ) +
  ### Colors
  ggplot2::scale_fill_brewer(palette="Spectral")

## Save plot
ggplot2::ggsave(
  filename = here::here(
    "data", "figs",
    "f0-6_age-result-subj-hist.png"
    ),
  plot = plot
  )

## Display plot
plot
```

We performed Student T-Test and Wilcox Rank-Sum testing to assess for a statistical association.

```{r}
#| label: sec1-t6-demo-result-subj-age-stats
# T-Test and Wilcox Rank-Sum for Age, by Screening Status
get_twos_num_stats(
  .df = t_df |>
    dplyr::mutate(
      dt_positive = dplyr::case_when(
        dt_positive == 't' ~ T,
        dt_positive == 'f' ~ F
      )
    ),
  .var_name = 'age_avg',
  .binary_var = 'dt_positive'
)
```

##### Sex

We calculated summary statistics for sex.

```{r}
#| label: sec1-t6-demo-result-subj-sex-summ
# Get Summary Statistics for Sex, Subject-Level
## Calculate summary statistics
obs <- get_group_cat_summary(
  .df = t_df |>
    dplyr::mutate(
      sex_cat = ifelse(is.na(sex_cat), 'missing', sex_cat)
    ),
  "sex_cat",
  .val_order = sex_val_list,
  .group_var = "dt_positive",
  .group_order = t_group_order
  )

## Display Table - Text columns only
obs |>
  dplyr::select(
    !dplyr::all_of(c(dplyr::ends_with("_n"), dplyr::ends_with("_perc")))
    )
```

We performed Chi-Square and Fisher's Exact test to assess for an association.

```{r}
#| label: sec1-t6-demo-result-subj-sex-stats
# Chi-Square and Fisher's Exact test
get_chi_fisher(
  .df = obs |> 
  dplyr::select(value_name, t_n, f_n) |>
  dplyr::filter(value_name != "TOTAL"),
  .counts_a_var = 't_n',
  .counts_b_var = 'f_n',
  .value_var = 'value_name',
  .omit_vals = c('Unable to Assess', 'Missing (NA)')
  )
```

##### Race

We calculated summary statistics for race.

```{r}
#| label: sec1-t6-demo-result-subj-race-summ
# Get Summary Statistics for Race, Subject-Level
## Calculate summary statistics
obs <- get_group_cat_summary(
  .df = t_df |>
    dplyr::mutate(
      race_cat = ifelse(is.na(race_cat), 'missing', race_cat)
    ),
  "race_cat",
  .val_order = race_val_list,
  .group_var = "dt_positive",
  .group_order = t_group_order
  )

## Display Table - Text columns only
obs |>
  dplyr::select(
    !dplyr::all_of(c(dplyr::ends_with("_n"), dplyr::ends_with("_perc")))
    )
```

We performed Chi-Square and Fisher's Exact test to assess for an association.

```{r}
#| label: sec1-t6-demo-result-subj-race-stats
# Chi-Square and Fisher's Exact test
get_chi_fisher(
  .df = obs |> 
  dplyr::select(value_name, t_n, f_n) |>
  dplyr::filter(value_name != "TOTAL"),
  .counts_a_var = 't_n',
  .counts_b_var = 'f_n',
  .value_var = 'value_name',
  .omit_vals = c('Missing (NA)')
  )
```

##### Ethnicity

We calculated summary statistics for ethnicity.

```{r}
#| label: sec1-t6-demo-result-subj-ethn-summ
# Get Summary Statistics for Ethnicity, Subject-Level
## Calculate summary statistics
obs <- get_group_cat_summary(
  .df = t_df |>
    dplyr::mutate(
      hispanic = dplyr::case_when(
        is.na(hispanic) ~ 'missing',
        hispanic ~ 'hispanic',
        !hispanic ~ 'nonhispanic'
      )
    ),
  "hispanic",
  .val_order = hispanic_val_list,
  .group_var = "dt_positive",
  .group_order = t_group_order
  )

## Display Table - Text columns only
obs |>
  dplyr::select(
    !dplyr::all_of(c(dplyr::ends_with("_n"), dplyr::ends_with("_perc")))
    )
```

We performed Chi-Square and Fisher's Exact test to assess for an association.

```{r}
#| label: sec1-t6-demo-result-subj-ethn-stats
# Chi-Square and Fisher's Exact test
get_chi_fisher(
  .df = obs |> 
  dplyr::select(value_name, t_n, f_n) |>
  dplyr::filter(value_name != "TOTAL"),
  .counts_a_var = 't_n',
  .counts_b_var = 'f_n',
  .value_var = 'value_name',
  .omit_vals = c('Missing (NA)')
  )
```

### By Reporting Intent

#### All Screenings

##### Table 1.7: Response-Level (#sec1-t7-demo-intent-all-resp)

We wished to examine demographic differences between responses that did and did not have a DETECT Tool recorded intent to report. We stored this internally as Table 1.7.

```{r}
#| label: sec1-t7-demo-intent-all-resp-subset
# Take response-level subset for the following analyses
t_df <- ms_records |>
  ## Drop "Duplicate" flagged records
  dplyr::filter(!dup_drop) |>
  ## Select only records with a DETECT screening
  dplyr::filter(dt_screened) |>
  ## Convert grouping variable to text for table functions
  dplyr::mutate(
    dt_aps_reported = dplyr::case_when(
      dt_aps_reported ~ 't',
      !dt_aps_reported ~ 'f'
    )
  )

## Subset-specific group order for tables
t_group_order = list(t = 'Intent to Report', f = 'No Intent')
```

###### Age

We calculated summary statistics for calculated age.

```{r}
#| label: sec1-t7-demo-intent-all-resp-age-summ
# Get Summary Statistics for Age by Intent to Report, Response-Level
get_group_cont_summary(
  .df = t_df,
  .var_name = "age_calc",
  .group_var = "dt_aps_reported",
  .group_order = t_group_order
  ) 
```

We used a histogram to broadly examine the distribution of values for age. Values demonstrated a significant left skew, and were not approximately normally distributed

```{r}
#| label: sec1-t7-demo-intent-all-resp-age-hist-f0-7
# Figure 0.7: Distribution of Age by Intent to Report, Response-Level
## Create Histogram
plot <- ggplot2::ggplot(
  t_df |>
    dplyr::mutate(
      dt_aps_reported = factor(
        dt_aps_reported, levels = names(t_group_order),
        labels = as.character(t_group_order), ordered = T
        )
    ), 
  ggplot2::aes(
    x = age_calc, fill = dt_aps_reported, y = ggplot2::after_stat(density),
    alpha = 0.5
  )) +
  ggplot2::scale_alpha(guide = "none") +
  ggplot2::geom_histogram(binwidth = 1, position = 'identity') +
  ### Convert y-axis scale to a percent
  ggplot2::scale_y_continuous(labels = scales::percent) +
  ### Labels
  ggplot2::labs(
    title="Distribution of Age by Intent to Report, Response-Level",
    x= "Calculated Age at Encounter (Years)", 
    y = "Frequency (%)",
    fill = "Intent to Report"
    ) +
  ### Colors
  ggplot2::scale_fill_brewer(palette="Spectral")

## Save plot
ggplot2::ggsave(
  filename = here::here(
    "data", "figs",
    "f0-7_age-intent-all-resp-hist.png"
    ),
  plot = plot
  )

## Display plot
plot
```

We performed Student T-Test and Wilcox Rank-Sum testing to assess for a statistical association.

```{r}
#| label: sec1-t7-demo-intent-all-resp-age-stats
# T-Test and Wilcox Rank-Sum for Age, by Intent to Report
get_twos_num_stats(
  .df = t_df |>
    dplyr::mutate(
      dt_aps_reported = dplyr::case_when(
        dt_aps_reported == 't' ~ T,
        dt_aps_reported == 'f' ~ F
      )
    ),
  .var_name = "age_calc",
  .binary_var = "dt_aps_reported"
)
```

###### Sex

We calculated summary statistics for sex.

```{r}
#| label: sec1-t7-demo-intent-all-resp-sex-summ
# Get Summary Statistics for Sex, Response-Level
## Calculate summary statistics
obs <- get_group_cat_summary(
  .df = t_df |>
    dplyr::mutate(
      sex_cat = ifelse(is.na(sex_cat), 'missing', sex_cat)
    ),
  "sex_cat",
  .val_order = sex_val_list,
  .group_var = "dt_aps_reported",
  .group_order = t_group_order
  )

## Display Table - Text columns only
obs |>
  dplyr::select(
    !dplyr::all_of(c(dplyr::ends_with("_n"), dplyr::ends_with("_perc")))
    )
```

We performed Chi-Square and Fisher's Exact test to assess for an association.

```{r}
#| label: sec1-t7-demo-intent-all-resp-sex-stats
# Chi-Square and Fisher's Exact test
get_chi_fisher(
  .df = obs |> 
  dplyr::select(value_name, t_n, f_n) |>
  dplyr::filter(value_name != "TOTAL"),
  .counts_a_var = 't_n',
  .counts_b_var = 'f_n',
  .value_var = 'value_name',
  .omit_vals = c('Unable to Assess', 'Missing (NA)')
  )
```

###### Race

We calculated summary statistics for race.

```{r}
#| label: sec1-t7-demo-intent-all-resp-race-summ
# Get Summary Statistics for Race, Response-Level
## Calculate summary statistics
obs <- get_group_cat_summary(
  .df = t_df |>
    dplyr::mutate(
      race_cat = ifelse(is.na(race_cat), 'missing', race_cat)
    ),
  "race_cat",
  .val_order = race_val_list,
  .group_var = "dt_aps_reported",
  .group_order = t_group_order
  )

## Display Table - Text columns only
obs |>
  dplyr::select(
    !dplyr::all_of(c(dplyr::ends_with("_n"), dplyr::ends_with("_perc")))
    )
```

We performed Chi-Square and Fisher's Exact test to assess for an association.

```{r}
#| label: sec1-t7-demo-intent-all-resp-race-stats
# Chi-Square and Fisher's Exact test
get_chi_fisher(
  .df = obs |> 
  dplyr::select(value_name, t_n, f_n) |>
  dplyr::filter(value_name != "TOTAL"),
  .counts_a_var = 't_n',
  .counts_b_var = 'f_n',
  .value_var = 'value_name',
  .omit_vals = c('Missing (NA)')
  )
```

###### Ethnicity

We calculated summary statistics for ethnicity.

```{r}
#| label: sec1-t7-demo-intent-all-resp-ethn-summ
# Get Summary Statistics for Ethnicity, Response-Level
## Calculate summary statistics
obs <- get_group_cat_summary(
  .df = t_df |>
    dplyr::mutate(
      hispanic = dplyr::case_when(
        is.na(hispanic) ~ 'missing',
        hispanic ~ 'hispanic',
        !hispanic ~ 'nonhispanic'
      )
    ),
  "hispanic",
  .val_order = hispanic_val_list,
  .group_var = "dt_aps_reported",
  .group_order = t_group_order
  )

## Display Table - Text columns only
obs |>
  dplyr::select(
    !dplyr::all_of(c(dplyr::ends_with("_n"), dplyr::ends_with("_perc")))
    )
```

We performed Chi-Square and Fisher's Exact test to assess for an association.

```{r}
#| label: sec1-t7-demo-intent-all-resp-ethn-stats
# Chi-Square and Fisher's Exact test
get_chi_fisher(
  .df = obs |> 
  dplyr::select(value_name, t_n, f_n) |>
  dplyr::filter(value_name != "TOTAL"),
  .counts_a_var = 't_n',
  .counts_b_var = 'f_n',
  .value_var = 'value_name',
  .omit_vals = c('Missing (NA)')
  )
```

##### Table 1.8: Subject-Level (#sec1-t8-demo-intent-all-subj)

We wished to examine demographic differences between subjects that did and did not have a DETECT Tool recorded intent to report. We stored this internally as Table 1.8.

```{r}
#| label: sec1-t8-demo-intent-all-subj-subset
# Take response-level subset for the following analyses
t_df <- ms_subjs |>
  ## Filter to only subjects with at least one screening
  dplyr::filter(dt_screened) |>
  ## Convert grouping variable to text for table functions
  dplyr::mutate(
    dt_aps_reported = dplyr::case_when(
      dt_aps_reported ~ 't',
      !dt_aps_reported ~ 'f'
    )
  )

## Subset-specific group order for tables
t_group_order = list(t = 'Intent to Report', f = 'No Intent')
```


###### Age

We calculated summary statistics for calculated age.

```{r}
#| label: sec1-t8-demo-intent-all-subj-age-summ
# Get Summary Statistics for Age by Intent to Report, Subject-Level
get_group_cont_summary(
  .df = t_df,
  .var_name = "age_avg",
  .group_var = "dt_aps_reported",
  .group_order = t_group_order
  ) 
```

We used a histogram to broadly examine the distribution of values for age. Values demonstrated a significant left skew, and were not approximately normally distributed

```{r}
#| label: sec1-t8-demo-intent-all-subj-age-hist-f0-8
# Figure 0.8: Distribution of Age by Intent to Report, Subject-Level
## Create Histogram
plot <- ggplot2::ggplot(
  t_df |>
    dplyr::mutate(
      dt_aps_reported = factor(
        dt_aps_reported, levels = names(t_group_order),
        labels = as.character(t_group_order), ordered = T
        )
    ), 
  ggplot2::aes(
    x = age_avg, fill = dt_aps_reported, y = ggplot2::after_stat(density),
    alpha = 0.5
  )) +
  ggplot2::scale_alpha(guide = "none") +
  ggplot2::geom_histogram(binwidth = 1, position = 'identity') +
  ### Convert y-axis scale to a percent
  ggplot2::scale_y_continuous(labels = scales::percent) +
  ### Labels
  ggplot2::labs(
    title="Distribution of Age by Intent to Report, Subject-Level",
    x= "Average Calculated Age at Encounter (Years)", 
    y = "Frequency (%)",
    fill = "Intent to Report"
    ) +
  ### Colors
  ggplot2::scale_fill_brewer(palette="Spectral")

## Save plot
ggplot2::ggsave(
  filename = here::here(
    "data", "figs",
    "f0-8_age-intent-all-subj-hist.png"
    ),
  plot = plot
  )

## Display plot
plot
```

We performed Student T-Test and Wilcox Rank-Sum testing to assess for a statistical association.

```{r}
#| label: sec1-t8-demo-intent-all-subj-age-stats
# T-Test and Wilcox Rank-Sum for Age, by Screening Status
get_twos_num_stats(
  .df = t_df |>
    dplyr::mutate(
      dt_aps_reported = dplyr::case_when(
        dt_aps_reported == 't' ~ T,
        dt_aps_reported == 'f' ~ F
      )
    ),
  .var_name = "age_avg",
  .binary_var = "dt_aps_reported"
)
```

###### Sex

We calculated summary statistics for sex.

```{r}
#| label: sec1-t8-demo-intent-all-subj-sex-summ
# Get Summary Statistics for Sex, Subject-Level
## Calculate summary statistics
obs <- get_group_cat_summary(
  .df = t_df |>
    dplyr::mutate(
      sex_cat = ifelse(is.na(sex_cat), 'missing', sex_cat)
    ),
  "sex_cat",
  .val_order = sex_val_list,
  .group_var = "dt_aps_reported",
  .group_order = t_group_order
  )

## Display Table - Text columns only
obs |>
  dplyr::select(
    !dplyr::all_of(c(dplyr::ends_with("_n"), dplyr::ends_with("_perc")))
    )
```

We performed Chi-Square and Fisher's Exact test to assess for an association.

```{r}
#| label: sec1-t8-demo-intent-all-subj-sex-stats
# Chi-Square and Fisher's Exact test
get_chi_fisher(
  .df = obs |> 
  dplyr::select(value_name, t_n, f_n) |>
  dplyr::filter(value_name != "TOTAL"),
  .counts_a_var = 't_n',
  .counts_b_var = 'f_n',
  .value_var = 'value_name',
  .omit_vals = c('Unable to Assess', 'Missing (NA)')
  )
```

###### Race

We calculated summary statistics for race.

```{r}
#| label: sec1-t8-demo-intent-all-subj-race-summ
# Get Summary Statistics for Race, Subject-Level
## Calculate summary statistics
obs <- get_group_cat_summary(
  .df = t_df |>
    dplyr::mutate(
      race_cat = ifelse(is.na(race_cat), 'missing', race_cat)
    ),
  "race_cat",
  .val_order = race_val_list,
  .group_var = "dt_aps_reported",
  .group_order = t_group_order
  )

## Display Table - Text columns only
obs |>
  dplyr::select(
    !dplyr::all_of(c(dplyr::ends_with("_n"), dplyr::ends_with("_perc")))
    )
```

We performed Chi-Square and Fisher's Exact test to assess for an association.

```{r}
#| label: sec1-t8-demo-intent-all-subj-race-stats
# Chi-Square and Fisher's Exact test
get_chi_fisher(
  .df = obs |> 
  dplyr::select(value_name, t_n, f_n) |>
  dplyr::filter(value_name != "TOTAL"),
  .counts_a_var = 't_n',
  .counts_b_var = 'f_n',
  .value_var = 'value_name',
  .omit_vals = c('Missing (NA)')
  )
```

###### Ethnicity

We calculated summary statistics for ethnicity.

```{r}
#| label: sec1-t8-demo-intent-all-subj-ethn-summ
# Get Summary Statistics for Ethnicity, Subject-Level
## Calculate summary statistics
obs <- get_group_cat_summary(
  .df = t_df |>
    dplyr::mutate(
      hispanic = dplyr::case_when(
        is.na(hispanic) ~ 'missing',
        hispanic ~ 'hispanic',
        !hispanic ~ 'nonhispanic'
      )
    ),
  "hispanic",
  .val_order = hispanic_val_list,
  .group_var = "dt_aps_reported",
  .group_order = t_group_order
  )

## Display Table - Text columns only
obs |>
  dplyr::select(
    !dplyr::all_of(c(dplyr::ends_with("_n"), dplyr::ends_with("_perc")))
    )
```

We performed Chi-Square and Fisher's Exact test to assess for an association.

```{r}
#| label: sec1-t8-demo-intent-all-subj-ethn-stats
# Chi-Square and Fisher's Exact test
get_chi_fisher(
  .df = obs |> 
  dplyr::select(value_name, t_n, f_n) |>
  dplyr::filter(value_name != "TOTAL"),
  .counts_a_var = 't_n',
  .counts_b_var = 'f_n',
  .value_var = 'value_name',
  .omit_vals = c('Missing (NA)')
  )
```

#### Table 1.9: Positive Screenings, Response-Level (#sec1-t9-demo-intent-pos-resp)

We wished to examine demographic differences between responses with positive DETECT screenings that did and not have a DETECT Tool recorded intent to report. We stored this internally as Table 1.9.

```{r}
#| label: sec1-t9-demo-intent-pos-resp-subset
# Take response-level subset for the following analyses
t_df <- ms_records |>
  ## Drop "Duplicate" flagged records
  dplyr::filter(!dup_drop) |>
  ## Select only records with a DETECT screening
  dplyr::filter(dt_screened) |>
  ## Select only positive DETECT screenings
  dplyr::filter(dt_positive) |>
  ## Convert grouping variable to text for table functions
  dplyr::mutate(
    dt_aps_reported = dplyr::case_when(
      dt_aps_reported ~ 't',
      !dt_aps_reported ~ 'f'
    )
  )

## Subset-specific group order for tables
t_group_order = list(t = 'Intent to Report', f = 'No Intent')
```

##### Age

We calculated summary statistics for calculated age.

```{r}
#| label: sec1-t9-demo-intent-pos-resp-age-summ
# Get Summary Statistics for Age by Intent to Report, Response-Level
get_group_cont_summary(
  .df = t_df,
  .var_name = "age_calc",
  .group_var = "dt_aps_reported",
  .group_order = t_group_order
  ) 
```

We used a histogram to broadly examine the distribution of values for age. Values demonstrated a significant left skew, and were not approximately normally distributed

```{r}
#| label: sec1-t9-demo-intent-pos-resp-age-hist-f0-9
# Figure 0.9: Distribution of Age by Intent to Report, Positive Screenings, 
# Response-Level
## Create Histogram
plot <- ggplot2::ggplot(
  t_df |>
    dplyr::mutate(
      dt_aps_reported = factor(
        dt_aps_reported, levels = names(t_group_order),
        labels = as.character(t_group_order), ordered = T
        )
    ), 
  ggplot2::aes(
    x = age_calc, fill = dt_aps_reported, y = ggplot2::after_stat(density),
    alpha = 0.5
  )) +
  ggplot2::scale_alpha(guide = "none") +
  ggplot2::geom_histogram(binwidth = 1, position = 'identity') +
  ### Convert y-axis scale to a percent
  ggplot2::scale_y_continuous(labels = scales::percent) +
  ### Labels
  ggplot2::labs(
    title = paste0(
      "Distribution of Age by Intent to Report, Positive Screenings,",
      " Response-Level"
      ),
    x = "Calculated Age at Encounter (Years)", 
    y = "Frequency (%)",
    fill = "Intent to Report"
    ) +
  ### Colors
  ggplot2::scale_fill_brewer(palette="Spectral")

## Save plot
ggplot2::ggsave(
  filename = here::here(
    "data", "figs",
    "f0-9_age-intent-pos-resp-hist.png"
    ),
  plot = plot
  )

## Display plot
plot
```

We performed Student T-Test and Wilcox Rank-Sum testing to assess for a statistical association.

```{r}
#| label: sec1-t9-demo-intent-pos-resp-age-stats
# T-Test and Wilcox Rank-Sum for Age, by Intent to Report
get_twos_num_stats(
  .df = t_df |>
    dplyr::mutate(
      dt_aps_reported = dplyr::case_when(
        dt_aps_reported == 't' ~ T,
        dt_aps_reported == 'f' ~ F
      )
    ),
  .var_name = "age_calc",
  .binary_var = "dt_aps_reported"
)
```

##### Sex

We calculated summary statistics for sex.

```{r}
#| label: sec1-t9-demo-intent-pos-resp-sex-summ
# Get Summary Statistics for Sex, Response-Level
## Calculate summary statistics
obs <- get_group_cat_summary(
  .df = t_df |>
    dplyr::mutate(
      sex_cat = ifelse(is.na(sex_cat), 'missing', sex_cat)
    ),
  "sex_cat",
  .val_order = sex_val_list,
  .group_var = "dt_aps_reported",
  .group_order = t_group_order
  )

## Display Table - Text columns only
obs |>
  dplyr::select(
    !dplyr::all_of(c(dplyr::ends_with("_n"), dplyr::ends_with("_perc")))
    )
```

We performed Chi-Square and Fisher's Exact test to assess for an association.

```{r}
#| label: sec1-t9-demo-intent-pos-resp-sex-stats
# Chi-Square and Fisher's Exact test
get_chi_fisher(
  .df = obs |> 
  dplyr::select(value_name, t_n, f_n) |>
  dplyr::filter(value_name != "TOTAL"),
  .counts_a_var = 't_n',
  .counts_b_var = 'f_n',
  .value_var = 'value_name',
  .omit_vals = c('Unable to Assess', 'Missing (NA)')
  )
```

##### Race

We calculated summary statistics for race.

```{r}
#| label: sec1-t9-demo-intent-pos-resp-race-summ
# Get Summary Statistics for Race, Response-Level
## Calculate summary statistics
obs <- get_group_cat_summary(
  .df = t_df |>
    dplyr::mutate(
      race_cat = ifelse(is.na(race_cat), 'missing', race_cat)
    ),
  "race_cat",
  .val_order = race_val_list,
  .group_var = "dt_aps_reported",
  .group_order = t_group_order
  )

## Display Table - Text columns only
obs |>
  dplyr::select(
    !dplyr::all_of(c(dplyr::ends_with("_n"), dplyr::ends_with("_perc")))
    )
```

We performed Chi-Square and Fisher's Exact test to assess for an association.

```{r}
#| label: sec1-t9-demo-intent-pos-resp-race-stats
# Chi-Square and Fisher's Exact test
get_chi_fisher(
  .df = obs |> 
  dplyr::select(value_name, t_n, f_n) |>
  dplyr::filter(value_name != "TOTAL"),
  .counts_a_var = 't_n',
  .counts_b_var = 'f_n',
  .value_var = 'value_name',
  .omit_vals = c('Missing (NA)')
  )
```

##### Ethnicity

We calculated summary statistics for ethnicity.

```{r}
#| label: sec1-t9-demo-intent-pos-resp-ethn-summ
# Get Summary Statistics for Ethnicity, Response-Level
## Calculate summary statistics
obs <- get_group_cat_summary(
  .df = t_df |>
    dplyr::mutate(
      hispanic = dplyr::case_when(
        is.na(hispanic) ~ 'missing',
        hispanic ~ 'hispanic',
        !hispanic ~ 'nonhispanic'
      )
    ),
  "hispanic",
  .val_order = hispanic_val_list,
  .group_var = "dt_aps_reported",
  .group_order = t_group_order
  )

## Display Table - Text columns only
obs |>
  dplyr::select(
    !dplyr::all_of(c(dplyr::ends_with("_n"), dplyr::ends_with("_perc")))
    )
```

We performed Chi-Square and Fisher's Exact test to assess for an association.

```{r}
#| label: sec1-t9-demo-intent-pos-resp-ethn-stats
# Chi-Square and Fisher's Exact test
get_chi_fisher(
  .df = obs |> 
  dplyr::select(value_name, t_n, f_n) |>
  dplyr::filter(value_name != "TOTAL"),
  .counts_a_var = 't_n',
  .counts_b_var = 'f_n',
  .value_var = 'value_name',
  .omit_vals = c('Missing (NA)')
  )
```

#### Table 1.10: Positive Screenings, Response-Level (#sec1-t10-demo-intent-neg-resp)

We wished to examine demographic differences between responses with negative DETECT screenings that did and not have a DETECT Tool recorded intent to report. We stored this internally as Table 1.10.

```{r}
#| label: sec1-t10-demo-intent-neg-resp-subset
# Take response-level subset for the following analyses
t_df <- ms_records |>
  ## Drop "Duplicate" flagged records
  dplyr::filter(!dup_drop) |>
  ## Select only records with a DETECT screening
  dplyr::filter(dt_screened) |>
  ## Select only negative DETECT screenings
  dplyr::filter(!dt_positive) |>
  ## Convert grouping variable to text for table functions
  dplyr::mutate(
    dt_aps_reported = dplyr::case_when(
      dt_aps_reported ~ 't',
      !dt_aps_reported ~ 'f'
    )
  )

## Subset-specific group order for tables
t_group_order = list(t = 'Intent to Report', f = 'No Intent')
```

##### Age

We calculated summary statistics for calculated age.

```{r}
#| label: sec1-t10-demo-intent-neg-resp-age-summ
# Get Summary Statistics for Age by Intent to Report, Response-Level
get_group_cont_summary(
  .df = t_df,
  .var_name = "age_calc",
  .group_var = "dt_aps_reported",
  .group_order = t_group_order
  ) 
```

We used a histogram to broadly examine the distribution of values for age. Values demonstrated a significant left skew, and were not approximately normally distributed

```{r}
#| label: sec1-t10-demo-intent-neg-resp-age-hist-f0-10
# Figure 0.9: Distribution of Age by Intent to Report, Negative Screenings, 
# Response-Level
## Create Histogram
plot <- ggplot2::ggplot(
  t_df |>
    dplyr::mutate(
      dt_aps_reported = factor(
        dt_aps_reported, levels = names(t_group_order),
        labels = as.character(t_group_order), ordered = T
        )
    ), 
  ggplot2::aes(
    x = age_calc, fill = dt_aps_reported, y = ggplot2::after_stat(density),
    alpha = 0.5
  )) +
  ggplot2::scale_alpha(guide = "none") +
  ggplot2::geom_histogram(binwidth = 1, position = 'identity') +
  ### Convert y-axis scale to a percent
  ggplot2::scale_y_continuous(labels = scales::percent) +
  ### Labels
  ggplot2::labs(
    title = paste0(
      "Distribution of Age by Intent to Report, Negative Screenings,",
      " Response-Level"
      ),
    x = "Calculated Age at Encounter (Years)", 
    y = "Frequency (%)",
    fill = "Intent to Report"
    ) +
  ### Colors
  ggplot2::scale_fill_brewer(palette="Spectral")

## Save plot
ggplot2::ggsave(
  filename = here::here(
    "data", "figs",
    "f0-10_age-intent-neg-resp-hist.png"
    ),
  plot = plot
  )

## Display plot
plot
```

We performed Student T-Test and Wilcox Rank-Sum testing to assess for a statistical association.

```{r}
#| label: sec1-t10-demo-intent-neg-resp-age-stats
# T-Test and Wilcox Rank-Sum for Age, by Intent to Report
get_twos_num_stats(
  .df = t_df |>
    dplyr::mutate(
      dt_aps_reported = dplyr::case_when(
        dt_aps_reported == 't' ~ T,
        dt_aps_reported == 'f' ~ F
      )
    ),
  .var_name = "age_calc",
  .binary_var = "dt_aps_reported"
)
```

##### Sex

We calculated summary statistics for sex.

```{r}
#| label: sec1-t10-demo-intent-neg-resp-sex-summ
# Get Summary Statistics for Sex, Response-Level
## Calculate summary statistics
obs <- get_group_cat_summary(
  .df = t_df |>
    dplyr::mutate(
      sex_cat = ifelse(is.na(sex_cat), 'missing', sex_cat)
    ),
  "sex_cat",
  .val_order = sex_val_list,
  .group_var = "dt_aps_reported",
  .group_order = t_group_order
  )

## Display Table - Text columns only
obs |>
  dplyr::select(
    !dplyr::all_of(c(dplyr::ends_with("_n"), dplyr::ends_with("_perc")))
    )
```

We performed Chi-Square and Fisher's Exact test to assess for an association.

```{r}
#| label: sec1-t10-demo-intent-neg-resp-sex-stats
# Chi-Square and Fisher's Exact test
get_chi_fisher(
  .df = obs |> 
  dplyr::select(value_name, t_n, f_n) |>
  dplyr::filter(value_name != "TOTAL"),
  .counts_a_var = 't_n',
  .counts_b_var = 'f_n',
  .value_var = 'value_name',
  .omit_vals = c('Unable to Assess', 'Missing (NA)')
  )
```

##### Race

We calculated summary statistics for race.

```{r}
#| label: sec1-t10-demo-intent-neg-resp-race-summ
# Get Summary Statistics for Race, Response-Level
## Calculate summary statistics
obs <- get_group_cat_summary(
  .df = t_df |>
    dplyr::mutate(
      race_cat = ifelse(is.na(race_cat), 'missing', race_cat)
    ),
  "race_cat",
  .val_order = race_val_list,
  .group_var = "dt_aps_reported",
  .group_order = t_group_order
  )

## Display Table - Text columns only
obs |>
  dplyr::select(
    !dplyr::all_of(c(dplyr::ends_with("_n"), dplyr::ends_with("_perc")))
    )
```

We performed Chi-Square and Fisher's Exact test to assess for an association.

```{r}
#| label: sec1-t10-demo-intent-neg-resp-race-stats
# Chi-Square and Fisher's Exact test
get_chi_fisher(
  .df = obs |> 
  dplyr::select(value_name, t_n, f_n) |>
  dplyr::filter(value_name != "TOTAL"),
  .counts_a_var = 't_n',
  .counts_b_var = 'f_n',
  .value_var = 'value_name',
  .omit_vals = c('Missing (NA)')
  )
```

##### Ethnicity

We calculated summary statistics for ethnicity.

```{r}
#| label: sec1-t10-demo-intent-neg-resp-ethn-summ
# Get Summary Statistics for Ethnicity, Response-Level
## Calculate summary statistics
obs <- get_group_cat_summary(
  .df = t_df |>
    dplyr::mutate(
      hispanic = dplyr::case_when(
        is.na(hispanic) ~ 'missing',
        hispanic ~ 'hispanic',
        !hispanic ~ 'nonhispanic'
      )
    ),
  "hispanic",
  .val_order = hispanic_val_list,
  .group_var = "dt_aps_reported",
  .group_order = t_group_order
  )

## Display Table - Text columns only
obs |>
  dplyr::select(
    !dplyr::all_of(c(dplyr::ends_with("_n"), dplyr::ends_with("_perc")))
    )
```

We performed Chi-Square and Fisher's Exact test to assess for an association.

```{r}
#| label: sec1-t10-demo-intent-neg-resp-ethn-stats
# Chi-Square and Fisher's Exact test
get_chi_fisher(
  .df = obs |> 
  dplyr::select(value_name, t_n, f_n) |>
  dplyr::filter(value_name != "TOTAL"),
  .counts_a_var = 't_n',
  .counts_b_var = 'f_n',
  .value_var = 'value_name',
  .omit_vals = c('Missing (NA)')
  )
```

# 🧹 Clean up

```{r}
#| label: end-cleanup
rm(list=ls())
```

