---
title: "Analyses Section 4: Temporal Trends"
html:
  embed-resources: true
format: html
---

# ⭐️ Overview

## This File

This file performs the initial explorations and analyses of Temporal Trends within the MedStar 5-year follow-up data, internally referred to as "Section 4: Temporal Trends".

## MedStar Data Background

The MedStar records were originally recorded in Filemaker Pro. Processing of this data was extensive and across multiple data files. These files are documented in the [wiki](https://github.com/brad-cannell/detect_fu_interviews_public/wiki).

The primary files of interest for subject-level interest included participant demographic data in the `participant_import.rds` file [created in a separate Quarto file](https://github.com/brad-cannell/detect_fu_interviews_public/blob/main/data_management/data_01_participant_import.qmd), and the original within-set unique subject ID assignment in `participant_unique_ids.rds` file [created in a separate Quarto file](https://github.com/brad-cannell/detect_fu_interviews_public/blob/main/data_management/unique_person_identification/data_02_unique_person_detect_fu_data.qmd).

These files originally contained 92,160 observations of approximately 30 demographic variables. Refinement of unique subject ID assignments in subject-linkage to APS resulted in 41,955 values of `ms_id`.

## Internal Files

This document was created as part of the DETECT project, specifically the merger of APS and MedStar data for analysis using the full follow-up period data. Internal documents relating to these files, which contain PHI, are securely stored on the research group's SharePoint in the [5-year data manuscript directory](https://uthtmc.sharepoint.com/:f:/r/sites/SPHDETECT-RPC/Shared%20Documents/DETECT%20R01%202018/Manuscripts/Brianna%20Morri%20-%20APS%205%20year%20year%20update?csf=1&web=1&e=fhfOfL).

**Notes for analyses** start at the parent document["00_DETECT 5-year Analysis Notes.docx"](https://uthtmc.sharepoint.com/:w:/r/sites/SPHDETECT-RPC/Shared%20Documents/DETECT%20R01%202018/Manuscripts/Brianna%20Morri%20-%20APS%205%20year%20year%20update/tables/00_DETECT%205-Year%20Analysis%20Notes.docx?d=w09a61782c9ef4fe78780683996fdbd1b&csf=1&web=1&e=OWsgTv). Notes for this file are in ["section 4 - temporal trends.docx"](https://uthtmc.sharepoint.com/:w:/r/sites/SPHDETECT-RPC/Shared%20Documents/DETECT%20R01%202018/Manuscripts/Brianna%20Morri%20-%20APS%205%20year%20year%20update/tables/section%204%20-%20temporal%20trends.docx?d=wb184cfc2889d4ee9a731c1e4adfa49c6&csf=1&web=1&e=iY2Wcg).

Notes for the MedStar data are located in the [notes_00_data_medstar.docx](https://uthtmc.sharepoint.com/:w:/r/sites/SPHDETECT-RPC/Shared%20Documents/DETECT%20R01%202018/02%20Shared%20Folders/DETECT%20Follow-up%20Interview%20Data%20Shared/data/notes_documents/notes_00_data_medstar.docx?d=w7367b418df5644fbb3ff5117908f27d9&csf=1&web=1&e=gueXsZ) file.

Please note: as these files contain PHI and proprietary information, they are not publicly available. Links are internal to the research team.

# 📦 Load Packages and Functions

## Library Imports

```{r}
#| label: imports-libraries
#| warning: FALSE
suppressPackageStartupMessages({
  library(tidyverse)
  library(here)
  library(ggplot2)
  library(patchwork)
})
```

### Versioning

This file was created with:

-   R version 4.4.1 ("Race for Your Life").
-   tidyverse version 2.0.0, including all attached packages
-   here version 1.0.1
-   stats version 4.4.1
-   ggplot2 version 3.5.1
-   patchwork version 1.3.0

## Functions

```{r}
#| label: imports-functions
# Function to reduce code repetition in informative imports of data
source(here::here("r", "informative_df_import.R"))

# Function that creates a modified version of table output, allowing
# simplified manual review of unique values in a given column or set of
# columns
source(here::here("r", "get_unique_value_summary.R"))

# Function that creates a text-based, human-legible summary statistic table
# for a numeric column
source(here::here("r", "get_cont_summary.R"))
# Function that wraps "get_cont_summary()" to process multiple groups at once.
source(here::here("r", "get_group_cont_summary.R"))

# Function that creates a text-based, human-legible summary statistic table
# for a categorical column
source(here::here("r", "get_cat_summary.R"))
# Function that wraps "get_cat_summary()" to process multiple groups at once.
source(here::here("r", "get_group_cat_summary.R"))

## Function that performs 2-Category Chi-Square and Fisher Exact and produces
## a human-legible summary table
source(here::here("r", "get_chi_fisher.R"))

## Function that performs 2-category T-Test and Wilcox Rank-Sum test and 
## produces a human-legible summary table
source(here::here("r", "get_twos_num_stats.R"))

## Function that extracts response pattern tables from DETECT variables
source(here::here("r", "get_dt_resp_pattern.R"))

## Function that performs Chi-Square and Fisher's Exact on DETECT Response
## Patterns, by Item
source(here::here("r", "get_dt_rp_chi_fisher.R"))

## Function that extracts the count and percent of values in a set of columns
## based on a grouping variable
source(here::here("r", "get_freq_grouped.R"))
```

# 📥 Load Data

## MedStar Data

We loaded our MedStar record-level data.

```{r}
#| label: load-ms-records
# Load MedStar Record Level Data
## Path to data
path <- here::here(
    "data", "cleaned_rds_files", "analysis", 
    "medstar_01_record-lvl.rds"
    )

## Load
informative_df_import(
    "ms_records", path, overwrite = T
  )

# [Placeholder]
```

# Analyses

We set the path to where we wished to save our plot files.

```{r}
#| label: set-plot-path
# Set path to directory to save plot image files
plot_path <- paste0(here::here('data', 'figs'), '/')
```

We set the order and labels for values in categorical variables we may use in temporal trends plots.

```{r}
#| label: set-value-orders
# Set order and labels for values in categorical variables that may be used
# in plots

## Sex value order
sex_val_list = list(
    male = 'Male', female = 'Female', uta = 'Unable to Assess', 
    missing = 'Missing (NA)'
    )

## Race value order and labels
race_val_list = list(
  white = "White", black = "Black or African American", asian = "Asian", 
  nhpi = "Native Hawaiian or Other Pacific Islander", 
  aian = "American Indian or Alaska Native", 
  mena = "Middle Eastern or North African", 
  other = "Other Race", multiracial = "Multiracial", missing = "Missing (NA)"
  )

## Hispanic Ethnicity value order and labels
hispanic_val_list = list(
  hispanic = 'Hispanic or Latino', nonhispanic = 'Not Hispanic or Latino', 
  missing = 'Missing (NA)'
  )

## Screening Result value labels ('dt_positive') 
screen_result_list <- list(
  completed = "Screenings Completed (Any Result)", 
  negative = "Negative Screenings", 
  positive = "Positive Screenings",
  missing = "No Screening Performed"
  )

## Reporting Intent value labels ('dt_aps_reported')
report_intent_vals <- list(
  completed = "Recorded Intent (Any Result)",
  intent = "Intent to Report", 
  no_intent = "No Intent to Report", 
  missing = "Not Screened"
  )

## DETECT Tool Variable Item Order and labels
dt_item_list <- list(
  dt_env_odor = "Unusual odor", 
  dt_env_hoard = "Disarray or hoarding",
  dt_env_concern = "Health or safety concern",
  dt_pt_isolated = "Isolated in the home", 
  dt_pt_hygiene = "Poor personal hygiene",
  dt_pt_clothes = "Inadequately clothed",
  dt_pt_needs = "Unmet needs for assistance",
  dt_pt_depress = "Emotionally distressed",
  dt_pt_med_hoard = "Hoarding or saving old medications", 
  dt_pt_med_diff = "Difficulties taking medications as directed",
  dt_cg_lack = "Lacks knowledge of medical needs",
  dt_cg_uneng = "Unengaged and inattentive",
  dt_cg_frust = "Frustrated, tired, angry, or burdened",
  dt_cg_anx = "Overly concerned (e.g. anxious, hovering)"
  )

## DETECT Tool Response Item Order and labels
dt_item_vals <- list(
    completed = "Item Completed (Any Response)",
    yes = "Yes", no = "No", uta = "Unable to Assess", 
    missing = "Item Not Completed"
    )

## DETECT Tool Question Categories and labels
dt_cat_labels <- list(
  env = "Environmental Questions",
  pt = "Patient Condition Questions",
  cg = "Caregiver Questions"
  )

## APS Intake Flag value order and labels
aps_intake_labels <- list(
  t = "Matched APS Intake, Any Reporter Type",
  f = "No Matched APS Intake, Any Reporter Type"
  )

## APS Intake Type value order and labels
aps_intake_type_labels <- list(
  completed = "Matched APS Intake, Any Reporter Type",
  ems = "Explicitly EMS Reporter Type",
  poss = "EMS Reasonable Reporter Type (Not EMS Explicit)",
  any = "Not Likely to be EMS Reporter",
  missing = "No Matched Intake, Any Reporter Type"
  )

## APS Investigation presence value order and labels
aps_inv_labels <- list(
  t = "Matched APS Investigation, Any Disposition",
  f = "No Matched APS Investigation"
  )

## APS Investigation Disposition value order and labels
aps_dispo_labels <- list(
  completed = "Matched APS Investigation, Any Disposition",
  valid = "1+ Valid Allegation",
  mixed_validity = "Mix of Valid and Invalid Allegations",
  invalid = "No Valid Allegations",
  utd = "Unable to Determine",
  other = "Other (Not Investigated)",
  missing = "No Matched APS Investigation"
  )
```

## Section 4: Temporal Trends

We wished to analyse our temporal trends at the study month level.

```{r}
#| label: sec4-add-month
# Create Month-data backbone
## Add Study Month variable to the records data.
ms_records <- ms_records |>
    ## Calculate study month
    dplyr::mutate(
      month = 1 + lubridate::interval(
        '2019-07-01', 
        lubridate::as_date(incident_timestamp)
        ) %/% months(1)
    ) |>
  ## Remove potentially duplicated responses
  dplyr::filter(!dup_drop)
```

### Screening Completion Rate, by Month 

We calculated our screening completion rate and results, by month.

```{r}
#| label: sec4-screen-outcomes-month-calc
# Get Screening Completion & Result Rates, by Month
## Calculate the screening results, which also calculates completion, for
## each month
screening_freqs <- get_freq_grouped(
  .df = ms_records |>
    ## Reduce to month and screening result columns
    dplyr::select(month, dt_positive) |>
    ## Convert screening result column from binary/logical to text categories
    dplyr::mutate(
      dt_positive = dplyr::case_when(
        dt_positive ~ 'positive',
        !dt_positive ~ 'negative',
        is.na(dt_positive) ~ 'missing'
      )
    ),
  .group_var = 'month',
  .item_list = list(dt_positive = "Screening Result"),
  .val_order = screen_result_list[names(screen_result_list) != 'completed']
  ) |>
  ### Convert month to a numeric, for plot
  dplyr::mutate(month = as.numeric(month))
```

#### Figure 4.1: Screening Completion Rate, by Month (#sec4-f1-screen-rate-month)

We examined our screening completion rate, by month.

```{r}
#| label: sec4-f1-screen-rate-month-plot
# Plotting Screening Rate per Month
## Extract data frame for the plot
plot_df <- screening_freqs |>
  ### Filter to only 'completed' responses for this plot
  dplyr::filter(response == 'completed') |>
  ### Flag the month with the lowest completion rate
  dplyr::mutate(min_point = per_total == min(per_total))

## Create plot
plot <- ggplot2::ggplot(
  data = plot_df, 
  ggplot2::aes(x = month, y = per_total)
  ) + 
  ggplot2::geom_line() +
  ### Convert y-axis scale to a percent
  ggplot2::scale_y_continuous(labels = scales::percent) +
  ### Add a purple dot at the points with the lowest "per_total"
  ggplot2::geom_point(size = 1, ggplot2::aes(colour = factor(min_point))) +
  ggplot2::scale_color_manual(values = c('black', 'purple')) +
  ggplot2::theme(legend.position = 'none') +
  ### Labels
  ggplot2::labs(
    title="DETECT Screening Rate by Study Month",
    x= "Study Month", 
    y = "Screening Rate (% of Responses)",
    #### Add the lowest rate month(s) in the caption.
    caption = paste0(
      "Minimum rate at month(s): ", 
      paste(plot_df[plot_df$min_point,]$month, collapse = ', ')
      )
    )

## Save plot
ggplot2::ggsave(
  filename = paste0(
    plot_path,
    'f4-1-screen-rate-month.png'
    ),
  plot = plot
  )

## Display plot
plot
```

### Screening Results, by Month

We examined the count and percent of our overall screening completion, as well as positive and negative results of screenings. A positive screening was defined as at least one "yes" response to a DETECT item question.

#### Figure 4.2: Counts (#sec4-f2-result-month-count)

We examined our screening counts per month, by result type.

```{r}
#| label: sec4-f2-result-month-count-plot
# Plotting Screening Count per Month
## Extract data frame for the plot
plot_df <- screening_freqs |>
  ### Filter to omit "missing" as a value for this plot
  dplyr::filter(!response %in% c('missing')) |>
  ### Apply group variable labels/order
    dplyr::mutate(
      response = factor(
        response, 
        levels = names(screen_result_list), 
        labels = as.character(screen_result_list)
        )
      )

## Make Plot
plot <- ggplot2::ggplot(
  data = plot_df, 
  ggplot2::aes(x = month, y = n, fill = response)
  ) + 
  ### Ribbon to use lines that fill the area under the line
  ggplot2::geom_ribbon(ggplot2::aes(ymin = 0, ymax = n, fill = response)) +
  ### Labels
  ggplot2::labs(
    title="DETECT Screening Count by Study Month",
    x= "Study Month", 
    y = "Screening Count",
    fill = "Screening Result Type"
    ) +
  ### Color Palette
  ggplot2::scale_fill_brewer(palette = "Paired")

## Save plot
ggplot2::ggsave(
  filename = paste0(
    plot_path,
    'f4-2-result-month-count.png'
    ),
  plot = plot
  )

## Display plot
plot
```

#### Figure 4.3: Rates, Per Completed Screenings (#sec4-f3-result-month-per-comp)

We examined our screening result rates per month, by result type.

```{r}
#| label: sec4-f3-result-month-per-comp-plot
# Plotting Screening Result Frequency per Month, Completed Screenings
## Extract data frame for the plot
plot_df <- screening_freqs |>
  ### Filter to omit "missing" or "total" values for this plot
  dplyr::filter(!response %in% c('missing', 'completed')) |>
  ### Apply group variable labels/order
    dplyr::mutate(
      response = factor(
        response, 
        levels = names(screen_result_list), 
        labels = as.character(screen_result_list)
        )
      )

## Create plot
plot <- ggplot2::ggplot(
  data = plot_df, 
  ggplot2::aes(x = month, y = per_comp, fill = response)
  ) + 
  ## Convert y-axis scale to a percent
  ggplot2::scale_y_continuous(labels = scales::percent) +
  ### Stacked area plot
  ggplot2::geom_area(alpha = 0.8) +
  ### Labels
  ggplot2::labs(
    title="DETECT Screening Result Rates, by Month",
    x= "Study Month", 
    y = "Screening Rate (% of Screenings)",
    fill = "Screening Result Type"
    ) +
  ### Color Palette
  ggplot2::scale_fill_brewer(palette = "Paired")

## Save plot
ggplot2::ggsave(
  filename = paste0(
    plot_path,
    'f4-3-result-month-per-comp.png'
    ),
  plot = plot
  )

## Display plot
plot
```

#### Figure 4.4: Rates, Per All Responses (#sec4-f4-result-month-per-total)

We examined our screening result rates per month, by result type, for all responses (including no screening).

```{r}
#| label: sec4-f4-result-month-per-comp-plot
# Plotting Screening Result Frequency per Month, All Responses
## Extract data frame for the plot
plot_df <- screening_freqs |>
  ### Filter to omit "total" value for this plot
  dplyr::filter(!response %in% c('completed')) |>
  ### Apply group variable labels/order
    dplyr::mutate(
      response = factor(
        response, 
        levels = names(screen_result_list), 
        labels = as.character(screen_result_list)
        )
      )

## Create plot
plot <- ggplot2::ggplot(
  data = plot_df, 
  ggplot2::aes(x = month, y = per_total, fill = response)
  ) + 
  ## Convert y-axis scale to a percent
  ggplot2::scale_y_continuous(labels = scales::percent) +
  ### Stacked area plot
  ggplot2::geom_area(alpha = 0.8) +
  ### Labels
  ggplot2::labs(
    title="DETECT Screening Result Rates, by Month",
    subtitle = "All Responses, including missing screenings",
    x= "Study Month", 
    y = "Screening Rate (% of Responses)",
    fill = "Screening Result Type"
    ) +
  ### Color Palette
  ggplot2::scale_fill_brewer(palette = "Paired")

## Save plot
ggplot2::ggsave(
  filename = paste0(
    plot_path,
    'f4-4-result-month-per-total.png'
    ),
  plot = plot
  )

## Display plot
plot
```

### Initial Exploration of DETECT Item Response Patterns, by Month

#### All Responses

##### Figure 4.5: Item Completion Rates, All Responses (#sec4-f5-item-comp-all-month)

We extracted the item completion and value patterns of each DETECT tool item, for all responses each month. This included non-screened responses.

```{r}
#| label: sec4-item-comp-all-month-calc
# Get Screening Completion & Result Rates, by Month, all responses
## Calculate frequency of responses in all DETECT Tool Questions, per month
## Includes completion rate calculations
dt_freqs <- get_freq_grouped(
  .df = ms_records |>
    ### Reduce to month and DETECT Tool Items
    dplyr::select(month, dplyr::all_of(names(dt_item_list))) |>
    ### Convert missing values in DETECT Tool items to "missing"
    dplyr::mutate(
      dplyr::across(
        dplyr::all_of(names(dt_item_list)), 
        ~ifelse(is.na(.x), 'missing', .x)
        )
    ),
  .group_var = 'month',
  .item_list = dt_item_list,
  .val_order = dt_item_vals[names(dt_item_vals) != 'completed']
  ) |>
  ### Convert month to a numeric, for plot
  dplyr::mutate(month = as.numeric(month)) |>
  ### Add Variable Label, Response Label, Subset (character), Subset Title
  ### to facilitate loop processing in groups
  dplyr::mutate(
    var_label = factor(
      var_name,
      levels = names(dt_item_list),
      labels = as.character(dt_item_list)
      ),
    response_label = factor(
      response,
      levels = names(dt_item_vals),
      labels = as.character(dt_item_vals)
    ),
    subset = dplyr::case_when(
      stringr::str_detect(var_name, '_env_') ~'env',
      stringr::str_detect(var_name, '_pt_') ~'pt',
      stringr::str_detect(var_name, '_cg') ~'cg'
      ),
    subset_title = subset,
    subset_title = factor(
      subset_title, 
      levels = names(dt_cat_labels), 
      labels = as.character(dt_cat_labels)
      )
    )
```

We generated our plots. We plotted DETECT Items by broader categories (Environmental, Patient Condition, Caregiver) for visibility.

```{r}
#| label: sec4-f5-item-comp-all-month-rate-plot
# Plot DETECT Item Completion Rate by Month, all responses
## Extract Plot Data Frame
plot_df <- dt_freqs |>
  ## Reduce to completion rate values
  dplyr::filter(response %in% c("completed"))

## Create plots for the 3 groups
### Create list to hold plots as they are generated
plots <- list()
groups <- names(dt_cat_labels)
palette_order <- c("Paired", "Accent", "Spectral")

### Create each plot and add to list
for (i in seq(1, length(groups))){
  
  plots[[i]] <- ggplot2::ggplot(
    data = plot_df |>
      ## Reduce to selected DETECT Category
      dplyr::filter(subset == groups[i]),
    ggplot2::aes(x = month, y = per_total, color = var_label)
    ) +
    ggplot2::geom_line() +
    #### Convert y-axis scale to a percent
    ggplot2::scale_y_continuous(labels = scales::percent) +
    #### Labels
    ggplot2::labs(
      title = as.character(dt_cat_labels[groups[i]]),
      x= "Study Month", 
      y = "Completion Rate (% of Responses)",
      col = as.character(dt_cat_labels[groups[i]])
      ) +
    #### Set colors
    ggplot2::scale_color_brewer(palette=palette_order[i])
}

### Use Patchwork to wrap plots into a unified graphic
plot <- patchwork::wrap_plots(
  plots[1:length(groups)]
  ) + 
  patchwork::plot_annotation(
    title = 'DETECT Item Completion Rate, by Month',
    subtitle = "All responses, includes responses with no screening"
    ) + 
  patchwork::plot_layout(guides = 'collect', axes = 'collect') &
  ggplot2::theme(plot.title = ggplot2::element_text(size = 10))

## Save plot
ggplot2::ggsave(
  filename = paste0(
    plot_path,
    'f4-5-item-comp-all-month-rate.png'
    ),
  plot = plot
  )

## Display plot
plot
```

##### Figure 4.6: Environment Items Response Patterns by Month, All Responses (#sec4-f6-item-pat-all-env-month)

We created plots exploring the response patterns for the Environment Questions across all responses, including responses without a screening.

```{r}
#| label: sec4-f6-item-pat-all-env-month-plot
# Plot DETECT Item Response Patterns, Environment Questions, All Responses
## Extract Plot Data Frame
plot_df <- dt_freqs |>
  ## Remove "completed" value, as individual responses will fill this
  dplyr::filter(!response %in% c("completed"))

## Create plots for each item in the section
### Create list to hold plots as they are generated
plots <- list()
cat_label <- as.character(dt_cat_labels$env)
subset_items <- dt_item_list[stringr::str_detect(names(dt_item_list), 'env')]
palette_order <- rep("Paired", length(subset_items))

### Create each plot and add to list
for (i in seq(1, length(names(subset_items)))){
  
  plots[[i]] <- ggplot2::ggplot(
    data = plot_df |>
      ## Reduce to selected DETECT item
      dplyr::filter(var_name == names(subset_items)[i]),
    ggplot2::aes(x = month, y = per_total, fill = response_label)
    ) +
    ### Stacked area plot
    ggplot2::geom_area(alpha = 0.8) +
    #### Convert y-axis scale to a percent
    ggplot2::scale_y_continuous(labels = scales::percent) +
    #### Labels
    ggplot2::labs(
      title = as.character(subset_items[i]),
      x= "Study Month", 
      y = "Response Rate (% of Responses)",
      fill = "Item Response"
      ) +
    #### Set colors
    ggplot2::scale_fill_brewer(palette=palette_order[i])
}

### Use Patchwork to wrap plots into a unified graphic
plot <- patchwork::wrap_plots(
  plots[1:length(names(subset_items))]
  ) + 
  patchwork::plot_annotation(
    title = "DETECT Item Response Patterns, by Month",
    subtitle = cat_label
    ) + 
  patchwork::plot_layout(guides = 'collect', axes = 'collect') &
  ggplot2::theme(plot.title = ggplot2::element_text(size = 10))

## Save plot
ggplot2::ggsave(
  filename = paste0(
    plot_path,
    'f4-6-item-pat-all-env-month.png'
    ),
  plot = plot
  )

## Display plot
plot
```

##### Figure 4.7: Patient Question Items Response Patterns by Month, All Responses (#sec4-f7-item-pat-all-pt-month)

We created plots exploring the response patterns for the Patient Questions across all responses, including responses without a screening.

```{r}
#| label: sec4-f7-item-pat-all-pt-month-plot
# Plot DETECT Item Response Patterns, Patient Questions, All Responses
## Extract Plot Data Frame
plot_df <- dt_freqs |>
  ## Remove "completed" value, as individual responses will fill this
  dplyr::filter(!response %in% c("completed"))

## Create plots for each item in the section
### Create list to hold plots as they are generated
plots <- list()
cat_label <- as.character(dt_cat_labels$pt)
subset_items <- dt_item_list[stringr::str_detect(names(dt_item_list), 'pt')]
palette_order <- rep("Paired", length(subset_items))

### Create each plot and add to list
for (i in seq(1, length(names(subset_items)))){
  
  plots[[i]] <- ggplot2::ggplot(
    data = plot_df |>
      ## Reduce to selected DETECT item
      dplyr::filter(var_name == names(subset_items)[i]),
    ggplot2::aes(x = month, y = per_total, fill = response_label)
    ) +
    ### Stacked area plot
    ggplot2::geom_area(alpha = 0.8) +
    #### Convert y-axis scale to a percent
    ggplot2::scale_y_continuous(labels = scales::percent) +
    #### Labels
    ggplot2::labs(
      title = as.character(subset_items[i]),
      x= "Study Month", 
      y = "Response Rate (% of Responses)",
      fill = "Item Response"
      ) +
    #### Set colors
    ggplot2::scale_fill_brewer(palette=palette_order[i])
}

### Use Patchwork to wrap plots into a unified graphic
plot <- patchwork::wrap_plots(
  plots[1:length(names(subset_items))]
  ) + 
  patchwork::plot_annotation(
    title = "DETECT Item Response Patterns, by Month",
    subtitle = cat_label
    ) + 
  patchwork::plot_layout(guides = 'collect', axes = 'collect') &
  ggplot2::theme(plot.title = ggplot2::element_text(size = 10))

## Save plot
ggplot2::ggsave(
  filename = paste0(
    plot_path,
    'f4-7-item-pat-all-pt-month.png'
    ),
  plot = plot
  )

## Display plot
plot
```

##### Figure 4.8: Caregiver Question Items Response Patterns by Month, All Responses (#sec4-f8-item-pat-all-cg-month)

We created plots exploring the response patterns for the Caregiver Questions across all responses, including responses without a screening.

```{r}
#| label: sec4-f8-item-pat-all-cg-month-plot
# Plot DETECT Item Response Patterns, Caregiver Questions, All Responses
## Extract Plot Data Frame
plot_df <- dt_freqs |>
  ## Remove "completed" value, as individual responses will fill this
  dplyr::filter(!response %in% c("completed"))

## Create plots for each item in the section
### Create list to hold plots as they are generated
plots <- list()
cat_label <- as.character(dt_cat_labels$cg)
subset_items <- dt_item_list[stringr::str_detect(names(dt_item_list), 'cg')]
palette_order <- rep("Paired", length(subset_items))

### Create each plot and add to list
for (i in seq(1, length(names(subset_items)))){
  
  plots[[i]] <- ggplot2::ggplot(
    data = plot_df |>
      ## Reduce to selected DETECT item
      dplyr::filter(var_name == names(subset_items)[i]),
    ggplot2::aes(x = month, y = per_total, fill = response_label)
    ) +
    ### Stacked area plot
    ggplot2::geom_area(alpha = 0.8) +
    #### Convert y-axis scale to a percent
    ggplot2::scale_y_continuous(labels = scales::percent) +
    #### Labels
    ggplot2::labs(
      title = as.character(subset_items[i]),
      x= "Study Month", 
      y = "Response Rate (% of Responses)",
      fill = "Item Response"
      ) +
    #### Set colors
    ggplot2::scale_fill_brewer(palette=palette_order[i])
}

### Use Patchwork to wrap plots into a unified graphic
plot <- patchwork::wrap_plots(
  plots[1:length(names(subset_items))]
  ) + 
  patchwork::plot_annotation(
    title = "DETECT Item Response Patterns, by Month",
    subtitle = cat_label
    ) + 
  patchwork::plot_layout(guides = 'collect', axes = 'collect') &
  ggplot2::theme(plot.title = ggplot2::element_text(size = 10))

## Save plot
ggplot2::ggsave(
  filename = paste0(
    plot_path,
    'f4-8-item-pat-all-cg-month.png'
    ),
  plot = plot
  )

## Display plot
plot
```

#### All Screenings

##### Figure 4.9: Item Completion Rates, All Screenings (#sec4f-9-item-comp-scr-month)

We extracted the item completion and value patterns of each DETECT tool item, for all screenings each month. This excluded responses that did not have a screening.

```{r}
#| label: sec4-item-comp-scr-month-calc
# Get Screening Completion & Result Rates, by Month, All Screenings
## Calculate frequency of responses in all DETECT Tool Questions, per month
## Includes completion rate calculations
dt_freqs <- get_freq_grouped(
  .df = ms_records |>
    ### Reduce to SCREENINGS
    dplyr::mutate(dt_screened) |>
    ### Reduce to month and DETECT Tool Items
    dplyr::select(month, dplyr::all_of(names(dt_item_list))) |>
    ### Convert missing values in DETECT Tool items to "missing"
    dplyr::mutate(
      dplyr::across(
        dplyr::all_of(names(dt_item_list)), 
        ~ifelse(is.na(.x), 'missing', .x)
        )
    ),
  .group_var = 'month',
  .item_list = dt_item_list,
  .val_order = dt_item_vals[names(dt_item_vals) != 'completed']
  ) |>
  ### Convert month to a numeric, for plot
  dplyr::mutate(month = as.numeric(month)) |>
  ### Add Variable Label, Response Label, Subset (character), Subset Title
  ### to facilitate loop processing in groups
  dplyr::mutate(
    var_label = factor(
      var_name,
      levels = names(dt_item_list),
      labels = as.character(dt_item_list)
      ),
    response_label = factor(
      response,
      levels = names(dt_item_vals),
      labels = as.character(dt_item_vals)
    ),
    subset = dplyr::case_when(
      stringr::str_detect(var_name, '_env_') ~'env',
      stringr::str_detect(var_name, '_pt_') ~'pt',
      stringr::str_detect(var_name, '_cg') ~'cg'
      ),
    subset_title = subset,
    subset_title = factor(
      subset_title, 
      levels = names(dt_cat_labels), 
      labels = as.character(dt_cat_labels)
      )
    )
```

We generated our plots. We plotted DETECT Items by broader categories (Environmental, Patient Condition, Caregiver) for visibility.

```{r}
#| label: sec4f-9-item-comp-scr-month-rate-plot
# Plot DETECT Item Completion Rate by Month, All Screenings
## Extract Plot Data Frame
plot_df <- dt_freqs |>
  ## Reduce to completion rate values
  dplyr::filter(response %in% c("completed"))

## Create plots for the 3 groups
### Create list to hold plots as they are generated
plots <- list()
groups <- names(dt_cat_labels)
palette_order <- c("Paired", "Accent", "Spectral")

### Create each plot and add to list
for (i in seq(1, length(groups))){
  
  plots[[i]] <- ggplot2::ggplot(
    data = plot_df |>
      ## Reduce to selected DETECT Category
      dplyr::filter(subset == groups[i]),
    ggplot2::aes(x = month, y = per_total, color = var_label)
    ) +
    ggplot2::geom_line() +
    #### Convert y-axis scale to a percent
    ggplot2::scale_y_continuous(labels = scales::percent) +
    #### Labels
    ggplot2::labs(
      title = as.character(dt_cat_labels[groups[i]]),
      x= "Study Month", 
      y = "Completion Rate (% of Screenings)",
      col = as.character(dt_cat_labels[groups[i]])
      ) +
    #### Set colors
    ggplot2::scale_color_brewer(palette=palette_order[i])
}

### Use Patchwork to wrap plots into a unified graphic
plot <- patchwork::wrap_plots(
  plots[1:length(groups)]
  ) + 
  patchwork::plot_annotation(
    title = 'DETECT Item Completion Rate, by Month',
    subtitle = "All screenings"
    ) + 
  patchwork::plot_layout(guides = 'collect', axes = 'collect') &
  ggplot2::theme(plot.title = ggplot2::element_text(size = 10))

## Save plot
ggplot2::ggsave(
  filename = paste0(
    plot_path,
    'f4-9-item-comp-all-month-rate.png'
    ),
  plot = plot
  )

## Display plot
plot
```

##### Figure 4.10: Environment Items Response Patterns by Month, All Screenings (#sec4f-10-item-pat-scr-env-month)

We created plots exploring the response patterns for the Environment Questions across all responses, including responses without a screening.

```{r}
#| label: sec4f-10-item-pat-scr-env-month-plot
# Plot DETECT Item Response Patterns, Environment Questions, All Screenings
## Extract Plot Data Frame
plot_df <- dt_freqs |>
  ## Remove "completed" value, as individual responses will fill this
  dplyr::filter(!response %in% c("completed"))

## Create plots for each item in the section
### Create list to hold plots as they are generated
plots <- list()
cat_label <- as.character(dt_cat_labels$env)
subset_items <- dt_item_list[stringr::str_detect(names(dt_item_list), 'env')]
palette_order <- rep("Paired", length(subset_items))

### Create each plot and add to list
for (i in seq(1, length(names(subset_items)))){
  
  plots[[i]] <- ggplot2::ggplot(
    data = plot_df |>
      ## Reduce to selected DETECT item
      dplyr::filter(var_name == names(subset_items)[i]),
    ggplot2::aes(x = month, y = per_total, fill = response_label)
    ) +
    ### Stacked area plot
    ggplot2::geom_area(alpha = 0.8) +
    #### Convert y-axis scale to a percent
    ggplot2::scale_y_continuous(labels = scales::percent) +
    #### Labels
    ggplot2::labs(
      title = as.character(subset_items[i]),
      x= "Study Month", 
      y = "Response Rate (% of Screenings)",
      fill = "Item Response"
      ) +
    #### Set colors
    ggplot2::scale_fill_brewer(palette=palette_order[i])
}

### Use Patchwork to wrap plots into a unified graphic
plot <- patchwork::wrap_plots(
  plots[1:length(names(subset_items))]
  ) + 
  patchwork::plot_annotation(
    title = "DETECT Item Response Patterns, by Month",
    subtitle = cat_label
    ) + 
  patchwork::plot_layout(guides = 'collect', axes = 'collect') &
  ggplot2::theme(plot.title = ggplot2::element_text(size = 10))

## Save plot
ggplot2::ggsave(
  filename = paste0(
    plot_path,
    'f4-10-item-pat-scr-env-month.png'
    ),
  plot = plot
  )

## Display plot
plot
```

##### Figure 4.11: Patient Question Items Response Patterns by Month, All Screenings (#sec4f-11-item-pat-scr-pt-month)

We created plots exploring the response patterns for the Patient Questions across all responses, including responses without a screening.

```{r}
#| label: sec4f-11-item-pat-scr-pt-month-plot
# Plot DETECT Item Response Patterns, Patient Questions, All Screenings
## Extract Plot Data Frame
plot_df <- dt_freqs |>
  ## Remove "completed" value, as individual responses will fill this
  dplyr::filter(!response %in% c("completed"))

## Create plots for each item in the section
### Create list to hold plots as they are generated
plots <- list()
cat_label <- as.character(dt_cat_labels$pt)
subset_items <- dt_item_list[stringr::str_detect(names(dt_item_list), 'pt')]
palette_order <- rep("Paired", length(subset_items))

### Create each plot and add to list
for (i in seq(1, length(names(subset_items)))){
  
  plots[[i]] <- ggplot2::ggplot(
    data = plot_df |>
      ## Reduce to selected DETECT item
      dplyr::filter(var_name == names(subset_items)[i]),
    ggplot2::aes(x = month, y = per_total, fill = response_label)
    ) +
    ### Stacked area plot
    ggplot2::geom_area(alpha = 0.8) +
    #### Convert y-axis scale to a percent
    ggplot2::scale_y_continuous(labels = scales::percent) +
    #### Labels
    ggplot2::labs(
      title = as.character(subset_items[i]),
      x= "Study Month", 
      y = "Response Rate (% of Screenings)",
      fill = "Item Response"
      ) +
    #### Set colors
    ggplot2::scale_fill_brewer(palette=palette_order[i])
}

### Use Patchwork to wrap plots into a unified graphic
plot <- patchwork::wrap_plots(
  plots[1:length(names(subset_items))]
  ) + 
  patchwork::plot_annotation(
    title = "DETECT Item Response Patterns, by Month",
    subtitle = cat_label
    ) + 
  patchwork::plot_layout(guides = 'collect', axes = 'collect') &
  ggplot2::theme(plot.title = ggplot2::element_text(size = 10))

## Save plot
ggplot2::ggsave(
  filename = paste0(
    plot_path,
    'f4-11-item-pat-scr-pt-month.png'
    ),
  plot = plot
  )

## Display plot
plot
```

##### Figure 4.12: Caregiver Question Items Response Patterns by Month, All Screenings (#sec4f-12-item-pat-scr-cg-month)

We created plots exploring the response patterns for the Caregiver Questions across all responses, including responses without a screening.

```{r}
#| label: sec4f-12-item-pat-scr-cg-month-plot
# Plot DETECT Item Response Patterns, Caregiver Questions, All Screenings
## Extract Plot Data Frame
plot_df <- dt_freqs |>
  ## Remove "completed" value, as individual responses will fill this
  dplyr::filter(!response %in% c("completed"))

## Create plots for each item in the section
### Create list to hold plots as they are generated
plots <- list()
cat_label <- as.character(dt_cat_labels$cg)
subset_items <- dt_item_list[stringr::str_detect(names(dt_item_list), 'cg')]
palette_order <- rep("Paired", length(subset_items))

### Create each plot and add to list
for (i in seq(1, length(names(subset_items)))){
  
  plots[[i]] <- ggplot2::ggplot(
    data = plot_df |>
      ## Reduce to selected DETECT item
      dplyr::filter(var_name == names(subset_items)[i]),
    ggplot2::aes(x = month, y = per_total, fill = response_label)
    ) +
    ### Stacked area plot
    ggplot2::geom_area(alpha = 0.8) +
    #### Convert y-axis scale to a percent
    ggplot2::scale_y_continuous(labels = scales::percent) +
    #### Labels
    ggplot2::labs(
      title = as.character(subset_items[i]),
      x= "Study Month", 
      y = "Response Rate (% of Screenings)",
      fill = "Item Response"
      ) +
    #### Set colors
    ggplot2::scale_fill_brewer(palette=palette_order[i])
}

### Use Patchwork to wrap plots into a unified graphic
plot <- patchwork::wrap_plots(
  plots[1:length(names(subset_items))]
  ) + 
  patchwork::plot_annotation(
    title = "DETECT Item Response Patterns, by Month",
    subtitle = cat_label
    ) + 
  patchwork::plot_layout(guides = 'collect', axes = 'collect') &
  ggplot2::theme(plot.title = ggplot2::element_text(size = 10))

## Save plot
ggplot2::ggsave(
  filename = paste0(
    plot_path,
    'f4-12-item-pat-scr-cg-month.png'
    ),
  plot = plot
  )

## Display plot
plot
```

##### Figure 4.13: Item "Yes" (Only Yes) Rates, All Screenings (#sec4f-13-item-yoy-scr-all-month)

We extracted the "Yes" patterns relating to each item of the DETECT tool, specifically if a "yes" response was or was not the only "yes" in a given screening, across all screenings each month.

```{r}
#| label: sec4-item-yoy-scr-all-month-calc
# Get the "Yes, Only Yes" pattern for each Item, for each Month
## Calculate using group response pattern functions
onlyyes_df <- dplyr::left_join(
  ### Get the total number of "Yes" responses for each item, by month
  get_freq_grouped(
    .df = ms_records |>
      #### Reduce to SCREENINGS
      dplyr::mutate(dt_screened) |>
      #### Reduce to month and DETECT Tool Items
      dplyr::select(month, dplyr::all_of(names(dt_item_list))) |>
      #### Convert missing values in DETECT Tool items to "missing"
      dplyr::mutate(
        dplyr::across(
          dplyr::all_of(names(dt_item_list)), 
          ~ifelse(is.na(.x), 'missing', .x)
          )
      ),
    .group_var = 'month',
    .item_list = dt_item_list,
    .val_order = dt_item_vals[names(dt_item_vals) != 'completed']
    ) |>
    #### Filter to "Yes" responses
    dplyr::filter(response == 'yes') |>
    #### Reduce to Month - VarName - Number of "Yes" Responses in Item
    dplyr::select(month, var_name, n) |>
    dplyr::rename_at("n", ~"total_yes"),
  ### Get total number of "Yes, Only Yes" responses for each item, by month
  get_freq_grouped(
    .df = ms_records |>
      #### Reduce to SCREENINGS
      dplyr::mutate(dt_screened) |>
      #### Reduce to screenings with only one "Yes" selected
      dplyr::filter(dt_num_pos == 1) |>
      #### Reduce to month and DETECT Tool Items
      dplyr::select(month, dplyr::all_of(names(dt_item_list))) |>
      #### Convert missing values in DETECT Tool items to "missing"
      dplyr::mutate(
        dplyr::across(
          dplyr::all_of(names(dt_item_list)), 
          ~ifelse(is.na(.x), 'missing', .x)
          )
      ),
    .group_var = 'month',
    .item_list = dt_item_list,
    .val_order = dt_item_vals[names(dt_item_vals) != 'completed']
    ) |>
    #### Filter to "Yes" responses
    dplyr::filter(response == 'yes') |>
    #### Reduce to Month - VarName - Number of "Yes, Only Yes" Responses
    dplyr::select(month, var_name, n) |>
    dplyr::rename_at("n", ~"only_yes"),
  by = c("month", "var_name")
  ) |>
  ### Calculate the number of "Yes"es that are NOT the only Yes for each Item
  dplyr::mutate(
    not_only_yes = total_yes - only_yes
    ) |>
  ### Pivot so each row is the "Num Yes (only)" or "Num Yes (Not only)"
  tidyr::pivot_longer(
    cols = c("only_yes", "not_only_yes"),
    names_to = "response",
    values_to = "n"
  ) |>
  ### Change labels for values of "YES (ONLY)" or "NOT YES (ONLY)" for plots
  dplyr::mutate(
    response = dplyr::case_when(
      response == "only_yes" ~ "Only Yes",
      response == "not_only_yes" ~ "Yes, but not the only Yes"
    ),
    ### Calculate the percentage of "Yes"es each count represents
    per_yes = n / total_yes
  ) |>
  ### Convert month to a numeric, for plot
  dplyr::mutate(month = as.numeric(month)) |>
  ### Add Variable Label, Response Label, Subset (character), Subset Title
  ### to facilitate loop processing in groups
  dplyr::mutate(
    var_label = factor(
      var_name,
      levels = names(dt_item_list),
      labels = as.character(dt_item_list)
      ),
    response_label = factor(
      response,
      levels = names(dt_item_vals),
      labels = as.character(dt_item_vals)
    ),
    subset = dplyr::case_when(
      stringr::str_detect(var_name, '_env_') ~'env',
      stringr::str_detect(var_name, '_pt_') ~'pt',
      stringr::str_detect(var_name, '_cg') ~'cg'
      ),
    subset_title = subset,
    subset_title = factor(
      subset_title, 
      levels = names(dt_cat_labels), 
      labels = as.character(dt_cat_labels)
      )
    )
```

We generated our plots. We plotted DETECT Items by broader categories (Environmental, Patient Condition, Caregiver) for visibility.

```{r}
#| label: sec4f-13-item-yoy-scr-all-month-plot
# Plot DETECT Item "Yes (only yes)" Rate by Month
## Extract Plot Data Frame
plot_df <- onlyyes_df |>
  ### Reduce to "Only Yes" items
  dplyr::filter(response == "Only Yes")

## Create plots for the 3 groups
### Create list to hold plots as they are generated
plots <- list()
groups <- names(dt_cat_labels)
palette_order <- c("Paired", "Accent", "Spectral")

### Create each plot and add to list
for (i in seq(1, length(groups))){
  
  plots[[i]] <- ggplot2::ggplot(
    data = plot_df |>
      ## Reduce to selected DETECT Category
      dplyr::filter(subset == groups[i]),
    ggplot2::aes(x = month, y = per_yes, color = var_label)
    ) +
    ggplot2::geom_line() +
    #### Convert y-axis scale to a percent
    ggplot2::scale_y_continuous(labels = scales::percent) +
    #### Labels
    ggplot2::labs(
      title = as.character(dt_cat_labels[groups[i]]),
      x= "Study Month", 
      y = paste0(
        "Frequency of Item being the only 'Yes' Response ",
        "(% of 'Yes' Responses)"
        ),
      col = as.character(dt_cat_labels[groups[i]])
      ) +
    #### Set colors
    ggplot2::scale_color_brewer(palette=palette_order[i])
}

### Use Patchwork to wrap plots into a unified graphic
plot <- patchwork::wrap_plots(
  plots[1:length(groups)]
  ) + 
  patchwork::plot_annotation(
    title = 'Yes (only yes) Frequency, by Month'
    ) + 
  patchwork::plot_layout(guides = 'collect', axes = 'collect') &
  ggplot2::theme(plot.title = ggplot2::element_text(size = 10))

## Save plot
ggplot2::ggsave(
  filename = paste0(
    plot_path,
    'f4-13-item-yoy-scr-all-month.png'
    ),
  plot = plot
  )

## Display plot
plot
```

##### Figure 4.14: Environmental Question Items "Yes" (Only Yes) Rates, All Screenings (#sec4f-14-item-yoy-scr-env-month)

We created plots exploring the "Yes (Only Yes)" pattern for the Environment Questions across all responses, including responses without a screening.

```{r}
#| label: sec4f-14-item-yoy-scr-env-month-plot
# Plot DETECT Item "Yes (Only Yes)", Environment Questions, All Screenings
## Extract Plot Data Frame
plot_df <- onlyyes_df

## Create plots for each item in the section
### Create list to hold plots as they are generated
plots <- list()
cat_label <- as.character(dt_cat_labels$env)
subset_items <- dt_item_list[stringr::str_detect(names(dt_item_list), 'env')]
palette_order <- rep("Paired", length(subset_items))

### Create each plot and add to list
for (i in seq(1, length(names(subset_items)))){
  
  plots[[i]] <- ggplot2::ggplot(
    data = plot_df |>
      ## Reduce to selected DETECT item
      dplyr::filter(var_name == names(subset_items)[i]),
    ggplot2::aes(x = month, y = per_yes, fill = response)
    ) +
    ### Stacked area plot
    ggplot2::geom_area(alpha = 0.8) +
    #### Convert y-axis scale to a percent
    ggplot2::scale_y_continuous(labels = scales::percent) +
    #### Labels
    ggplot2::labs(
      title = as.character(subset_items[i]),
      x= "Study Month", 
      y = paste0(
        "Frequency of Item being the only 'Yes' Response ",
        "(% of 'Yes' Responses)"
        ),
      fill = "Yes Type"
      ) +
    #### Set colors
    ggplot2::scale_fill_brewer(palette=palette_order[i])
}

### Use Patchwork to wrap plots into a unified graphic
plot <- patchwork::wrap_plots(
  plots[1:length(names(subset_items))]
  ) + 
  patchwork::plot_annotation(
    title = 'Yes (only yes) Frequency, by Month',
    subtitle = cat_label
    ) + 
  patchwork::plot_layout(guides = 'collect', axes = 'collect') &
  ggplot2::theme(plot.title = ggplot2::element_text(size = 10))

## Save plot
ggplot2::ggsave(
  filename = paste0(
    plot_path,
    'f4-14-item-yoy-scr-env-month.png'
    ),
  plot = plot
  )

## Display plot
plot
```

##### Figure 4.15: Patient Question Items "Yes" (Only Yes) Rates, All Screenings (#sec4f-15-item-yoy-scr-pt-month)

We created plots exploring the "Yes (Only Yes)" pattern for the Patient Questions across all responses, including responses without a screening.

```{r}
#| label: sec4f-15-item-yoy-scr-pt-month-plot
# Plot DETECT Item "Yes (Only Yes)", Patient Questions, All Screenings
## Extract Plot Data Frame
plot_df <- onlyyes_df

## Create plots for each item in the section
### Create list to hold plots as they are generated
plots <- list()
cat_label <- as.character(dt_cat_labels$env)
subset_items <- dt_item_list[stringr::str_detect(names(dt_item_list), 'pt')]
palette_order <- rep("Paired", length(subset_items))

### Create each plot and add to list
for (i in seq(1, length(names(subset_items)))){
  
  plots[[i]] <- ggplot2::ggplot(
    data = plot_df |>
      ## Reduce to selected DETECT item
      dplyr::filter(var_name == names(subset_items)[i]),
    ggplot2::aes(x = month, y = per_yes, fill = response)
    ) +
    ### Stacked area plot
    ggplot2::geom_area(alpha = 0.8) +
    #### Convert y-axis scale to a percent
    ggplot2::scale_y_continuous(labels = scales::percent) +
    #### Labels
    ggplot2::labs(
      title = as.character(subset_items[i]),
      x= "Study Month", 
      y = paste0(
        "Frequency of Item being the only 'Yes' Response ",
        "(% of 'Yes' Responses)"
        ),
      fill = "Yes Type"
      ) +
    #### Set colors
    ggplot2::scale_fill_brewer(palette=palette_order[i])
}

### Use Patchwork to wrap plots into a unified graphic
plot <- patchwork::wrap_plots(
  plots[1:length(names(subset_items))]
  ) + 
  patchwork::plot_annotation(
    title = 'Yes (only yes) Frequency, by Month',
    subtitle = cat_label
    ) + 
  patchwork::plot_layout(guides = 'collect', axes = 'collect') &
  ggplot2::theme(plot.title = ggplot2::element_text(size = 10))

## Save plot
ggplot2::ggsave(
  filename = paste0(
    plot_path,
    'f4-15-item-yoy-scr-pt-month.png'
    ),
  plot = plot
  )

## Display plot
plot
```

##### Figure 4.16: Caregiver Question Items "Yes" (Only Yes) Rates, All Screenings (#sec4f-16-item-yoy-scr-cg-month)

We created plots exploring the "Yes (Only Yes)" pattern for the Caregiver Questions across all responses, including responses without a screening.

```{r}
#| label: sec4f-16-item-yoy-scr-cg-month-plot
# Plot DETECT Item "Yes (Only Yes)", Caregiver Questions, All Screenings
## Extract Plot Data Frame
plot_df <- onlyyes_df

## Create plots for each item in the section
### Create list to hold plots as they are generated
plots <- list()
cat_label <- as.character(dt_cat_labels$env)
subset_items <- dt_item_list[stringr::str_detect(names(dt_item_list), 'cg')]
palette_order <- rep("Paired", length(subset_items))

### Create each plot and add to list
for (i in seq(1, length(names(subset_items)))){
  
  plots[[i]] <- ggplot2::ggplot(
    data = plot_df |>
      ## Reduce to selected DETECT item
      dplyr::filter(var_name == names(subset_items)[i]),
    ggplot2::aes(x = month, y = per_yes, fill = response)
    ) +
    ### Stacked area plot
    ggplot2::geom_area(alpha = 0.8) +
    #### Convert y-axis scale to a percent
    ggplot2::scale_y_continuous(labels = scales::percent) +
    #### Labels
    ggplot2::labs(
      title = as.character(subset_items[i]),
      x= "Study Month", 
      y = paste0(
        "Frequency of Item being the only 'Yes' Response ",
        "(% of 'Yes' Responses)"
        ),
      fill = "Yes Type"
      ) +
    #### Set colors
    ggplot2::scale_fill_brewer(palette=palette_order[i])
}

### Use Patchwork to wrap plots into a unified graphic
plot <- patchwork::wrap_plots(
  plots[1:length(names(subset_items))]
  ) + 
  patchwork::plot_annotation(
    title = 'Yes (only yes) Frequency, by Month',
    subtitle = cat_label
    ) + 
  patchwork::plot_layout(guides = 'collect', axes = 'collect') &
  ggplot2::theme(plot.title = ggplot2::element_text(size = 10))

## Save plot
ggplot2::ggsave(
  filename = paste0(
    plot_path,
    'f4-16-item-yoy-scr-cg-month.png'
    ),
  plot = plot
  )

## Display plot
plot
```

#### Reporting Intent Rates, by Month

##### Figure 4.17: Rates, Per All Responses (#sec4-f17-report-intent-month-per-total)

We examined our DETECT-recorded intent to report per month, by result type. We calculated these frequencies in aggregate (all screenings) and by result type (positive or negative).

```{r}
#| label: sec4-f17-report-intent-month-per-total-calc
# Get Reporting Intent Rates, Overall and By Result Type, by Month
## Extract a temporary data frame of columns for reporting intent plots
reporting_df <- ms_records |>
      #### Reduce to SCREENINGS
      dplyr::mutate(dt_screened) |>
      #### Reduce to month, screening result, and DETECT Tool report item
      dplyr::select(month, dt_positive, dt_aps_reported) |>
      #### Convert missing values in DETECT Tool report item to "missing"
      dplyr::mutate(
        dplyr::across(
          dplyr::all_of('dt_aps_reported'), 
          ~dplyr::case_when(
            .x ~ 'intent',
            !.x ~ 'no_intent',
            is.na(.x) ~ 'missing'
            )
          )
      )

## Get results for all screenings, positive screens, and negative screens
plot_dfs <- list(
  ### Get count and frequency for all screenings
  completed = get_freq_grouped(
    .df = reporting_df,
    .group_var = 'month',
    .item_list = list(dt_aps_reported = "Reporting Intent"),
    .val_order = report_intent_vals[names(report_intent_vals) != 'completed']
    ),
  ### Get count and frequency for positive screenings
  positive = get_freq_grouped(
    .df = reporting_df |>
      #### Reduce to POSITIVE Screenings
      dplyr::filter(dt_positive),
    .group_var = 'month',
    .item_list = list(dt_aps_reported = "Reporting Intent"),
    .val_order = report_intent_vals[names(report_intent_vals) != 'completed']
    ),
  ### Get count and frequency for negative screenings
  negative = get_freq_grouped(
    .df = reporting_df |>
      #### Reduce to NEGATIVE Screenings
      dplyr::filter(!dt_positive),
    .group_var = 'month',
    .item_list = list(dt_aps_reported = "Reporting Intent"),
    .val_order = report_intent_vals[names(report_intent_vals) != 'completed']
    )
  )

## Small modification of data frames
for (i in seq(1,length(plot_dfs))){
  plot_dfs[[
    rlang::sym(names(plot_dfs)[i])
    ]] <- plot_dfs[[rlang::sym(names(plot_dfs)[i])]] |>
    ### Convert month to a numeric, for plot. Label Reporting Intent Values
    dplyr::mutate(
      month = as.numeric(month),
      response_label = factor(
        response,
        levels = names(report_intent_vals),
        labels = as.character(report_intent_vals)
      )
    )
}
```

We generated our plots.

```{r}
#| label: sec4-f17-report-intent-month-per-total-plot
# Plot Reporting Intent Rates, Overall and By Result Type, by Month
## Create plots for each item in the section
### Create list to hold plots as they are generated
plots <- list()
subset_items <- screen_result_list[names(screen_result_list) != 'missing']
palette_order <- rep("Paired", length(subset_items))

### Create each plot and add to list
for (i in seq(1, length(names(subset_items)))){
  
  plots[[i]] <- ggplot2::ggplot(
    # Use the subset data frame
    data = plot_dfs[[rlang::sym(names(subset_items)[i])]] |>
      ### Remove "completed", as other values will add to this
      dplyr::filter(response != "completed"),
    ggplot2::aes(x = month, y = per_total, fill = response_label)
    ) +
    ### Stacked area plot
    ggplot2::geom_area(alpha = 0.8) +
    #### Convert y-axis scale to a percent
    ggplot2::scale_y_continuous(labels = scales::percent) +
    #### Labels
    ggplot2::labs(
      title = as.character(subset_items[i]),
      x= "Study Month", 
      y = "Frequency",
      fill = "DETECT Recorded Reporting Intent"
      ) +
    #### Set colors
    ggplot2::scale_fill_brewer(palette=palette_order[i])
}

### Use Patchwork to wrap plots into a unified graphic
plot <- patchwork::wrap_plots(
  plots[1:length(names(subset_items))]
  ) + 
  patchwork::plot_annotation(
    title = "DETECT Item Recorded Intent to Report, by Month"
    ) + 
  patchwork::plot_layout(guides = 'collect', axes = 'collect') &
  ggplot2::theme(plot.title = ggplot2::element_text(size = 10))

## Save plot
ggplot2::ggsave(
  filename = paste0(
    plot_path,
    'f4-17-report-intent-month-per-total.png'
    ),
  plot = plot
  )

## Display plot
plot
```

#### APS Intakes, by Month

##### Figure 4.18: Matched APS Intakes by Screening Result, Per Month, All Screenings (#sec4-f18-intake-month-per-result)

We examined our DETECT-recorded intent to report per month, by result type. We calculated these frequencies in aggregate (all screenings) and by result type (positive or negative).

```{r}
#| label: sec4-f18-intake-month-per-result-calc
# Get Reporting Intent Rates, Overall and By Result Type, by Month
## Extract a temporary data frame of columns for reporting intent plots
reporting_df <- ms_records |>
      #### Reduce to SCREENINGS
      dplyr::mutate(dt_screened) |>
      #### Reduce to month, DETECT Tool Result, and Intake Reporter Type
      dplyr::select(month, dt_positive, aps_intake_type) |>
      dplyr::mutate(
      #### Convert APS Intake Type categories to label-set values
         aps_intake_type = dplyr::case_when(
           aps_intake_type == "EMS (explicit)" ~ "ems",
           aps_intake_type == "EMS reasonable" ~ "poss",
           aps_intake_type == "Not likely to be EMS" ~ "any",
           TRUE ~ "missing"
         )
      )

## Get results for all screenings, positive screens, and negative screens
plot_dfs <- list(
  ### Get count and frequency for all screenings
  completed = get_freq_grouped(
    .df = reporting_df,
    .group_var = 'month',
    .item_list = list(aps_intake_type = "APS Intake Type"),
    .val_order = aps_intake_type_labels[
      names(aps_intake_type_labels) != 'completed'
      ]
    ),
  ### Get count and frequency for positive screenings
  positive = get_freq_grouped(
    .df = reporting_df |>
      #### Reduce to POSITIVE Screenings
      dplyr::filter(dt_positive),
    .group_var = 'month',
    .item_list = list(aps_intake_type = "APS Intake Type"),
    .val_order = aps_intake_type_labels[
      names(aps_intake_type_labels) != 'completed'
      ]
    ),
  ### Get count and frequency for negative screenings
  negative = get_freq_grouped(
    .df = reporting_df |>
      #### Reduce to NEGATIVE Screenings
      dplyr::filter(!dt_positive),
    .group_var = 'month',
    .item_list = list(aps_intake_type = "APS Intake Type"),
    .val_order = aps_intake_type_labels[
      names(aps_intake_type_labels) != 'completed'
      ]
    )
  )

## Small modification of data frames
for (i in seq(1,length(plot_dfs))){
  plot_dfs[[
    rlang::sym(names(plot_dfs)[i])
    ]] <- plot_dfs[[rlang::sym(names(plot_dfs)[i])]] |>
    ### Convert month to a numeric, for plot. Label Reporting Intent Values
    dplyr::mutate(
      month = as.numeric(month),
      response_label = factor(
        response,
        levels = names(aps_intake_type_labels),
        labels = as.character(aps_intake_type_labels)
      )
    )
}
```

We generated our plots.

```{r}
#| label: sec4-f18-intake-month-per-result-plot
# Plot Reporting Intent Rates, Overall and By Result Type, by Month
## Create plots for each item in the section
### Create list to hold plots as they are generated
plots <- list()
subset_items <- screen_result_list[names(screen_result_list) != 'missing']
palette_order <- rep("Paired", length(subset_items))

### Create each plot and add to list
for (i in seq(1,length(names(subset_items)))){
  
  plots[[i]] <- ggplot2::ggplot(
    # Use the subset data frame
    data = plot_dfs[[rlang::sym(names(subset_items)[i])]] |>
      ### Remove "completed", as other values will add to this
      dplyr::filter(response != "completed") |>
      dplyr::select(month, response, per_total, response_label),
    ggplot2::aes(x = month, y = per_total, fill = response_label)
    ) +
    ### Stacked area plot
    ggplot2::geom_area(alpha = 0.8) +
    #### Convert y-axis scale to a percent
    ggplot2::scale_y_continuous(labels = scales::percent) +
    #### Labels
    ggplot2::labs(
      title = as.character(subset_items[i]),
      x= "Study Month", 
      y = "Frequency",
      fill = "Matched APS Intake Type"
      ) +
    #### Set colors
    ggplot2::scale_fill_brewer(palette=palette_order[i])
}

### Use Patchwork to wrap plots into a unified graphic
plot <- patchwork::wrap_plots(
  plots[1:length(names(subset_items))]
  ) + 
  patchwork::plot_annotation(
    title = "Matched APS Intake Types, by Month"
    ) + 
  patchwork::plot_layout(guides = 'collect', axes = 'collect') &
  ggplot2::theme(plot.title = ggplot2::element_text(size = 10))

## Save plot
ggplot2::ggsave(
  filename = paste0(
    plot_path,
    'f4-18-intake-month-per-result.png'
    ),
  plot = plot
  )

## Display plot
plot
```

##### Figure 4.19: Matched APS Intakes by Reporting Intent, Per Month, All Screenings (#sec4-f19-intake-month-per-intent)

We examined our DETECT-recorded intent to report per month, by DETECT recorded reporting intent. We calculated these frequencies in aggregate (all screenings) and by reporting intent.

```{r}
#| label: sec4-f19-intake-month-per-intent-calc
# Get Reporting Intent Rates, Overall and By Result Type, by Month
## Extract a temporary data frame of columns for reporting intent plots
reporting_df <- ms_records |>
      #### Reduce to SCREENINGS
      dplyr::mutate(dt_screened) |>
      #### Reduce to month, DETECT Tool Intent, and Intake Reporter Type
      dplyr::select(month, dt_aps_reported, aps_intake_type) |>
      dplyr::mutate(
      #### Convert APS Intake Type categories to label-set values
         aps_intake_type = dplyr::case_when(
           aps_intake_type == "EMS (explicit)" ~ "ems",
           aps_intake_type == "EMS reasonable" ~ "poss",
           aps_intake_type == "Not likely to be EMS" ~ "any",
           TRUE ~ "missing"
         )
      )

## Get results for all screenings, positive screens, and negative screens
plot_dfs <- list(
  ### Get count and frequency for all screenings
  completed = get_freq_grouped(
    .df = reporting_df,
    .group_var = 'month',
    .item_list = list(aps_intake_type = "APS Intake Type"),
    .val_order = aps_intake_type_labels[
      names(aps_intake_type_labels) != 'completed'
      ]
    ),
  ### Get count and frequency for positive screenings
  intent = get_freq_grouped(
    .df = reporting_df |>
      #### Reduce to Screenings WITH intent to report
      dplyr::filter(dt_aps_reported),
    .group_var = 'month',
    .item_list = list(aps_intake_type = "APS Intake Type"),
    .val_order = aps_intake_type_labels[
      names(aps_intake_type_labels) != 'completed'
      ]
    ),
  ### Get count and frequency for negative screenings
  no_intent = get_freq_grouped(
    .df = reporting_df |>
      #### Reduce to Screenings WITHOUT intent to report
      dplyr::filter(!dt_aps_reported),
    .group_var = 'month',
    .item_list = list(aps_intake_type = "APS Intake Type"),
    .val_order = aps_intake_type_labels[
      names(aps_intake_type_labels) != 'completed'
      ]
    )
  )

## Small modification of data frames
for (i in seq(1,length(plot_dfs))){
  plot_dfs[[
    rlang::sym(names(plot_dfs)[i])
    ]] <- plot_dfs[[rlang::sym(names(plot_dfs)[i])]] |>
    ### Convert month to a numeric, for plot. Label Reporting Intent Values
    dplyr::mutate(
      month = as.numeric(month),
      response_label = factor(
        response,
        levels = names(aps_intake_type_labels),
        labels = as.character(aps_intake_type_labels)
      )
    )
}
```

We generated our plots.

```{r}
#| label: sec4-f19-intake-month-per-intent-plot
# Plot Reporting Intent Rates, Overall and By Result Type, by Month
## Create plots for each item in the section
### Create list to hold plots as they are generated
plots <- list()
subset_items <- report_intent_vals[names(report_intent_vals) != 'missing']
palette_order <- rep("Paired", length(report_intent_vals))

### Create each plot and add to list
for (i in seq(1,length(names(subset_items)))){
  
  plots[[i]] <- ggplot2::ggplot(
    # Use the subset data frame
    data = plot_dfs[[rlang::sym(names(subset_items)[i])]] |>
      ### Remove "completed", as other values will add to this
      dplyr::filter(response != "completed") |>
      dplyr::select(month, response, per_total, response_label),
    ggplot2::aes(x = month, y = per_total, fill = response_label)
    ) +
    ### Stacked area plot
    ggplot2::geom_area(alpha = 0.8) +
    #### Convert y-axis scale to a percent
    ggplot2::scale_y_continuous(labels = scales::percent) +
    #### Labels
    ggplot2::labs(
      title = as.character(subset_items[i]),
      x= "Study Month", 
      y = "Frequency",
      fill = "Matched APS Intake Type"
      ) +
    #### Set colors
    ggplot2::scale_fill_brewer(palette=palette_order[i])
}

### Use Patchwork to wrap plots into a unified graphic
plot <- patchwork::wrap_plots(
  plots[1:length(names(subset_items))]
  ) + 
  patchwork::plot_annotation(
    title = "Matched APS Intake Types, by Month"
    ) + 
  patchwork::plot_layout(guides = 'collect', axes = 'collect') &
  ggplot2::theme(plot.title = ggplot2::element_text(size = 10))

## Save plot
ggplot2::ggsave(
  filename = paste0(
    plot_path,
    'f4-19-intake-month-per-intent.png'
    ),
  plot = plot
  )

## Display plot
plot
```

#### APS Investigation Dispositions, by Month

##### Figure 4.20: Matched APS Investigations (Broad, Aggregate) by Screening Result, Per Month, All Screenings (#sec4-f20-dispo-broad-all-month-per-result)

We examined our DETECT-recorded intent to report per month, by result type. We calculated these frequencies in aggregate (all screenings) and by result type (positive or negative).

```{r}
#| label: sec4-f20-dispo-broad-all-month-per-result-calc
# Get Data
## Extract a temporary data frame of columns for reporting intent plots
reporting_df <- ms_records |>
      #### Reduce to SCREENINGS
      dplyr::mutate(dt_screened) |>
      #### Reduce to month, DETECT Tool Result, and Intake Reporter Type
      dplyr::select(month, dt_positive, aps_inv_window_dispo) |>
      #### Fill missing values for disposition
      dplyr::mutate(
      #### Convert APS Intake Type categories to label-set values
         aps_inv_window_dispo = ifelse(
           is.na(aps_inv_window_dispo), "missing", aps_inv_window_dispo
           )
      )

## Get results for all screenings, positive screens, and negative screens
plot_dfs <- list(
  ### Get count and frequency for all screenings
  completed = get_freq_grouped(
    .df = reporting_df,
    .group_var = 'month',
    .item_list = list(
      aps_inv_window_dispo = paste0(
        "APS Investigation Disposition (Broad, Aggregate)"
        )
      ),
    .val_order = aps_dispo_labels[
      names(aps_dispo_labels) != 'completed'
      ]
    ),
  ### Get count and frequency for positive screenings
  positive = get_freq_grouped(
    .df = reporting_df |>
      #### Reduce to POSITIVE Screenings
      dplyr::filter(dt_positive),
    .group_var = 'month',
    .item_list = list(
      aps_inv_window_dispo = paste0(
        "APS Investigation Disposition (Broad, Aggregate)"
        )
      ),
    .val_order = aps_dispo_labels[
      names(aps_dispo_labels) != 'completed'
      ]
    ),
  ### Get count and frequency for negative screenings
  negative = get_freq_grouped(
    .df = reporting_df |>
      #### Reduce to NEGATIVE Screenings
      dplyr::filter(!dt_positive),
    .group_var = 'month',
    .item_list = list(
      aps_inv_window_dispo = paste0(
        "APS Investigation Disposition (Broad, Aggregate)"
        )
      ),
    .val_order = aps_dispo_labels[
      names(aps_dispo_labels) != 'completed'
      ]
    )
  )

## Small modification of data frames
for (i in seq(1,length(plot_dfs))){
  plot_dfs[[
    rlang::sym(names(plot_dfs)[i])
    ]] <- plot_dfs[[rlang::sym(names(plot_dfs)[i])]] |>
    ### Convert month to a numeric, for plot. Label Reporting Intent Values
    dplyr::mutate(
      month = as.numeric(month),
      response_label = factor(
        response,
        levels = names(aps_dispo_labels),
        labels = as.character(aps_dispo_labels)
      )
    )
}
```

We generated our plots.

```{r}
#| label: sec4-f20-dispo-broad-all-month-per-result-plot
# Plot
## Create plots for each item in the section
### Create list to hold plots as they are generated
plots <- list()
subset_items <- screen_result_list[names(screen_result_list) != 'missing']
palette_order <- rep("Paired", length(subset_items))

### Create each plot and add to list
for (i in seq(1,length(names(subset_items)))){
  
  plots[[i]] <- ggplot2::ggplot(
    # Use the subset data frame
    data = plot_dfs[[rlang::sym(names(subset_items)[i])]] |>
      ### Remove "completed", as other values will add to this
      dplyr::filter(response != "completed") |>
      dplyr::select(month, response, per_total, response_label),
    ggplot2::aes(x = month, y = per_total, fill = response_label)
    ) +
    ### Stacked area plot
    ggplot2::geom_area(alpha = 0.8) +
    #### Convert y-axis scale to a percent
    ggplot2::scale_y_continuous(labels = scales::percent) +
    #### Labels
    ggplot2::labs(
      title = as.character(subset_items[i]),
      x= "Study Month", 
      y = "Frequency",
      fill = "Matched APS Intake Type"
      ) +
    #### Set colors
    ggplot2::scale_fill_brewer(palette=palette_order[i])
}

### Use Patchwork to wrap plots into a unified graphic
plot <- patchwork::wrap_plots(
  plots[1:length(names(subset_items))]
  ) + 
  patchwork::plot_annotation(
    title = "Matched APS Investigation Dispositions, by Month",
    subtitle = "Aggregated all matched investigations"
    ) + 
  patchwork::plot_layout(guides = 'collect', axes = 'collect') &
  ggplot2::theme(plot.title = ggplot2::element_text(size = 10))

## Save plot
ggplot2::ggsave(
  filename = paste0(
    plot_path,
    'f4-20-dispo-broad-all-month-per-result.png'
    ),
  plot = plot
  )

## Display plot
plot
```

##### Figure 4.21: Matched APS Investigations (Broad, "Best") by Screening Result, Per Month, All Screenings (#sec4-f21-dispo-broad-best-month-per-result)

We examined our DETECT-recorded intent to report per month, by result type. We calculated these frequencies from the single "best" matched investigation and by result type (positive or negative).

```{r}
#| label: sec4-f21-dispo-broad-best-month-per-result-calc
# Get Data
## Extract a temporary data frame of columns for reporting intent plots
reporting_df <- ms_records |>
      #### Reduce to SCREENINGS
      dplyr::mutate(dt_screened) |>
      #### Reduce to month, DETECT Tool Result, and Intake Reporter Type
      dplyr::select(month, dt_positive, aps_inv_window_dispo_best) |>
      #### Fill missing values for disposition
      dplyr::mutate(
      #### Convert APS Disposition Types to label-set values
         aps_inv_window_dispo_best = ifelse(
           is.na(aps_inv_window_dispo_best), 
           "missing", 
           aps_inv_window_dispo_best
           )
      )

## Get results for all screenings, positive screens, and negative screens
plot_dfs <- list(
  ### Get count and frequency for all screenings
  completed = get_freq_grouped(
    .df = reporting_df,
    .group_var = 'month',
    .item_list = list(
      aps_inv_window_dispo_best = paste0(
        "APS Investigation Disposition (Broad, Best)"
        )
      ),
    .val_order = aps_dispo_labels[
      names(aps_dispo_labels) != 'completed'
      ]
    ),
  ### Get count and frequency for positive screenings
  positive = get_freq_grouped(
    .df = reporting_df |>
      #### Reduce to POSITIVE Screenings
      dplyr::filter(dt_positive),
    .group_var = 'month',
    .item_list = list(
      aps_inv_window_dispo_best = paste0(
        "APS Investigation Disposition (Broad, Best)"
        )
      ),
    .val_order = aps_dispo_labels[
      names(aps_dispo_labels) != 'completed'
      ]
    ),
  ### Get count and frequency for negative screenings
  negative = get_freq_grouped(
    .df = reporting_df |>
      #### Reduce to NEGATIVE Screenings
      dplyr::filter(!dt_positive),
    .group_var = 'month',
    .item_list = list(
      aps_inv_window_dispo_best = paste0(
        "APS Investigation Disposition (Broad, Best)"
        )
      ),
    .val_order = aps_dispo_labels[
      names(aps_dispo_labels) != 'completed'
      ]
    )
  )

## Smbest modification of data frames
for (i in seq(1,length(plot_dfs))){
  plot_dfs[[
    rlang::sym(names(plot_dfs)[i])
    ]] <- plot_dfs[[rlang::sym(names(plot_dfs)[i])]] |>
    ### Convert month to a numeric, for plot. Label Reporting Intent Values
    dplyr::mutate(
      month = as.numeric(month),
      response_label = factor(
        response,
        levels = names(aps_dispo_labels),
        labels = as.character(aps_dispo_labels)
      )
    )
}
```

We generated our plots.

```{r}
#| label: sec4-f21-dispo-broad-best-month-per-result-plot
# Plot 
## Create plots for each item in the section
### Create list to hold plots as they are generated
plots <- list()
subset_items <- screen_result_list[names(screen_result_list) != 'missing']
palette_order <- rep("Paired", length(subset_items))

### Create each plot and add to list
for (i in seq(1,length(names(subset_items)))){
  
  plots[[i]] <- ggplot2::ggplot(
    # Use the subset data frame
    data = plot_dfs[[rlang::sym(names(subset_items)[i])]] |>
      ### Remove "completed", as other values will add to this
      dplyr::filter(response != "completed") |>
      dplyr::select(month, response, per_total, response_label),
    ggplot2::aes(x = month, y = per_total, fill = response_label)
    ) +
    ### Stacked area plot
    ggplot2::geom_area(alpha = 0.8) +
    #### Convert y-axis scale to a percent
    ggplot2::scale_y_continuous(labels = scales::percent) +
    #### Labels
    ggplot2::labs(
      title = as.character(subset_items[i]),
      x= "Study Month", 
      y = "Frequency",
      fill = "Matched APS Intake Type"
      ) +
    #### Set colors
    ggplot2::scale_fill_brewer(palette=palette_order[i])
}

### Use Patchwork to wrap plots into a unified graphic
plot <- patchwork::wrap_plots(
  plots[1:length(names(subset_items))]
  ) + 
  patchwork::plot_annotation(
    title = "Matched APS Investigation Dispositions, by Month",
    subtitle = 'Single "Best" Matching Investigation'
    ) + 
  patchwork::plot_layout(guides = 'collect', axes = 'collect') &
  ggplot2::theme(plot.title = ggplot2::element_text(size = 10))

## Save plot
ggplot2::ggsave(
  filename = paste0(
    plot_path,
    'f4-21-dispo-broad-best-month-per-result.png'
    ),
  plot = plot
  )

## Display plot
plot
```

##### Figure 4.22: Matched APS Investigations (Exact, Aggregate) by Screening Result, Per Month, All Screenings (#sec4-f22-dispo-exact-all-month-per-result)

We examined our DETECT-recorded intent to report per month, by result type. We calculated these frequencies in aggregate (all screenings) and by result type (positive or negative).

```{r}
#| label: sec4-f22-dispo-exact-all-month-per-result-calc
# Get Data
## Extract a temporary data frame of columns for reporting intent plots
reporting_df <- ms_records |>
      #### Reduce to SCREENINGS
      dplyr::mutate(dt_screened) |>
      #### Reduce to month, DETECT Tool Result, and Intake Reporter Type
      dplyr::select(month, dt_positive, aps_inv_exact_dispo) |>
      #### Fill missing values for disposition
      dplyr::mutate(
      #### Convert APS Intake Type categories to label-set values
         aps_inv_exact_dispo = ifelse(
           is.na(aps_inv_exact_dispo), "missing", aps_inv_exact_dispo
           )
      )

## Get results for all screenings, positive screens, and negative screens
plot_dfs <- list(
  ### Get count and frequency for all screenings
  completed = get_freq_grouped(
    .df = reporting_df,
    .group_var = 'month',
    .item_list = list(
      aps_inv_exact_dispo = paste0(
        "APS Investigation Disposition (Exact, Aggregate)"
        )
      ),
    .val_order = aps_dispo_labels[
      names(aps_dispo_labels) != 'completed'
      ]
    ),
  ### Get count and frequency for positive screenings
  positive = get_freq_grouped(
    .df = reporting_df |>
      #### Reduce to POSITIVE Screenings
      dplyr::filter(dt_positive),
    .group_var = 'month',
    .item_list = list(
      aps_inv_exact_dispo = paste0(
        "APS Investigation Disposition (Exact, Aggregate)"
        )
      ),
    .val_order = aps_dispo_labels[
      names(aps_dispo_labels) != 'completed'
      ]
    ),
  ### Get count and frequency for negative screenings
  negative = get_freq_grouped(
    .df = reporting_df |>
      #### Reduce to NEGATIVE Screenings
      dplyr::filter(!dt_positive),
    .group_var = 'month',
    .item_list = list(
      aps_inv_exact_dispo = paste0(
        "APS Investigation Disposition (Exact, Aggregate)"
        )
      ),
    .val_order = aps_dispo_labels[
      names(aps_dispo_labels) != 'completed'
      ]
    )
  )

## Small modification of data frames
for (i in seq(1,length(plot_dfs))){
  plot_dfs[[
    rlang::sym(names(plot_dfs)[i])
    ]] <- plot_dfs[[rlang::sym(names(plot_dfs)[i])]] |>
    ### Convert month to a numeric, for plot. Label Reporting Intent Values
    dplyr::mutate(
      month = as.numeric(month),
      response_label = factor(
        response,
        levels = names(aps_dispo_labels),
        labels = as.character(aps_dispo_labels)
      )
    )
}
```

We generated our plots.

```{r}
#| label: sec4-f22-dispo-exact-all-month-per-result-plot
# Plot
## Create plots for each item in the section
### Create list to hold plots as they are generated
plots <- list()
subset_items <- screen_result_list[names(screen_result_list) != 'missing']
palette_order <- rep("Paired", length(subset_items))

### Create each plot and add to list
for (i in seq(1,length(names(subset_items)))){
  
  plots[[i]] <- ggplot2::ggplot(
    # Use the subset data frame
    data = plot_dfs[[rlang::sym(names(subset_items)[i])]] |>
      ### Remove "completed", as other values will add to this
      dplyr::filter(response != "completed") |>
      dplyr::select(month, response, per_total, response_label),
    ggplot2::aes(x = month, y = per_total, fill = response_label)
    ) +
    ### Stacked area plot
    ggplot2::geom_area(alpha = 0.8) +
    #### Convert y-axis scale to a percent
    ggplot2::scale_y_continuous(labels = scales::percent) +
    #### Labels
    ggplot2::labs(
      title = as.character(subset_items[i]),
      x= "Study Month", 
      y = "Frequency",
      fill = "Matched APS Intake Type"
      ) +
    #### Set colors
    ggplot2::scale_fill_brewer(palette=palette_order[i])
}

### Use Patchwork to wrap plots into a unified graphic
plot <- patchwork::wrap_plots(
  plots[1:length(names(subset_items))]
  ) + 
  patchwork::plot_annotation(
    title = "Matched APS Investigation Dispositions, by Month",
    subtitle = "Aggregated all matched investigations"
    ) + 
  patchwork::plot_layout(guides = 'collect', axes = 'collect') &
  ggplot2::theme(plot.title = ggplot2::element_text(size = 10))

## Save plot
ggplot2::ggsave(
  filename = paste0(
    plot_path,
    'f4-22-dispo-exact-all-month-per-result.png'
    ),
  plot = plot
  )

## Display plot
plot
```

##### Figure 4.23: Matched APS Investigations (Exact, "Best") by Screening Result, Per Month, All Screenings (#sec4-f23-dispo-exact-best-month-per-result)

We examined our DETECT-recorded intent to report per month, by result type. We calculated these frequencies from the single "best" matched investigation and by result type (positive or negative).

```{r}
#| label: sec4-f23-dispo-exact-best-month-per-result-calc
# Get Data
## Extract a temporary data frame of columns for reporting intent plots
reporting_df <- ms_records |>
      #### Reduce to SCREENINGS
      dplyr::mutate(dt_screened) |>
      #### Reduce to month, DETECT Tool Result, and Intake Reporter Type
      dplyr::select(month, dt_positive, aps_inv_exact_dispo_best) |>
      #### Fill missing values for disposition
      dplyr::mutate(
      #### Convert APS Disposition Types to label-set values
         aps_inv_exact_dispo_best = ifelse(
           is.na(aps_inv_exact_dispo_best), 
           "missing", 
           aps_inv_exact_dispo_best
           )
      )

## Get results for all screenings, positive screens, and negative screens
plot_dfs <- list(
  ### Get count and frequency for all screenings
  completed = get_freq_grouped(
    .df = reporting_df,
    .group_var = 'month',
    .item_list = list(
      aps_inv_exact_dispo_best = paste0(
        "APS Investigation Disposition (Exact, Best)"
        )
      ),
    .val_order = aps_dispo_labels[
      names(aps_dispo_labels) != 'completed'
      ]
    ),
  ### Get count and frequency for positive screenings
  positive = get_freq_grouped(
    .df = reporting_df |>
      #### Reduce to POSITIVE Screenings
      dplyr::filter(dt_positive),
    .group_var = 'month',
    .item_list = list(
      aps_inv_exact_dispo_best = paste0(
        "APS Investigation Disposition (Exact, Best)"
        )
      ),
    .val_order = aps_dispo_labels[
      names(aps_dispo_labels) != 'completed'
      ]
    ),
  ### Get count and frequency for negative screenings
  negative = get_freq_grouped(
    .df = reporting_df |>
      #### Reduce to NEGATIVE Screenings
      dplyr::filter(!dt_positive),
    .group_var = 'month',
    .item_list = list(
      aps_inv_exact_dispo_best = paste0(
        "APS Investigation Disposition (Exact, Best)"
        )
      ),
    .val_order = aps_dispo_labels[
      names(aps_dispo_labels) != 'completed'
      ]
    )
  )

## Smbest modification of data frames
for (i in seq(1,length(plot_dfs))){
  plot_dfs[[
    rlang::sym(names(plot_dfs)[i])
    ]] <- plot_dfs[[rlang::sym(names(plot_dfs)[i])]] |>
    ### Convert month to a numeric, for plot. Label Reporting Intent Values
    dplyr::mutate(
      month = as.numeric(month),
      response_label = factor(
        response,
        levels = names(aps_dispo_labels),
        labels = as.character(aps_dispo_labels)
      )
    )
}
```

We generated our plots.

```{r}
#| label: sec4-f23-dispo-exact-best-month-per-result-plot
# Plot 
## Create plots for each item in the section
### Create list to hold plots as they are generated
plots <- list()
subset_items <- screen_result_list[names(screen_result_list) != 'missing']
palette_order <- rep("Paired", length(subset_items))

### Create each plot and add to list
for (i in seq(1,length(names(subset_items)))){
  
  plots[[i]] <- ggplot2::ggplot(
    # Use the subset data frame
    data = plot_dfs[[rlang::sym(names(subset_items)[i])]] |>
      ### Remove "completed", as other values will add to this
      dplyr::filter(response != "completed") |>
      dplyr::select(month, response, per_total, response_label),
    ggplot2::aes(x = month, y = per_total, fill = response_label)
    ) +
    ### Stacked area plot
    ggplot2::geom_area(alpha = 0.8) +
    #### Convert y-axis scale to a percent
    ggplot2::scale_y_continuous(labels = scales::percent) +
    #### Labels
    ggplot2::labs(
      title = as.character(subset_items[i]),
      x= "Study Month", 
      y = "Frequency",
      fill = "Matched APS Intake Type"
      ) +
    #### Set colors
    ggplot2::scale_fill_brewer(palette=palette_order[i])
}

### Use Patchwork to wrap plots into a unified graphic
plot <- patchwork::wrap_plots(
  plots[1:length(names(subset_items))]
  ) + 
  patchwork::plot_annotation(
    title = "Matched APS Investigation Dispositions, by Month",
    subtitle = 'Single "Best" Matching Investigation'
    ) + 
  patchwork::plot_layout(guides = 'collect', axes = 'collect') &
  ggplot2::theme(plot.title = ggplot2::element_text(size = 10))

## Save plot
ggplot2::ggsave(
  filename = paste0(
    plot_path,
    'f4-23-dispo-exact-best-month-per-result.png'
    ),
  plot = plot
  )

## Display plot
plot
```

##### Figure 4.20: Matched APS Investigations (Broad, Aggregate) by Reporting Intent, Per Month, All Screenings (#sec4-f24-dispo-broad-all-month-per-intent)

We examined our DETECT-recorded intent to report per month, by reporting intent. We calculated these frequencies in aggregate (all screenings) and by reporting intent (intent or no intent).

```{r}
#| label: sec4-f24-dispo-broad-all-month-per-intent-calc
# Get Data
## Extract a temporary data frame of columns for reporting intent plots
reporting_df <- ms_records |>
      #### Reduce to SCREENINGS
      dplyr::mutate(dt_screened) |>
      #### Reduce to month, reporting intent, and Intake Reporter Type
      dplyr::select(month, dt_aps_reported, aps_inv_window_dispo) |>
      #### Fill missing values for disposition
      dplyr::mutate(
      #### Convert APS Intake Type categories to label-set values
         aps_inv_window_dispo = ifelse(
           is.na(aps_inv_window_dispo), "missing", aps_inv_window_dispo
           )
      )

## Get results for all screenings, positive screens, and negative screens
plot_dfs <- list(
  ### Get count and frequency for all screenings
  completed = get_freq_grouped(
    .df = reporting_df,
    .group_var = 'month',
    .item_list = list(
      aps_inv_window_dispo = paste0(
        "APS Investigation Disposition (Broad, Aggregate)"
        )
      ),
    .val_order = aps_dispo_labels[
      names(aps_dispo_labels) != 'completed'
      ]
    ),
  ### Get count and frequency for positive screenings
  intent = get_freq_grouped(
    .df = reporting_df |>
      #### Reduce to screenings WITH intent
      dplyr::filter(dt_aps_reported),
    .group_var = 'month',
    .item_list = list(
      aps_inv_window_dispo = paste0(
        "APS Investigation Disposition (Broad, Aggregate)"
        )
      ),
    .val_order = aps_dispo_labels[
      names(aps_dispo_labels) != 'completed'
      ]
    ),
  ### Get count and frequency for negative screenings
  no_intent = get_freq_grouped(
    .df = reporting_df |>
      #### Reduce to screenings WITHOUT intent
      dplyr::filter(!dt_aps_reported),
    .group_var = 'month',
    .item_list = list(
      aps_inv_window_dispo = paste0(
        "APS Investigation Disposition (Broad, Aggregate)"
        )
      ),
    .val_order = aps_dispo_labels[
      names(aps_dispo_labels) != 'completed'
      ]
    )
  )

## Small modification of data frames
for (i in seq(1,length(plot_dfs))){
  plot_dfs[[
    rlang::sym(names(plot_dfs)[i])
    ]] <- plot_dfs[[rlang::sym(names(plot_dfs)[i])]] |>
    ### Convert month to a numeric, for plot. Label Reporting Intent Values
    dplyr::mutate(
      month = as.numeric(month),
      response_label = factor(
        response,
        levels = names(aps_dispo_labels),
        labels = as.character(aps_dispo_labels)
      )
    )
}
```

We generated our plots.

```{r}
#| label: sec4-f24-dispo-broad-all-month-per-intent-plot
# Plot
## Create plots for each item in the section
### Create list to hold plots as they are generated
plots <- list()
subset_items <- report_intent_vals[names(report_intent_vals) != 'missing']
palette_order <- rep("Paired", length(subset_items))

### Create each plot and add to list
for (i in seq(1,length(names(subset_items)))){
  
  plots[[i]] <- ggplot2::ggplot(
    # Use the subset data frame
    data = plot_dfs[[rlang::sym(names(subset_items)[i])]] |>
      ### Remove "completed", as other values will add to this
      dplyr::filter(response != "completed") |>
      dplyr::select(month, response, per_total, response_label),
    ggplot2::aes(x = month, y = per_total, fill = response_label)
    ) +
    ### Stacked area plot
    ggplot2::geom_area(alpha = 0.8) +
    #### Convert y-axis scale to a percent
    ggplot2::scale_y_continuous(labels = scales::percent) +
    #### Labels
    ggplot2::labs(
      title = as.character(subset_items[i]),
      x= "Study Month", 
      y = "Frequency",
      fill = "Matched APS Intake Type"
      ) +
    #### Set colors
    ggplot2::scale_fill_brewer(palette=palette_order[i])
}

### Use Patchwork to wrap plots into a unified graphic
plot <- patchwork::wrap_plots(
  plots[1:length(names(subset_items))]
  ) + 
  patchwork::plot_annotation(
    title = "Matched APS Investigation Dispositions, by Month",
    subtitle = "Aggregated all matched investigations"
    ) + 
  patchwork::plot_layout(guides = 'collect', axes = 'collect') &
  ggplot2::theme(plot.title = ggplot2::element_text(size = 10))

## Save plot
ggplot2::ggsave(
  filename = paste0(
    plot_path,
    'f4-24-dispo-broad-all-month-per-intent.png'
    ),
  plot = plot
  )

## Display plot
plot
```

##### Figure 4.21: Matched APS Investigations (Broad, "Best") by Reporting Intent, Per Month, All Screenings (#sec4-f25-dispo-broad-best-month-per-intent)

We examined our DETECT-recorded intent to report per month, by reporting intent. We calculated these frequencies from the single "best" matched investigation and by reporting intent (intent or no intent).

```{r}
#| label: sec4-f25-dispo-broad-best-month-per-intent-calc
# Get Data
## Extract a temporary data frame of columns for reporting intent plots
reporting_df <- ms_records |>
      #### Reduce to SCREENINGS
      dplyr::mutate(dt_screened) |>
      #### Reduce to month, reporting intent, and Intake Reporter Type
      dplyr::select(month, dt_aps_reported, aps_inv_window_dispo_best) |>
      #### Fill missing values for disposition
      dplyr::mutate(
      #### Convert APS Disposition Types to label-set values
         aps_inv_window_dispo_best = ifelse(
           is.na(aps_inv_window_dispo_best), 
           "missing", 
           aps_inv_window_dispo_best
           )
      )

## Get results for all screenings, positive screens, and negative screens
plot_dfs <- list(
  ### Get count and frequency for all screenings
  completed = get_freq_grouped(
    .df = reporting_df,
    .group_var = 'month',
    .item_list = list(
      aps_inv_window_dispo_best = paste0(
        "APS Investigation Disposition (Broad, Best)"
        )
      ),
    .val_order = aps_dispo_labels[
      names(aps_dispo_labels) != 'completed'
      ]
    ),
  ### Get count and frequency for positive screenings
  intent = get_freq_grouped(
    .df = reporting_df |>
      #### Reduce to screenings WITH intent
      dplyr::filter(dt_aps_reported),
    .group_var = 'month',
    .item_list = list(
      aps_inv_window_dispo_best = paste0(
        "APS Investigation Disposition (Broad, Best)"
        )
      ),
    .val_order = aps_dispo_labels[
      names(aps_dispo_labels) != 'completed'
      ]
    ),
  ### Get count and frequency for negative screenings
  no_intent = get_freq_grouped(
    .df = reporting_df |>
      #### Reduce to screenings WITHOUT intent
      dplyr::filter(!dt_aps_reported),
    .group_var = 'month',
    .item_list = list(
      aps_inv_window_dispo_best = paste0(
        "APS Investigation Disposition (Broad, Best)"
        )
      ),
    .val_order = aps_dispo_labels[
      names(aps_dispo_labels) != 'completed'
      ]
    )
  )

## Smbest modification of data frames
for (i in seq(1,length(plot_dfs))){
  plot_dfs[[
    rlang::sym(names(plot_dfs)[i])
    ]] <- plot_dfs[[rlang::sym(names(plot_dfs)[i])]] |>
    ### Convert month to a numeric, for plot. Label Reporting Intent Values
    dplyr::mutate(
      month = as.numeric(month),
      response_label = factor(
        response,
        levels = names(aps_dispo_labels),
        labels = as.character(aps_dispo_labels)
      )
    )
}
```

We generated our plots.

```{r}
#| label: sec4-f25-dispo-broad-best-month-per-intent-plot
# Plot 
## Create plots for each item in the section
### Create list to hold plots as they are generated
plots <- list()
subset_items <- report_intent_vals[names(report_intent_vals) != 'missing']
palette_order <- rep("Paired", length(subset_items))

### Create each plot and add to list
for (i in seq(1,length(names(subset_items)))){
  
  plots[[i]] <- ggplot2::ggplot(
    # Use the subset data frame
    data = plot_dfs[[rlang::sym(names(subset_items)[i])]] |>
      ### Remove "completed", as other values will add to this
      dplyr::filter(response != "completed") |>
      dplyr::select(month, response, per_total, response_label),
    ggplot2::aes(x = month, y = per_total, fill = response_label)
    ) +
    ### Stacked area plot
    ggplot2::geom_area(alpha = 0.8) +
    #### Convert y-axis scale to a percent
    ggplot2::scale_y_continuous(labels = scales::percent) +
    #### Labels
    ggplot2::labs(
      title = as.character(subset_items[i]),
      x= "Study Month", 
      y = "Frequency",
      fill = "Matched APS Intake Type"
      ) +
    #### Set colors
    ggplot2::scale_fill_brewer(palette=palette_order[i])
}

### Use Patchwork to wrap plots into a unified graphic
plot <- patchwork::wrap_plots(
  plots[1:length(names(subset_items))]
  ) + 
  patchwork::plot_annotation(
    title = "Matched APS Investigation Dispositions, by Month",
    subtitle = 'Single "Best" Matching Investigation'
    ) + 
  patchwork::plot_layout(guides = 'collect', axes = 'collect') &
  ggplot2::theme(plot.title = ggplot2::element_text(size = 10))

## Save plot
ggplot2::ggsave(
  filename = paste0(
    plot_path,
    'f4-25-dispo-broad-best-month-per-intent.png'
    ),
  plot = plot
  )

## Display plot
plot
```

##### Figure 4.26: Matched APS Investigations (Exact, Aggregate) by Reporting Intent, Per Month, All Screenings (#sec4-f26-dispo-exact-all-month-per-intent)

We examined our DETECT-recorded intent to report per month, by reporting intent. We calculated these frequencies in aggregate (all screenings) and by reporting intent (intent or no intent).

```{r}
#| label: sec4-f26-dispo-exact-all-month-per-intent-calc
# Get Data
## Extract a temporary data frame of columns for reporting intent plots
reporting_df <- ms_records |>
      #### Reduce to SCREENINGS
      dplyr::mutate(dt_screened) |>
      #### Reduce to month, reporting intent, and Intake Reporter Type
      dplyr::select(month, dt_aps_reported, aps_inv_exact_dispo) |>
      #### Fill missing values for disposition
      dplyr::mutate(
      #### Convert APS Intake Type categories to label-set values
         aps_inv_exact_dispo = ifelse(
           is.na(aps_inv_exact_dispo), "missing", aps_inv_exact_dispo
           )
      )

## Get results for all screenings, positive screens, and negative screens
plot_dfs <- list(
  ### Get count and frequency for all screenings
  completed = get_freq_grouped(
    .df = reporting_df,
    .group_var = 'month',
    .item_list = list(
      aps_inv_exact_dispo = paste0(
        "APS Investigation Disposition (Exact, Aggregate)"
        )
      ),
    .val_order = aps_dispo_labels[
      names(aps_dispo_labels) != 'completed'
      ]
    ),
  ### Get count and frequency for positive screenings
  intent = get_freq_grouped(
    .df = reporting_df |>
      #### Reduce to screenings WITH intent
      dplyr::filter(dt_aps_reported),
    .group_var = 'month',
    .item_list = list(
      aps_inv_exact_dispo = paste0(
        "APS Investigation Disposition (Exact, Aggregate)"
        )
      ),
    .val_order = aps_dispo_labels[
      names(aps_dispo_labels) != 'completed'
      ]
    ),
  ### Get count and frequency for negative screenings
  no_intent = get_freq_grouped(
    .df = reporting_df |>
      #### Reduce to screenings WITHOUT intent
      dplyr::filter(!dt_aps_reported),
    .group_var = 'month',
    .item_list = list(
      aps_inv_exact_dispo = paste0(
        "APS Investigation Disposition (Exact, Aggregate)"
        )
      ),
    .val_order = aps_dispo_labels[
      names(aps_dispo_labels) != 'completed'
      ]
    )
  )

## Small modification of data frames
for (i in seq(1,length(plot_dfs))){
  plot_dfs[[
    rlang::sym(names(plot_dfs)[i])
    ]] <- plot_dfs[[rlang::sym(names(plot_dfs)[i])]] |>
    ### Convert month to a numeric, for plot. Label Reporting Intent Values
    dplyr::mutate(
      month = as.numeric(month),
      response_label = factor(
        response,
        levels = names(aps_dispo_labels),
        labels = as.character(aps_dispo_labels)
      )
    )
}
```

We generated our plots.

```{r}
#| label: sec4-f26-dispo-exact-all-month-per-intent-plot
# Plot
## Create plots for each item in the section
### Create list to hold plots as they are generated
plots <- list()
subset_items <- report_intent_vals[names(report_intent_vals) != 'missing']
palette_order <- rep("Paired", length(subset_items))

### Create each plot and add to list
for (i in seq(1,length(names(subset_items)))){
  
  plots[[i]] <- ggplot2::ggplot(
    # Use the subset data frame
    data = plot_dfs[[rlang::sym(names(subset_items)[i])]] |>
      ### Remove "completed", as other values will add to this
      dplyr::filter(response != "completed") |>
      dplyr::select(month, response, per_total, response_label),
    ggplot2::aes(x = month, y = per_total, fill = response_label)
    ) +
    ### Stacked area plot
    ggplot2::geom_area(alpha = 0.8) +
    #### Convert y-axis scale to a percent
    ggplot2::scale_y_continuous(labels = scales::percent) +
    #### Labels
    ggplot2::labs(
      title = as.character(subset_items[i]),
      x= "Study Month", 
      y = "Frequency",
      fill = "Matched APS Intake Type"
      ) +
    #### Set colors
    ggplot2::scale_fill_brewer(palette=palette_order[i])
}

### Use Patchwork to wrap plots into a unified graphic
plot <- patchwork::wrap_plots(
  plots[1:length(names(subset_items))]
  ) + 
  patchwork::plot_annotation(
    title = "Matched APS Investigation Dispositions, by Month",
    subtitle = "Aggregated all matched investigations"
    ) + 
  patchwork::plot_layout(guides = 'collect', axes = 'collect') &
  ggplot2::theme(plot.title = ggplot2::element_text(size = 10))

## Save plot
ggplot2::ggsave(
  filename = paste0(
    plot_path,
    'f4-26-dispo-exact-all-month-per-intent.png'
    ),
  plot = plot
  )

## Display plot
plot
```

##### Figure 4.27: Matched APS Investigations (Exact, "Best") by Reporting Intent, Per Month, All Screenings (#sec4-f27-dispo-exact-best-month-per-intent)

We examined our DETECT-recorded intent to report per month, by reporting intent. We calculated these frequencies from the single "best" matched investigation and by reporting intent (intent or no intent).

```{r}
#| label: sec4-f27-dispo-exact-best-month-per-intent-calc
# Get Data
## Extract a temporary data frame of columns for reporting intent plots
reporting_df <- ms_records |>
      #### Reduce to SCREENINGS
      dplyr::mutate(dt_screened) |>
      #### Reduce to month, reporting intent, and Intake Reporter Type
      dplyr::select(month, dt_aps_reported, aps_inv_exact_dispo_best) |>
      #### Fill missing values for disposition
      dplyr::mutate(
      #### Convert APS Disposition Types to label-set values
         aps_inv_exact_dispo_best = ifelse(
           is.na(aps_inv_exact_dispo_best), 
           "missing", 
           aps_inv_exact_dispo_best
           )
      )

## Get results for all screenings, positive screens, and negative screens
plot_dfs <- list(
  ### Get count and frequency for all screenings
  completed = get_freq_grouped(
    .df = reporting_df,
    .group_var = 'month',
    .item_list = list(
      aps_inv_exact_dispo_best = paste0(
        "APS Investigation Disposition (Exact, Best)"
        )
      ),
    .val_order = aps_dispo_labels[
      names(aps_dispo_labels) != 'completed'
      ]
    ),
  ### Get count and frequency for positive screenings
  intent = get_freq_grouped(
    .df = reporting_df |>
      #### Reduce to screenings WITH intent
      dplyr::filter(dt_aps_reported),
    .group_var = 'month',
    .item_list = list(
      aps_inv_exact_dispo_best = paste0(
        "APS Investigation Disposition (Exact, Best)"
        )
      ),
    .val_order = aps_dispo_labels[
      names(aps_dispo_labels) != 'completed'
      ]
    ),
  ### Get count and frequency for negative screenings
  no_intent = get_freq_grouped(
    .df = reporting_df |>
      #### Reduce to screenings WITHOUT intent
      dplyr::filter(!dt_aps_reported),
    .group_var = 'month',
    .item_list = list(
      aps_inv_exact_dispo_best = paste0(
        "APS Investigation Disposition (Exact, Best)"
        )
      ),
    .val_order = aps_dispo_labels[
      names(aps_dispo_labels) != 'completed'
      ]
    )
  )

## Smbest modification of data frames
for (i in seq(1,length(plot_dfs))){
  plot_dfs[[
    rlang::sym(names(plot_dfs)[i])
    ]] <- plot_dfs[[rlang::sym(names(plot_dfs)[i])]] |>
    ### Convert month to a numeric, for plot. Label Reporting Intent Values
    dplyr::mutate(
      month = as.numeric(month),
      response_label = factor(
        response,
        levels = names(aps_dispo_labels),
        labels = as.character(aps_dispo_labels)
      )
    )
}
```

We generated our plots.

```{r}
#| label: sec4-f27-dispo-exact-best-month-per-intent-plot
# Plot 
## Create plots for each item in the section
### Create list to hold plots as they are generated
plots <- list()
subset_items <- report_intent_vals[names(report_intent_vals) != 'missing']
palette_order <- rep("Paired", length(subset_items))

### Create each plot and add to list
for (i in seq(1,length(names(subset_items)))){
  
  plots[[i]] <- ggplot2::ggplot(
    # Use the subset data frame
    data = plot_dfs[[rlang::sym(names(subset_items)[i])]] |>
      ### Remove "completed", as other values will add to this
      dplyr::filter(response != "completed") |>
      dplyr::select(month, response, per_total, response_label),
    ggplot2::aes(x = month, y = per_total, fill = response_label)
    ) +
    ### Stacked area plot
    ggplot2::geom_area(alpha = 0.8) +
    #### Convert y-axis scale to a percent
    ggplot2::scale_y_continuous(labels = scales::percent) +
    #### Labels
    ggplot2::labs(
      title = as.character(subset_items[i]),
      x= "Study Month", 
      y = "Frequency",
      fill = "Matched APS Intake Type"
      ) +
    #### Set colors
    ggplot2::scale_fill_brewer(palette=palette_order[i])
}

### Use Patchwork to wrap plots into a unified graphic
plot <- patchwork::wrap_plots(
  plots[1:length(names(subset_items))]
  ) + 
  patchwork::plot_annotation(
    title = "Matched APS Investigation Dispositions, by Month",
    subtitle = 'Single "Best" Matching Investigation'
    ) + 
  patchwork::plot_layout(guides = 'collect', axes = 'collect') &
  ggplot2::theme(plot.title = ggplot2::element_text(size = 10))

## Save plot
ggplot2::ggsave(
  filename = paste0(
    plot_path,
    'f4-27-dispo-exact-best-month-per-intent.png'
    ),
  plot = plot
  )

## Display plot
plot
```

# 🧹 Clean up

```{r}
#| label: end-cleanup
rm(list=ls())
```