---
title: "Analyses Section 5: Consort Diagrams"
html:
  embed-resources: true
format: html
---

# ⭐️ Overview

## This File

This file creates consort diagrams for the APS-MedStar DETECT 5-year follow-up data, internally referred to as "Section 5: Consort Diagrams".

## MedStar Data Background

The MedStar records were originally recorded in Filemaker Pro. Processing of this data was extensive and across multiple data files. These files are documented in the [wiki](https://github.com/brad-cannell/detect_fu_interviews_public/wiki).

The primary files of interest for subject-level interest included participant demographic data in the `participant_import.rds` file [created in a separate Quarto file](https://github.com/brad-cannell/detect_fu_interviews_public/blob/main/data_management/data_01_participant_import.qmd), and the original within-set unique subject ID assignment in `participant_unique_ids.rds` file [created in a separate Quarto file](https://github.com/brad-cannell/detect_fu_interviews_public/blob/main/data_management/unique_person_identification/data_02_unique_person_detect_fu_data.qmd).

These files originally contained 92,160 observations of approximately 30 demographic variables. Refinement of unique subject ID assignments in subject-linkage to APS resulted in 41,955 values of `ms_id`.

## Internal Files

This document was created as part of the DETECT project, specifically the merger of APS and MedStar data for analysis using the full follow-up period data. Internal documents relating to these files, which contain PHI, are securely stored on the research group's SharePoint in the [5-year data manuscript directory](https://uthtmc.sharepoint.com/:f:/r/sites/SPHDETECT-RPC/Shared%20Documents/DETECT%20R01%202018/Manuscripts/Brianna%20Morri%20-%20APS%205%20year%20year%20update?csf=1&web=1&e=fhfOfL).

**Notes for analyses** start at the parent document["00_DETECT 5-year Analysis Notes.docx"](https://uthtmc.sharepoint.com/:w:/r/sites/SPHDETECT-RPC/Shared%20Documents/DETECT%20R01%202018/Manuscripts/Brianna%20Morri%20-%20APS%205%20year%20year%20update/tables/00_DETECT%205-Year%20Analysis%20Notes.docx?d=w09a61782c9ef4fe78780683996fdbd1b&csf=1&web=1&e=OWsgTv). Notes for this file are in ["section 5 - consort diagrams.docx"](https://uthtmc.sharepoint.com/:w:/r/sites/SPHDETECT-RPC/Shared%20Documents/DETECT%20R01%202018/Manuscripts/Brianna%20Morri%20-%20APS%205%20year%20year%20update/tables/section%205%20-%20consort%20diagrams.docx?d=w1ee2d8817d644999a9e6080c73027b46&csf=1&web=1&e=QDoyeY).

Notes for the MedStar data are located in the [notes_00_data_medstar.docx](https://uthtmc.sharepoint.com/:w:/r/sites/SPHDETECT-RPC/Shared%20Documents/DETECT%20R01%202018/02%20Shared%20Folders/DETECT%20Follow-up%20Interview%20Data%20Shared/data/notes_documents/notes_00_data_medstar.docx?d=w7367b418df5644fbb3ff5117908f27d9&csf=1&web=1&e=gueXsZ) file.

Please note: as these files contain PHI and proprietary information, they are not publicly available. Links are internal to the research team.

# 📦 Load Packages and Functions

## Library Imports

```{r}
#| label: imports-libraries
#| warning: FALSE
suppressPackageStartupMessages({
  library(tidyverse)
  library(here)
  library(consort)
  library(ggplot2)
  library(patchwork)
})
```

### Versioning

This file was created with:

-   R version 4.4.1 ("Race for Your Life").
-   tidyverse version 2.0.0, including all attached packages
-   here version 1.0.1
-   consort version 1.2.2
-   ggplot2 version 3.5.1
-   patchwork version 1.3.0

## Functions

```{r}
#| label: imports-functions
# Function to reduce code repetition in informative imports of data
source(here::here("r", "informative_df_import.R"))
```

# 📥 Load Data

## MedStar Data

We loaded our MedStar record-level data.

```{r}
#| label: load-ms-records
# Load MedStar Record Level Data
## Path to data
path <- here::here(
    "data", "cleaned_rds_files", "analysis", 
    "medstar_01_record-lvl.rds"
    )

## Load
informative_df_import(
    "ms_records", path, overwrite = T
  )

 # [PLACEHOLDER]
```

We loaded our MedStar subject-level data.

```{r}
#| label: load-ms-subjs
# Load MedStar Subject Level Data
## Path to data
path <- here::here(
    "data", "cleaned_rds_files", "analysis", 
    "medstar_02_subj-lvl.rds"
    )

## Load
informative_df_import(
    "ms_subjs", path, overwrite = T
  )

 # [PLACEHOLDER]
```

# Analyses

## Section 5: Consort Tables

We set the path to where we wished to save our plot files.

```{r}
#| label: set-plot-path
# Set path to directory to save plot image files
plot_path <- paste0(here::here('data', 'figs'), '/')
```

We created a version of our record-level data that was compatible with consort table generation with the consort package.

```{r}
#| label: sec5-record-consort-df
# Create record-level consort compatible data frame
record_df <- ms_records |>
  ## Isolate columns of interest, which flag the "stages"
  dplyr::select(
    id, ems_num, dt_screened, dt_positive,
    dt_aps_reported
    ) |>
  ## Convert to consort compatibe values
  dplyr::mutate(
    ### Unique subject ID for each record (combine ID, EMS_NUM into a var)
    resp_key = paste(id, ems_num, sep = "_"),
    ### If screened, have the record ID
    screenings = ifelse(dt_screened, resp_key, NA),
    ### Mark the reason why the record was excluded (not screened)
    record_exclusion = ifelse(
      is.na(screenings), 
      "No Recorded\nDETECT Screening", NA
      ),
    ### Mark "arm" of Screening Result
    screen_result = dplyr::case_when(
      dt_positive ~ "Positive Screening \n(1+ 'yes' response)",
      !dt_positive ~ "Negative Screening \n(no 'yes' responses)",
      TRUE ~ NA
    ),
    ### Mark "arm3" of Reporting Intent
    report_intent = dplyr::case_when(
      dt_aps_reported ~ "Intent to Report",
      !dt_aps_reported ~ "No Intent to Report",
      TRUE ~ NA
    ),
    ### PLACEHOLDERS
    mitt = screenings,
    present = screenings
  )

```

### Figure 5.1: Response Patterns: All Items (#sec5-f1-resps-reporting)

We plotted a consort table demonstrating the flow of records to DETECT-reported intent to report.

```{r}
#| label: sec5-f1-resps-reporting

## Create Consort Plot
consort_plot <- consort::consort_plot(
  data = record_df,
  orders = c(
   resp_key = "EMS Response Records",
   record_exclusion = "Excluded",
   screenings = "Screened with DETECT",
   ### Omit text to omit a parent-level box from displaying
   screen_result = "",
   report_intent = ""
             ),
  ### At least one side_box is required, or we could omit this
  side_box = c("record_exclusion"),
  allocation = c("screen_result", "report_intent"),
  labels = c(
    #### Level of "resp_key"
    "1" = "EMS Response", 
    #### Level of "screenings"
    "2" = "Screening with DETECT"
    ),
  ### Set to false to avoid it giving a bunch of 0 values
  kickoff_sidebox = F,
  ### Sets font size multiplier - default of 0.8 gives errors
  cex = 0.7
  )

## Add Title and Subtitle
consort_plot <- patchwork::wrap_elements(
  consort::build_grid(consort_plot)
  ) + 
  patchwork::plot_annotation(
    title = 'Consort Diagram',
    subtitle = 'Flow of MedStar Record Reporting Intent'
  )

## Save plot
ggplot2::ggsave(
  filename = paste0(
    plot_path,
    'f5-1-resps-reporting.png'
    ),
  plot = consort_plot
  )

## Display plot
consort_plot
```

# 🧹 Clean up

```{r}
#| label: end-cleanup
rm(list=ls())
```


# BOTTOM