---
title: "Analyses Section 2: DETECT-Tool Response Patterns"
html:
  embed-resources: true
format: html
---

# ⭐️ Overview

## This File

This file performs the initial explorations and analyses of DETECT-Tool Response Patterns within the MedStar 5-year follow-up data, internally referred to as "Section 2: DETECT-Tool Response Patterns".

## MedStar Data Background

The MedStar records were originally recorded in Filemaker Pro. Processing of this data was extensive and across multiple data files. These files are documented in the [wiki](https://github.com/brad-cannell/detect_fu_interviews_public/wiki).

The primary files of interest for subject-level interest included participant demographic data in the `participant_import.rds` file [created in a separate Quarto file](https://github.com/brad-cannell/detect_fu_interviews_public/blob/main/data_management/data_01_participant_import.qmd), and the original within-set unique subject ID assignment in `participant_unique_ids.rds` file [created in a separate Quarto file](https://github.com/brad-cannell/detect_fu_interviews_public/blob/main/data_management/unique_person_identification/data_02_unique_person_detect_fu_data.qmd).

These files originally contained 92,160 observations of approximately 30 demographic variables. Refinement of unique subject ID assignments in subject-linkage to APS resulted in 41,955 values of `ms_id`.

## Internal Files

This document was created as part of the DETECT project, specifically the merger of APS and MedStar data for analysis using the full follow-up period data. Internal documents relating to these files, which contain PHI, are securely stored on the research group's SharePoint in the [5-year data manuscript directory](https://uthtmc.sharepoint.com/:f:/r/sites/SPHDETECT-RPC/Shared%20Documents/DETECT%20R01%202018/Manuscripts/Brianna%20Morri%20-%20APS%205%20year%20year%20update?csf=1&web=1&e=fhfOfL).

**Notes for analyses** start at the parent document["00_DETECT 5-year Analysis Notes.docx"](https://uthtmc.sharepoint.com/:w:/r/sites/SPHDETECT-RPC/Shared%20Documents/DETECT%20R01%202018/Manuscripts/Brianna%20Morri%20-%20APS%205%20year%20year%20update/tables/00_DETECT%205-Year%20Analysis%20Notes.docx?d=w09a61782c9ef4fe78780683996fdbd1b&csf=1&web=1&e=OWsgTv). Notes for this file are in ["section 2 - detect item response patterns.docx"](https://uthtmc.sharepoint.com/:w:/r/sites/SPHDETECT-RPC/Shared%20Documents/DETECT%20R01%202018/Manuscripts/Brianna%20Morri%20-%20APS%205%20year%20year%20update/tables/section%202%20-%20detect%20item%20response%20patterns.docx?d=wb545e8832bdc4d02a56ad337921e743d&csf=1&web=1&e=v9I3lg).

Notes for the MedStar data are located in the [notes_00_data_medstar.docx](https://uthtmc.sharepoint.com/:w:/r/sites/SPHDETECT-RPC/Shared%20Documents/DETECT%20R01%202018/02%20Shared%20Folders/DETECT%20Follow-up%20Interview%20Data%20Shared/data/notes_documents/notes_00_data_medstar.docx?d=w7367b418df5644fbb3ff5117908f27d9&csf=1&web=1&e=gueXsZ) file.

Please note: as these files contain PHI and proprietary information, they are not publicly available. Links are internal to the research team.

# 📦 Load Packages and Functions

## Library Imports

```{r}
#| label: imports-libraries
#| warning: FALSE
suppressPackageStartupMessages({
  library(tidyverse)
  library(here)
  library(janitor, include.only = "clean_names")
})
```

### Versioning

This file was created with:

-   R version 4.4.1 ("Race for Your Life").
-   tidyverse version 2.0.0, including all attached packages
-   here version 1.0.1
-   janitor version 2.2.0
-   stats version 4.4.1

## Functions

```{r}
#| label: imports-functions
# Function to reduce code repetition in informative imports of data
source(here::here("r", "informative_df_import.R"))

## Function that performs 2-Category Chi-Square and Fisher Exact and produces
## a human-legible summary table
source(here::here("r", "get_chi_fisher.R"))

## Function that extracts response pattern tables from DETECT variables
source(here::here("r", "get_dt_resp_pattern.R"))

## Function that performs Chi-Square and Fisher's Exact on DETECT Response
## Patterns, by Item
source(here::here("r", "get_dt_rp_chi_fisher.R"))
```

# 📥 Load Data

## MedStar Data

We loaded our MedStar record-level data.

```{r}
#| label: load-ms-records
# Load MedStar Record Level Data
## Path to data
path <- here::here(
    "data", "cleaned_rds_files", "analysis", 
    "medstar_01_record-lvl.rds"
    )

## Load
informative_df_import(
    "ms_records", path, overwrite = T
  )

 # 2025-03-07: MS RECORDS data imported with 91,700 rows and 126 columns.
 # Data last modified on OneDrive: 2025-03-05 12:27:24 
```

We loaded our MedStar subject-level data.

```{r}
#| label: load-ms-subjs
# Load MedStar Subject Level Data
## Path to data
path <- here::here(
    "data", "cleaned_rds_files", "analysis", 
    "medstar_02_subj-lvl.rds"
    )

## Load
informative_df_import(
    "ms_subjs", path, overwrite = T
  )

 # 2025-03-07: MS SUBJS data imported with 41,612 rows and 75 columns.
 # Data last modified on OneDrive: 2025-03-05 12:27:24 
```

## Prior Study Response Patterns

We loaded the DETECT Tool response patterns from the Pilot study.

```{r}
#| label: load-prev-pat-pilot
# Load Pilot study response pattern data
## Path to data
path <- here::here(
    "data", "prev_data", "prev_dt_resp_pattern_pilot.csv"
    )

## Load
informative_df_import(
    "pat_pilot", path, overwrite = T,
    show_col_types = F
  )

## Filter to only items that also appear in the current study
pat_pilot <- pat_pilot |>
  dplyr::filter(!is.na(var_val))

## Add text-based formatted values for display in tables
pat_pilot <- pat_pilot |>
  ### Pivot to item_name, n, per format
  tidyr::pivot_longer(
    cols = dplyr::all_of(
      c(dplyr::starts_with("n_"), dplyr::starts_with("per_"))
      ), 
    cols_vary = "slowest",
    names_to = c(".value", "item_name"),
    names_pattern = "(.*?)_(.*)"
    ) |>
  ### Add text value for display
  dplyr::mutate(
    text = paste0(
      format(n, big.mark = ','),
      " (",
      stringr::str_trim(format(round(per*100, 2), nsmall = 2), side = 'both'), 
      "%)"
    )
  ) |> 
  ### Pivot back to DETECT item as row
  tidyr::pivot_wider(
    names_from = c('item_name'), 
    values_from = c('n', 'per', 'text'), 
    names_glue = "{.value}_{item_name}"
    )

### Set count of total responses
total_pilot <- 1247

 # 2025-03-07: PAT PILOT data imported with 26 rows and 12 columns.
 # Data last modified on OneDrive: 2025-03-06 14:34:28 
```

We loaded the DETECT Tool response patterns from the 1 Year Study interval.

```{r}
#| label: load-prev-pat-year
# Load 1-Year study response pattern data
## Path to data
path <- here::here(
    "data", "prev_data", "prev_dt_resp_pattern_1year.csv"
    )

## Load
informative_df_import(
    "pat_year", path, overwrite = T,
    show_col_types = F
  )

## Add text-based formatted values for display in tables
pat_year <- pat_year |>
  ### Pivot to item_name, n, per format
  tidyr::pivot_longer(
    cols = dplyr::all_of(
      c(dplyr::starts_with("n_"), dplyr::starts_with("per_"))
      ), 
    cols_vary = "slowest",
    names_to = c(".value", "item_name"),
    names_pattern = "(.*?)_(.*)"
    ) |>
  ### Add text value for display
  dplyr::mutate(
    text = paste0(
      format(n, big.mark = ','),
      " (",
      stringr::str_trim(format(round(per*100, 2), nsmall = 2), side = 'both'), 
      "%)"
    )
  ) |> 
  ### Pivot back to DETECT item as row
  tidyr::pivot_wider(
    names_from = c('item_name'), 
    values_from = c('n', 'per', 'text'), 
    names_glue = "{.value}_{item_name}"
    )

### Set count of total responses
total_year <- 24007

 # 2025-03-07: PAT YEAR data imported with 14 rows and 12 columns.
 # Data last modified on OneDrive: 2025-03-06 14:48:35 
```

# Analyses

We set the order we wanted to present our DETECT-Tool Items in our summary tables.

```{r}
#| label: set-value-orders
# Set order of values when presented in summary table functions
## DETECT Tool Variable Item Order
dt_item_list <- list(
  dt_env_odor = "Unusual odor (e.g., urine, feces)", 
  dt_env_hoard = paste0(
    "Inside of the home is in extreme disarray or there is hoarding"
    ), 
  dt_env_concern = paste0(
    "Living environment poses a health or safety concern (e.g., fire hazard,",
    " insect or rodent infestation, or urine or feces present)"
    ), 
  dt_pt_isolated = "Is the patient or older adult isolated in the home?", 
  dt_pt_hygiene = paste0(
    "Does the patient or older adult have poor personal hygiene",
    " (including soiled in urine or feces)?"
    ), 
  dt_pt_clothes = paste0(
    "Is the patient or older adult inadequately clothed or wearing",
    " dirty, torn, or soiled clothing?"
    ), 
  dt_pt_needs = paste0(
    "Does the patient or older adult have unmet needs for assistance",
    " with eating, toileting, transferring, dressing, or bathing?"
    ), 
  dt_pt_depress = paste0(
    "Does the patient or older adult appear depressed, anxious, or ",
    "emotionally distressed for reasons other than their immediate medical",
    " condition?"
    ), 
  dt_pt_med_hoard = paste0(
    "Does the patient or older adult appear to be hoarding or saving old",
    " medications?"), 
  dt_pt_med_diff = paste0(
    "Does the patient or older adult have difficulties taking their",
    " prescribed medications as directed?"
    ), 
  dt_cg_lack = paste0(
    "If caregiver is present, they appear to lack knowledge of the",
    " patient or older adult’s medical needs"
    ), 
  dt_cg_uneng = paste0(
    "If caregiver is present, they appear unengaged and inattentive in",
    " caring for the patient or older adult"
    ), 
  dt_cg_frust = paste0(
    "If caregiver is present, they appear frustrated, tired, angry, or ",
    "burdened by the patient or older adult"
    ), 
  dt_cg_anx = paste0(
    "If caregiver is present, they appear overly concerned ",
    "(e.g., anxious, hovering)")
  )
```

## Section 2: DETECT-Tool Response Patterns

### Response Pattern Tables

#### Table 2.1: Response Patterns: All Items (#sec2-t1-rp-all-resp)

We wished to examine response patterns of DETECT-Tool Items, across all screenings.

```{r}
#| label: sec2-t1-rp-all-resp-subset
# Take response-level subset for the following analyses
t_df <- ms_records |>
  ## Drop "Duplicate" flagged records
  dplyr::filter(!dup_drop) |>
  ## Subset to records with a screening
  dplyr::filter(dt_screened)

## Display number of records in subset
format(nrow(t_df), big.mark = ',')
```

We calculated our response patterns for all DETECT Items, across all screenings. We stored this internally as Table 2.1.

```{r}
#| label: sec2-t1-rp-all-resp-table
# Extract response pattern table
## Get table
resp_pattern <- get_dt_resp_pattern(t_df, dt_item_list)

## Display text portion of table
resp_pattern |>
  dplyr::select(dplyr::all_of(dplyr::starts_with('text_')))
```

#### Comparison to Pilot Study

We wished to examine differences in DETECT-Tool Item patterns with the Pilot study.

#### Table 2.2: Item Completion (#sec2-t2-rp-pilot-resp-comp)

We examined the difference in item completion patterns between our follow-up data and our Pilot study.  We stored this internally as Table 2.2.

```{r}
#| label: sec2-t2-rp-pilot-resp-comp-table
# Extract comparative response pattern table
## Pull text values of completion rates for both tables for display
dplyr::left_join(
  pat_pilot |>
    dplyr::select(text_completed, var_val) |>
    dplyr::rename_at("text_completed", ~"Pilot Completed"),
  resp_pattern |>
    dplyr::select(text_var_val, text_completed, var_val) |>
    dplyr::rename_at("text_completed", ~"Follow-up Completed"),
  by = 'var_val'
  ) |>
  dplyr::select(-var_val) |>
  dplyr::relocate(text_var_val)
```

We calculated Chi-square and Fisher exact tests for the completion rates of each item.

```{r}
#| label: sec2-t2-rp-pilot-resp-comp-stats
# Chi-Square and Fisher's Exact Test, Completion Comparison
## Calculate statistics
stats <- get_dt_rp_chi_fisher(
  ### Use total number of responses to calculate the number "not complete"
  resp_pattern |>
    dplyr::select(text_var_val, var_val, n_completed) |>
    dplyr::mutate(not_complete = nrow(t_df) - n_completed) |>
    dplyr::rename_at("n_completed", ~"complete"),
  pat_pilot |>
    dplyr::select(text_var_val, var_val, n_completed) |>
    dplyr::mutate(not_complete = total_pilot - n_completed) |>
    dplyr::rename_at("n_completed", ~"complete"),
  .target_vals = c("complete", "not_complete")
)

stats
```

##### Table 2.3: Item Response Patterns (#sec2-t3-rp-pilot-resp-pats)

We examined the difference in item response patterns between our follow-up data and our Pilot study.  We stored this internally as Table 2.3.

```{r}
#| label: sec2-t3-rp-pilot-resp-pats-table
# Extract comparative response pattern table
## Pull text values of completion rates for both tables for display
dplyr::left_join(
  pat_pilot |>
    dplyr::select(text_yes, text_no, text_uta, var_val) |>
    dplyr::rename_at(
      c("text_yes", "text_no", "text_uta"), 
      ~c("Pilot Yes", "Pilot No", "Pilot UTA")
      ),
  resp_pattern |>
    dplyr::select(text_var_val, text_yes, text_no, text_uta, var_val) |>
    dplyr::rename_at(
      c("text_yes", "text_no", "text_uta"), 
      ~c("Follow-Up Yes", "Follow-Up No", "Follow-Up UTA")
      ),
  by = 'var_val'
  ) |>
  dplyr::select(-var_val) |>
  dplyr::relocate(text_var_val) 
```

We calculated Chi-square and Fisher exact tests for the response patterns of each item.

```{r}
#| label: sec2-t3-rp-pilot-resp-pats-stats
# Chi-Square and Fisher's Exact Test, Response Comparison
## Calculate statistics
stats <- get_dt_rp_chi_fisher(
  resp_pattern |>
    dplyr::select(text_var_val, var_val, n_yes, n_no, n_uta) |>
    dplyr::rename_at(
      c("n_yes", "n_no", "n_uta"), 
      ~c("yes", "no", "uta")
      ),
  pat_pilot |>
    dplyr::select(text_var_val, var_val, n_yes, n_no, n_uta) |>
    dplyr::rename_at(
      c("n_yes", "n_no", "n_uta"), 
      ~c("yes", "no", "uta")
      ),
  .target_vals = c("yes", "no", "uta"),
  .omit_vals = c("uta")
)

stats
```

##### Table 2.4: "Only Yes" (#sec2-t4-rp-pilot-resp-onlyyes)

We examined the difference in the "only yes" item patterns between our follow-up data and our Pilot study. We stored this internally as Table 2.4.

```{r}
#| label: sec2-t4-rp-pilot-resp-onlyyes-table
# Extract comparative "only yes" pattern table
## Pull text values of completion rates for both tables for display
dplyr::left_join(
  pat_pilot |>
    dplyr::select(text_yes_only, var_val) |>
    dplyr::rename_at("text_yes_only", ~"Pilot Yes (Only)"),
  resp_pattern |>
    dplyr::select(text_var_val, text_yes_only, var_val) |>
    dplyr::rename_at("text_yes_only", ~"Follow-Up Yes (Only)"),
  by = 'var_val'
  ) |>
  dplyr::select(-var_val) |>
  dplyr::relocate(text_var_val)
```

We calculated Chi-square and Fisher exact tests for the "only yes" patterns of each item.

```{r}
#| label: sec2-t4-rp-pilot-resp-onlyyes-stats
# Chi-Square and Fisher's Exact Test, "Only Yes" comparison
## Calculate statistics
stats <- get_dt_rp_chi_fisher(
  resp_pattern |>
    dplyr::select(text_var_val, var_val, n_yes, n_yes_only) |>
    ### Calculate the number of "Yes" responses that were *not* the only yes
    dplyr::mutate(
      not_only_yes = n_yes - n_yes_only 
    ) |>
    dplyr::select(-n_yes) |>
    dplyr::rename_at(
      c("n_yes_only", "not_only_yes"), 
      ~c("only_yes", "not_only_yes")
      ),
  pat_pilot |>
    dplyr::select(text_var_val, var_val, n_yes, n_yes_only) |>
    dplyr::mutate(
      not_only_yes = n_yes - n_yes_only 
    ) |>
    dplyr::select(-n_yes) |>
    dplyr::rename_at(
      c("n_yes_only", "not_only_yes"), 
      ~c("only_yes", "not_only_yes")
      ),
  .target_vals = c("only_yes", "not_only_yes")
)

stats 
```

#### Comparison to 1-Year Study

We wished to examine differences in DETECT-Tool Item patterns with the 1-Year Study

###### Table 2.5: Item Completion (#sec2-t5-rp-year-resp-comp)

We examined the difference in item completion patterns between our follow-up data and our 1-Year study.  We stored this internally as Table 2.5.

```{r}
#| label: sec2-t5-rp-year-resp-comp-table
# Extract comparative response pattern table
## Pull text values of completion rates for both tables for display
dplyr::left_join(
  pat_year |>
    dplyr::select(text_completed, var_val) |>
    dplyr::rename_at("text_completed", ~"Year Completed"),
  resp_pattern |>
    dplyr::select(text_var_val, text_completed, var_val) |>
    dplyr::rename_at("text_completed", ~"Follow-up Completed"),
  by = 'var_val'
  ) |>
  dplyr::select(-var_val) |>
  dplyr::relocate(text_var_val)
```

We calculated Chi-square and Fisher exact tests for the completion rates of each item.

```{r}
#| label: sec2-t5-rp-year-resp-comp-stats
# Chi-Square and Fisher's Exact Test, Completion Comparison
## Calculate statistics
stats <- get_dt_rp_chi_fisher(
  ### Use total number of responses to calculate the number "not complete"
  resp_pattern |>
    dplyr::select(text_var_val, var_val, n_completed) |>
    dplyr::mutate(not_complete = nrow(t_df) - n_completed) |>
    dplyr::rename_at("n_completed", ~"complete"),
  pat_year |>
    dplyr::select(text_var_val, var_val, n_completed) |>
    dplyr::mutate(not_complete = total_year - n_completed) |>
    dplyr::rename_at("n_completed", ~"complete"),
  .target_vals = c("complete", "not_complete")
)

stats
```

###### Table 2.6: Item Response Patterns (#sec2-t6-rp-year-resp-pats)

We examined the difference in item response patterns between our follow-up data and our 1-Year study.  We stored this internally as Table 2.6.

```{r}
#| label: sec2-t6-rp-year-resp-pats-table
# Extract comparative response pattern table
## Pull text values of completion rates for both tables for display
dplyr::left_join(
  pat_year |>
    dplyr::select(text_yes, text_no, text_uta, var_val) |>
    dplyr::rename_at(
      c("text_yes", "text_no", "text_uta"), 
      ~c("Year Yes", "Year No", "Year UTA")
      ),
  resp_pattern |>
    dplyr::select(text_var_val, text_yes, text_no, text_uta, var_val) |>
    dplyr::rename_at(
      c("text_yes", "text_no", "text_uta"), 
      ~c("Follow-Up Yes", "Follow-Up No", "Follow-Up UTA")
      ),
  by = 'var_val'
  ) |>
  dplyr::select(-var_val) |>
  dplyr::relocate(text_var_val)
```

We calculated Chi-square and Fisher exact tests for the response patterns of each item.

```{r}
#| label: sec2-t6-rp-year-resp-pats-stats
# Chi-Square and Fisher's Exact Test, Response Comparison
## Calculate statistics
stats <- get_dt_rp_chi_fisher(
  resp_pattern |>
    dplyr::select(text_var_val, var_val, n_yes, n_no, n_uta) |>
    dplyr::rename_at(
      c("n_yes", "n_no", "n_uta"), 
      ~c("yes", "no", "uta")
      ),
  pat_year |>
    dplyr::select(text_var_val, var_val, n_yes, n_no, n_uta) |>
    dplyr::rename_at(
      c("n_yes", "n_no", "n_uta"), 
      ~c("yes", "no", "uta")
      ),
  .target_vals = c("yes", "no", "uta"),
  .omit_vals = c("uta")
)

stats
```

##### Table 2.7: "Only Yes" (#sec2-t7-rp-year-resp-onlyyes)

We examined the difference in the "only yes" item patterns between our follow-up data and our 1-Year study. We stored this internally as Table 2.7.

```{r}
#| label: sec2-t7-rp-year-resp-onlyyes-table
# Extract comparative "only yes" pattern table
## Pull text values of completion rates for both tables for display
dplyr::left_join(
  pat_year |>
    dplyr::select(text_yes_only, var_val) |>
    dplyr::rename_at("text_yes_only", ~"Year Yes (Only)"),
  resp_pattern |>
    dplyr::select(text_var_val, text_yes_only, var_val) |>
    dplyr::rename_at("text_yes_only", ~"Follow-Up Yes (Only)"),
  by = 'var_val'
  ) |>
  dplyr::select(-var_val) |>
  dplyr::relocate(text_var_val)
```

We calculated Chi-square and Fisher exact tests for the "only yes" patterns of each item.

```{r}
#| label: sec2-t7-rp-year-resp-onlyyes-stats
# Chi-Square and Fisher's Exact Test, "Only Yes" comparison
## Calculate statistics
stats <- get_dt_rp_chi_fisher(
  resp_pattern |>
    dplyr::select(text_var_val, var_val, n_yes, n_yes_only) |>
    ### Calculate the number of "Yes" responses that were *not* the only yes
    dplyr::mutate(
      not_only_yes = n_yes - n_yes_only 
    ) |>
    dplyr::select(-n_yes) |>
    dplyr::rename_at(
      c("n_yes_only", "not_only_yes"), 
      ~c("only_yes", "not_only_yes")
      ),
  pat_year |>
    dplyr::select(text_var_val, var_val, n_yes, n_yes_only) |>
    dplyr::mutate(
      not_only_yes = n_yes - n_yes_only 
    ) |>
    dplyr::select(-n_yes) |>
    dplyr::rename_at(
      c("n_yes_only", "not_only_yes"), 
      ~c("only_yes", "not_only_yes")
      ),
  .target_vals = c("only_yes", "not_only_yes")
)

stats
```

#### Table 2.8: Item Completion by Screening Result (#sec2-t8-rp-result-resp-comp)

We wished to examine differences in DETECT Tool Item completion between screenings with and without a DETECT-tool result, defined as one or more "yes" responses to DETECT Tool Items. We stored this internally as Table 2.8.

```{r}
#| label: sec2-rp-result-resp-subset
# Take response-level subsets for the following analyses
## Positive Screening
screen_pos <- ms_records |>
  ### Drop "Duplicate" flagged records
  dplyr::filter(!dup_drop) |>
  ### Subset to records with a screening
  dplyr::filter(dt_screened) |>
  ### Subset to positive screenings
  dplyr::filter(dt_positive)

## Negative Screening
screen_neg <- ms_records |>
  ## Drop "Duplicate" flagged records
  dplyr::filter(!dup_drop) |>
  ## Subset to records with a screening
  dplyr::filter(dt_screened) |>
  ### Subset to negative screenings
  dplyr::filter(!dt_positive)

## Get total number of records in each subset
screen_pos_total <- nrow(screen_pos)
screen_neg_total <- nrow(screen_neg)

## Get response patterns for each subset
screen_pos <- get_dt_resp_pattern(screen_pos, .dt_item_list = dt_item_list)
screen_neg <- get_dt_resp_pattern(screen_neg, .dt_item_list = dt_item_list)

## Display text-summary of the record counts
paste0(
  format(screen_pos_total, big.mark = ','), " (",
  stringr::str_trim(
    format(
      round(screen_pos_total*100 / (screen_pos_total + screen_neg_total), 2),
      nsmall = 2
      ), 
    side = 'both'
    ),
  "%) records with positive screening. ",
  format(screen_neg_total, big.mark = ','), " (",
  stringr::str_trim(
    format(
      round(screen_neg_total*100 / (screen_pos_total + screen_neg_total), 2),
      nsmall = 2
      ), 
    side = 'both'
    ),"%) records with negative screening. "
)
```

We examined the difference in item completion patterns between screenings with and without a DETECT-tool recorded intent to report.

```{r}
#| label: sec2-t8-rp-result-resp-comp-table
# Extract comparative response pattern table
## Pull text values of completion rates for both tables for display
dplyr::left_join(
  screen_pos |>
    dplyr::select(text_completed, var_val) |>
    dplyr::rename_at("text_completed", ~"Positive Screen Completed"),
  screen_neg |>
    dplyr::select(text_var_val, text_completed, var_val) |>
    dplyr::rename_at("text_completed", ~"Negative Screen Completed"),
  by = 'var_val'
  ) |>
  dplyr::select(-var_val) |>
  dplyr::relocate(text_var_val)
```

We calculated Chi-square and Fisher exact tests for the completion rates of each item.

```{r}
#| label: sec2-t8-rp-result-resp-comp-stats
# Chi-Square and Fisher's Exact Test, Completion Comparison
## Calculate statistics
stats <- get_dt_rp_chi_fisher(
  ### Use total responses in subset to calculate the number "not complete"
  screen_pos |>
    dplyr::select(text_var_val, var_val, n_completed) |>
    dplyr::mutate(not_complete = screen_pos_total - n_completed) |>
    dplyr::rename_at("n_completed", ~"complete"),
  screen_neg |>
    dplyr::select(text_var_val, var_val, n_completed) |>
    dplyr::mutate(not_complete = screen_neg_total - n_completed) |>
    dplyr::rename_at("n_completed", ~"complete"),
  .target_vals = c("complete", "not_complete")
)

stats
```

#### Comparison by Intent to Report, All Screenings

We wished to examine differences in DETECT-Tool Item patterns between screenings with and without a DETECT-tool recorded intent to report, for all screenings.

```{r}
#| label: sec2-rp-all-intent-resp-subset
# Take response-level subsets for the following analyses
## Positive Intent
intent_pos <- ms_records |>
  ### Drop "Duplicate" flagged records
  dplyr::filter(!dup_drop) |>
  ### Subset to records with a screening
  dplyr::filter(dt_screened) |>
  ### Subset to only screenings with a recorded intent to report
  dplyr::filter(dt_aps_reported)

## Negative Intent
intent_neg <- ms_records |>
  ## Drop "Duplicate" flagged records
  dplyr::filter(!dup_drop) |>
  ## Subset to records with a screening
  dplyr::filter(dt_screened) |>
  ## Subset to only screenings with a recorded intent to report
  dplyr::filter(!dt_aps_reported)

## Get total number of records in each subset
intent_pos_total <- nrow(intent_pos)
intent_neg_total <- nrow(intent_neg)

## Get response patterns for each subset
intent_pos <- get_dt_resp_pattern(intent_pos, .dt_item_list = dt_item_list)
intent_neg <- get_dt_resp_pattern(intent_neg, .dt_item_list = dt_item_list)

## Display text-summary of the record counts
paste0(
  format(intent_pos_total, big.mark = ','), " (",
  stringr::str_trim(
    format(
      round(intent_pos_total*100 / (intent_pos_total + intent_neg_total), 2),
      nsmall = 2
      ), 
    side = 'both'
    ),
  "%) records with positive intent. ",
  format(intent_neg_total, big.mark = ','), " (",
  stringr::str_trim(
    format(
      round(intent_neg_total*100 / (intent_pos_total + intent_neg_total), 2),
      nsmall = 2
      ), 
    side = 'both'
    ),"%) records with negative intent. "
)
```

##### Table 2.9: Item Completion (#sec2-t2-rp-all-intent-resp-comp)

We examined the difference in item completion patterns between screenings with and without a DETECT-tool recorded intent to report. We stored this internally as Table 2.9.

```{r}
#| label: sec2-t9-rp-all-intent-resp-comp-table
# Extract comparative response pattern table
## Pull text values of completion rates for both tables for display
dplyr::left_join(
  intent_pos |>
    dplyr::select(text_completed, var_val) |>
    dplyr::rename_at("text_completed", ~"Positive Intent Completed"),
  intent_neg |>
    dplyr::select(text_var_val, text_completed, var_val) |>
    dplyr::rename_at("text_completed", ~"Negative Intent Completed"),
  by = 'var_val'
  ) |>
  dplyr::select(-var_val) |>
  dplyr::relocate(text_var_val)
```

We calculated Chi-square and Fisher exact tests for the completion rates of each item.

```{r}
#| label: sec2-t9-rp-all-intent-resp-comp-stats
# Chi-Square and Fisher's Exact Test, Completion Comparison
## Calculate statistics
stats <- get_dt_rp_chi_fisher(
  ### Use total responses in subset to calculate the number "not complete"
  intent_pos |>
    dplyr::select(text_var_val, var_val, n_completed) |>
    dplyr::mutate(not_complete = intent_pos_total - n_completed) |>
    dplyr::rename_at("n_completed", ~"complete"),
  intent_neg |>
    dplyr::select(text_var_val, var_val, n_completed) |>
    dplyr::mutate(not_complete = intent_neg_total - n_completed) |>
    dplyr::rename_at("n_completed", ~"complete"),
  .target_vals = c("complete", "not_complete")
)

stats 
```

##### Table 2.10: Item Response Patterns (#sec2-t10-rp-all-intent-resp-pats)

We examined the difference in item response patterns between screenings with and without a DETECT-tool recorded intent to report. We stored this internally as Table 2.10.

```{r}
#| label: sec2-t10-rp-all-intent-resp-pats-table
# Extract comparative response pattern table
## Pull text values of completion rates for both tables for display
dplyr::left_join(
  intent_pos |>
    dplyr::select(text_yes, text_no, text_uta, var_val) |>
    dplyr::rename_at(
      c("text_yes", "text_no", "text_uta"), 
      ~c("Positive Intent Yes", "Positive Intent No", "Positive Intent UTA")
      ),
  intent_neg |>
    dplyr::select(text_var_val, text_yes, text_no, text_uta, var_val) |>
    dplyr::rename_at(
      c("text_yes", "text_no", "text_uta"), 
      ~c("Negative Intent Yes", "Negative Intent No", "Negative Intent UTA")
      ),
  by = 'var_val'
  ) |>
  dplyr::select(-var_val) |>
  dplyr::relocate(text_var_val)
```

We calculated Chi-square and Fisher exact tests for the response patterns of each item.

```{r}
#| label: sec2-t10-rp-all-intent-resp-pats-stats
# Chi-Square and Fisher's Exact Test, Response Comparison
## Calculate statistics
stats <- get_dt_rp_chi_fisher(
  intent_pos |>
    dplyr::select(text_var_val, var_val, n_yes, n_no, n_uta) |>
    dplyr::rename_at(
      c("n_yes", "n_no", "n_uta"), 
      ~c("yes", "no", "uta")
      ),
  intent_neg |>
    dplyr::select(text_var_val, var_val, n_yes, n_no, n_uta) |>
    dplyr::rename_at(
      c("n_yes", "n_no", "n_uta"), 
      ~c("yes", "no", "uta")
      ),
  .target_vals = c("yes", "no", "uta"),
  .omit_vals = c("uta")
)

stats
```

##### Table 2.11: "Only Yes" (#sec2-t11-rp-all-intent-resp-onlyyes)

We examined the difference in the "only yes" item patterns between screenings with and without a DETECT-tool recorded intent to report. We stored this internally as Table 2.11.

```{r}
#| label: sec2-t11-rp-all-intent-resp-onlyyes-table
# Extract comparative "only yes" pattern table
## Pull text values of completion rates for both tables for display
dplyr::left_join(
  intent_pos |>
    dplyr::select(text_yes_only, var_val) |>
    dplyr::rename_at("text_yes_only", ~"Positive Intent Yes (Only)"),
  intent_neg |>
    dplyr::select(text_var_val, text_yes_only, var_val) |>
    dplyr::rename_at("text_yes_only", ~"Negative Intent Yes (Only)"),
  by = 'var_val'
  ) |>
  dplyr::select(-var_val) |>
  dplyr::relocate(text_var_val)
```

We calculated Chi-square and Fisher exact tests for the "only yes" patterns of each item.

```{r}
#| label: sec2-t11-rp-all-intent-resp-onlyyes-stats
# Chi-Square and Fisher's Exact Test, "Only Yes" comparison
## Calculate statistics
stats <- get_dt_rp_chi_fisher(
  intent_neg |>
    dplyr::select(text_var_val, var_val, n_yes, n_yes_only) |>
    ### Calculate the number of "Yes" responses that were *not* the only yes
    dplyr::mutate(
      not_only_yes = n_yes - n_yes_only 
    ) |>
    dplyr::select(-n_yes) |>
    dplyr::rename_at(
      c("n_yes_only", "not_only_yes"), 
      ~c("only_yes", "not_only_yes")
      ),
  intent_pos |>
    dplyr::select(text_var_val, var_val, n_yes, n_yes_only) |>
    dplyr::mutate(
      not_only_yes = n_yes - n_yes_only 
    ) |>
    dplyr::select(-n_yes) |>
    dplyr::rename_at(
      c("n_yes_only", "not_only_yes"), 
      ~c("only_yes", "not_only_yes")
      ),
  .target_vals = c("only_yes", "not_only_yes")
)

stats
```

#### Comparison by Intent to Report, Positive Screenings

We wished to examine differences in DETECT-Tool Item patterns between screenings with and without a DETECT-tool recorded intent to report, for positive screenings.

```{r}
#| label: sec2-rp-posscr-intent-resp-subset
# Take response-level subsets for the following analyses
## Positive Intent
intent_pos <- ms_records |>
  ### Drop "Duplicate" flagged records
  dplyr::filter(!dup_drop) |>
  ### Subset to records with a screening
  dplyr::filter(dt_screened) |>
  ### Subset to positive screenings
  dplyr::filter(dt_positive) |>
  ### Subset to only screenings with a recorded intent to report
  dplyr::filter(dt_aps_reported)

## Negative Intent
intent_neg <- ms_records |>
  ## Drop "Duplicate" flagged records
  dplyr::filter(!dup_drop) |>
  ## Subset to records with a screening
  dplyr::filter(dt_screened) |>
  ### Subset to positive screenings
  dplyr::filter(dt_positive) |>
  ## Subset to only screenings with a recorded intent to report
  dplyr::filter(!dt_aps_reported)

## Get total number of records in each subset
intent_pos_total <- nrow(intent_pos)
intent_neg_total <- nrow(intent_neg)

## Get response patterns for each subset
intent_pos <- get_dt_resp_pattern(intent_pos, .dt_item_list = dt_item_list)
intent_neg <- get_dt_resp_pattern(intent_neg, .dt_item_list = dt_item_list)

## Display text-summary of the record counts
paste0(
  format(intent_pos_total, big.mark = ','), " (",
  stringr::str_trim(
    format(
      round(intent_pos_total*100 / (intent_pos_total + intent_neg_total), 2),
      nsmall = 2
      ), 
    side = 'both'
    ),
  "%) records with positive intent. ",
  format(intent_neg_total, big.mark = ','), " (",
  stringr::str_trim(
    format(
      round(intent_neg_total*100 / (intent_pos_total + intent_neg_total), 2),
      nsmall = 2
      ), 
    side = 'both'
    ),"%) records with negative intent. "
)
```

##### Table 2.12: Item Completion (#sec2-t12-rp-posscr-intent-resp-comp)

We examined the difference in item completion patterns between screenings with and without a DETECT-tool recorded intent to report. We stored this internally as Table 2.12.

```{r}
#| label: sec2-t12-rp-posscr-intent-resp-comp-table
# Extract comparative response pattern table
## Pull text values of completion rates for both tables for display
dplyr::left_join(
  intent_pos |>
    dplyr::select(text_completed, var_val) |>
    dplyr::rename_at("text_completed", ~"Positive Intent Completed"),
  intent_neg |>
    dplyr::select(text_var_val, text_completed, var_val) |>
    dplyr::rename_at("text_completed", ~"Negative Intent Completed"),
  by = 'var_val'
  ) |>
  dplyr::select(-var_val) |>
  dplyr::relocate(text_var_val)
```

We calculated Chi-square and Fisher exact tests for the completion rates of each item.

```{r}
#| label: sec2-t12-rp-posscr-intent-resp-comp-stats
# Chi-Square and Fisher's Exact Test, Completion Comparison
## Calculate statistics
stats <- get_dt_rp_chi_fisher(
  ### Use total responses in subset to calculate the number "not complete"
  intent_pos |>
    dplyr::select(text_var_val, var_val, n_completed) |>
    dplyr::mutate(not_complete = intent_pos_total - n_completed) |>
    dplyr::rename_at("n_completed", ~"complete"),
  intent_neg |>
    dplyr::select(text_var_val, var_val, n_completed) |>
    dplyr::mutate(not_complete = intent_neg_total - n_completed) |>
    dplyr::rename_at("n_completed", ~"complete"),
  .target_vals = c("complete", "not_complete")
)

stats
```

##### Table 2.13: Item Response Patterns (#sec2-t13-rp-posscr-intent-resp-pats)

We examined the difference in item response patterns between screenings with and without a DETECT-tool recorded intent to report. We stored this internally as Table 2.13.

```{r}
#| label: sec2-t13-rp-posscr-intent-resp-pats-table
# Extract comparative response pattern table
## Pull text values of completion rates for both tables for display
dplyr::left_join(
  intent_pos |>
    dplyr::select(text_yes, text_no, text_uta, var_val) |>
    dplyr::rename_at(
      c("text_yes", "text_no", "text_uta"), 
      ~c("Positive Intent Yes", "Positive Intent No", "Positive Intent UTA")
      ),
  intent_neg |>
    dplyr::select(text_var_val, text_yes, text_no, text_uta, var_val) |>
    dplyr::rename_at(
      c("text_yes", "text_no", "text_uta"), 
      ~c("Negative Intent Yes", "Negative Intent No", "Negative Intent UTA")
      ),
  by = 'var_val'
  ) |>
  dplyr::select(-var_val) |>
  dplyr::relocate(text_var_val)
```

We calculated Chi-square and Fisher exact tests for the response patterns of each item.

```{r}
#| label: sec2-t13-rp-posscr-intent-resp-pats-stats
# Chi-Square and Fisher's Exact Test, Response Comparison
## Calculate statistics
stats <- get_dt_rp_chi_fisher(
  intent_pos |>
    dplyr::select(text_var_val, var_val, n_yes, n_no, n_uta) |>
    dplyr::rename_at(
      c("n_yes", "n_no", "n_uta"), 
      ~c("yes", "no", "uta")
      ),
  intent_neg |>
    dplyr::select(text_var_val, var_val, n_yes, n_no, n_uta) |>
    dplyr::rename_at(
      c("n_yes", "n_no", "n_uta"), 
      ~c("yes", "no", "uta")
      ),
  .target_vals = c("yes", "no", "uta"),
  .omit_vals = c("uta")
)

stats 
```

##### Table 2.14: "Only Yes" (#sec2-t14-rp-posscr-intent-resp-onlyyes)

We examined the difference in the "only yes" item patterns between screenings with and without a DETECT-tool recorded intent to report. We stored this internally as Table 2.14.

```{r}
#| label: sec2-t14-rp-posscr-intent-resp-onlyyes-table
# Extract comparative "only yes" pattern table
## Pull text values of completion rates for both tables for display
dplyr::left_join(
  intent_pos |>
    dplyr::select(text_yes_only, var_val) |>
    dplyr::rename_at("text_yes_only", ~"Positive Intent Yes (Only)"),
  intent_neg |>
    dplyr::select(text_var_val, text_yes_only, var_val) |>
    dplyr::rename_at("text_yes_only", ~"Negative Intent Yes (Only)"),
  by = 'var_val'
  ) |>
  dplyr::select(-var_val) |>
  dplyr::relocate(text_var_val)
```

We calculated Chi-square and Fisher exact tests for the "only yes" patterns of each item.

```{r}
#| label: sec2-t14-rp-posscr-intent-resp-onlyyes-stats
# Chi-Square and Fisher's Exact Test, "Only Yes" comparison
## Calculate statistics
stats <- get_dt_rp_chi_fisher(
  intent_neg |>
    dplyr::select(text_var_val, var_val, n_yes, n_yes_only) |>
    ### Calculate the number of "Yes" responses that were *not* the only yes
    dplyr::mutate(
      not_only_yes = n_yes - n_yes_only 
    ) |>
    dplyr::select(-n_yes) |>
    dplyr::rename_at(
      c("n_yes_only", "not_only_yes"), 
      ~c("only_yes", "not_only_yes")
      ),
  intent_pos |>
    dplyr::select(text_var_val, var_val, n_yes, n_yes_only) |>
    dplyr::mutate(
      not_only_yes = n_yes - n_yes_only 
    ) |>
    dplyr::select(-n_yes) |>
    dplyr::rename_at(
      c("n_yes_only", "not_only_yes"), 
      ~c("only_yes", "not_only_yes")
      ),
  .target_vals = c("only_yes", "not_only_yes")
)

stats
```


#### Comparison by Intent to Report, Negative Screenings

We wished to examine differences in DETECT-Tool Item patterns between screenings with and without a DETECT-tool recorded intent to report, for negative screenings.

```{r}
#| label: sec2-rp-negscr-intent-resp-subset
# Take response-level subsets for the following analyses
## Positive Intent
intent_pos <- ms_records |>
  ### Drop "Duplicate" flagged records
  dplyr::filter(!dup_drop) |>
  ### Subset to records with a screening
  dplyr::filter(dt_screened) |>
  ### Subset to negative screenings
  dplyr::filter(!dt_positive) |>
  ### Subset to only screenings with a recorded intent to report
  dplyr::filter(dt_aps_reported)

## Negative Intent
intent_neg <- ms_records |>
  ## Drop "Duplicate" flagged records
  dplyr::filter(!dup_drop) |>
  ## Subset to records with a screening
  dplyr::filter(dt_screened) |>
  ### Subset to negative screenings
  dplyr::filter(!dt_positive) |>
  ## Subset to only screenings with a recorded intent to report
  dplyr::filter(!dt_aps_reported)

## Get total number of records in each subset
intent_pos_total <- nrow(intent_pos)
intent_neg_total <- nrow(intent_neg)

## Get response patterns for each subset
intent_pos <- get_dt_resp_pattern(intent_pos, .dt_item_list = dt_item_list)
intent_neg <- get_dt_resp_pattern(intent_neg, .dt_item_list = dt_item_list)

## Display text-summary of the record counts
paste0(
  format(intent_pos_total, big.mark = ','), " (",
  stringr::str_trim(
    format(
      round(intent_pos_total*100 / (intent_pos_total + intent_neg_total), 2),
      nsmall = 2
      ), 
    side = 'both'
    ),
  "%) records with positive intent. ",
  format(intent_neg_total, big.mark = ','), " (",
  stringr::str_trim(
    format(
      round(intent_neg_total*100 / (intent_pos_total + intent_neg_total), 2),
      nsmall = 2
      ), 
    side = 'both'
    ),"%) records with negative intent. "
)
```

##### Table 2.15: Item Completion (#sec2-t15-rp-negscr-intent-resp-comp)

We examined the difference in item completion patterns between screenings with and without a DETECT-tool recorded intent to report. We stored this internally as Table 2.15.

```{r}
#| label: sec2-t15-rp-negscr-intent-resp-comp-table
# Extract comparative response pattern table
## Pull text values of completion rates for both tables for display
dplyr::left_join(
  intent_pos |>
    dplyr::select(text_completed, var_val) |>
    dplyr::rename_at("text_completed", ~"Positive Intent Completed"),
  intent_neg |>
    dplyr::select(text_var_val, text_completed, var_val) |>
    dplyr::rename_at("text_completed", ~"Negative Intent Completed"),
  by = 'var_val'
  ) |>
  dplyr::select(-var_val) |>
  dplyr::relocate(text_var_val)
```

We calculated Chi-square and Fisher exact tests for the completion rates of each item.

```{r}
#| label: sec2-t15-rp-negscr-intent-resp-comp-stats
# Chi-Square and Fisher's Exact Test, Completion Comparison
## Calculate statistics
stats <- get_dt_rp_chi_fisher(
  ### Use total responses in subset to calculate the number "not complete"
  intent_pos |>
    dplyr::select(text_var_val, var_val, n_completed) |>
    dplyr::mutate(not_complete = intent_pos_total - n_completed) |>
    dplyr::rename_at("n_completed", ~"complete"),
  intent_neg |>
    dplyr::select(text_var_val, var_val, n_completed) |>
    dplyr::mutate(not_complete = intent_neg_total - n_completed) |>
    dplyr::rename_at("n_completed", ~"complete"),
  .target_vals = c("complete", "not_complete")
)

stats
```

##### Table 2.16: Item Response Patterns (#sec2-t16-rp-negscr-intent-resp-pats)

We examined the difference in item response patterns between screenings with and without a DETECT-tool recorded intent to report. We stored this internally as Table 2.16.

```{r}
#| label: sec2-t16-rp-negscr-intent-resp-pats-table
# Extract comparative response pattern table
## Pull text values of completion rates for both tables for display
dplyr::left_join(
  intent_pos |>
    dplyr::select(text_yes, text_no, text_uta, var_val) |>
    dplyr::rename_at(
      c("text_yes", "text_no", "text_uta"), 
      ~c("Positive Intent Yes", "Positive Intent No", "Positive Intent UTA")
      ),
  intent_neg |>
    dplyr::select(text_var_val, text_yes, text_no, text_uta, var_val) |>
    dplyr::rename_at(
      c("text_yes", "text_no", "text_uta"), 
      ~c("Negative Intent Yes", "Negative Intent No", "Negative Intent UTA")
      ),
  by = 'var_val'
  ) |>
  dplyr::select(-var_val) |>
  dplyr::relocate(text_var_val) |>
  ### Omit "Yes" columns, as these are negative screenings (no yes by def.)
  dplyr::select(-dplyr::all_of(dplyr::contains('yes', ignore.case = T)))
```

We calculated Chi-square and Fisher exact tests for the response patterns of each item.

```{r}
#| label: sec2-t16-rp-negscr-intent-resp-pats-stats
# Chi-Square and Fisher's Exact Test, Response Comparison
## Calculate statistics
stats <- get_dt_rp_chi_fisher(
  intent_pos |>
    dplyr::select(text_var_val, var_val, n_yes, n_no, n_uta) |>
    dplyr::rename_at(
      c("n_no", "n_uta"), 
      ~c("no", "uta")
      ),
  intent_neg |>
    dplyr::select(text_var_val, var_val, n_yes, n_no, n_uta) |>
    dplyr::rename_at(
      c("n_no", "n_uta"), 
      ~c("no", "uta")
      ),
  .target_vals = c("no", "uta")
)

stats
```

# 🧹 Clean up

```{r}
#| label: end-cleanup
rm(list=ls())
```
