---
title: "Analyses Section 3: Agreement"
html:
  embed-resources: true
format: html
---

# ⭐️ Overview

## This File

This file performs the initial explorations and analyses of agreement between outcome variables within the MedStar 5-year follow-up data, internally referred to as "Section 3: Agreement".

## MedStar Data Background

The MedStar records were originally recorded in Filemaker Pro. Processing of this data was extensive and across multiple data files. These files are documented in the [wiki](https://github.com/brad-cannell/detect_fu_interviews_public/wiki).

The primary files of interest for subject-level interest included participant demographic data in the `participant_import.rds` file [created in a separate Quarto file](https://github.com/brad-cannell/detect_fu_interviews_public/blob/main/data_management/data_01_participant_import.qmd), and the original within-set unique subject ID assignment in `participant_unique_ids.rds` file [created in a separate Quarto file](https://github.com/brad-cannell/detect_fu_interviews_public/blob/main/data_management/unique_person_identification/data_02_unique_person_detect_fu_data.qmd).

These files originally contained 92,160 observations of approximately 30 demographic variables. Refinement of unique subject ID assignments in subject-linkage to APS resulted in 41,955 values of `ms_id`.

## Internal Files

This document was created as part of the DETECT project, specifically the merger of APS and MedStar data for analysis using the full follow-up period data. Internal documents relating to these files, which contain PHI, are securely stored on the research group's SharePoint in the [5-year data manuscript directory](https://uthtmc.sharepoint.com/:f:/r/sites/SPHDETECT-RPC/Shared%20Documents/DETECT%20R01%202018/Manuscripts/Brianna%20Morri%20-%20APS%205%20year%20year%20update?csf=1&web=1&e=fhfOfL).

**Notes for analyses** start at the parent document["00_DETECT 5-year Analysis Notes.docx"](https://uthtmc.sharepoint.com/:w:/r/sites/SPHDETECT-RPC/Shared%20Documents/DETECT%20R01%202018/Manuscripts/Brianna%20Morri%20-%20APS%205%20year%20year%20update/tables/00_DETECT%205-Year%20Analysis%20Notes.docx?d=w09a61782c9ef4fe78780683996fdbd1b&csf=1&web=1&e=OWsgTv). Notes for this file are in ["section 3 - agreement tables.docx"](https://uthtmc.sharepoint.com/:w:/r/sites/SPHDETECT-RPC/Shared%20Documents/DETECT%20R01%202018/Manuscripts/Brianna%20Morri%20-%20APS%205%20year%20year%20update/tables/section%203%20-%20agreement%20tables.docx?d=we977750fe9144ee5bec9e25b7ab980ad&csf=1&web=1&e=tv5x5B).

Notes for the MedStar data are located in the [notes_00_data_medstar.docx](https://uthtmc.sharepoint.com/:w:/r/sites/SPHDETECT-RPC/Shared%20Documents/DETECT%20R01%202018/02%20Shared%20Folders/DETECT%20Follow-up%20Interview%20Data%20Shared/data/notes_documents/notes_00_data_medstar.docx?d=w7367b418df5644fbb3ff5117908f27d9&csf=1&web=1&e=gueXsZ) file.

Please note: as these files contain PHI and proprietary information, they are not publicly available. Links are internal to the research team.

# 📦 Load Packages and Functions

## Library Imports

```{r}
#| label: imports-libraries
#| warning: FALSE
suppressPackageStartupMessages({
  library(tidyverse)
  library(here)
  library(irr)
  library(janitor, include.only = "clean_names")
})
```

### Versioning

This file was created with:

-   R version 4.4.1 ("Race for Your Life").
-   tidyverse version 2.0.0, including all attached packages
-   here version 1.0.1
-   janitor version 2.2.0
-   stats version 4.4.1
-   irr version 0.84.1

## Functions

```{r}
#| label: imports-functions
# Function to reduce code repetition in informative imports of data
source(here::here("r", "informative_df_import.R"))

# Function that creates a modified version of table output, allowing
# simplified manual review of unique values in a given column or set of
# columns
source(here::here("r", "get_unique_value_summary.R"))

# Function that creates a text-based, human-legible summary statistic table
# for a numeric column
source(here::here("r", "get_cont_summary.R"))
# Function that wraps "get_cont_summary()" to process multiple groups at once.
source(here::here("r", "get_group_cont_summary.R"))

# Function that creates a text-based, human-legible summary statistic table
# for a categorical column
source(here::here("r", "get_cat_summary.R"))
# Function that wraps "get_cat_summary()" to process multiple groups at once.
source(here::here("r", "get_group_cat_summary.R"))

## Function that performs 2-Category Chi-Square and Fisher Exact and produces
## a human-legible summary table
source(here::here("r", "get_chi_fisher.R"))

## Function that performs 2-category T-Test and Wilcox Rank-Sum test and 
## produces a human-legible summary table
source(here::here("r", "get_twos_num_stats.R"))

## Function that extracts response pattern tables from DETECT variables
source(here::here("r", "get_dt_resp_pattern.R"))

## Function that performs Chi-Square and Fisher's Exact on DETECT Response
## Patterns, by Item
source(here::here("r", "get_dt_rp_chi_fisher.R"))

## Function that gets a formatted, human-legible 2x2 agreement summary table
source(here::here("r", "get_twox_logical_table.R"))

## Function that gets a formatted, human-legible table summarizing the results
## of agreement statistical tests (Chi-Square, McNemar, Correlation Coefficent,
## Kappa)
source(here::here("r", "get_agreement_stats_table.R"))
```

# 📥 Load Data

## MedStar Data

We loaded our MedStar record-level data.

```{r}
#| label: load-ms-records
# Load MedStar Record Level Data
## Path to data
path <- here::here(
    "data", "cleaned_rds_files", "analysis", 
    "medstar_01_record-lvl.rds"
    )

## Load
informative_df_import(
    "ms_records", path, overwrite = T
  )

## Drop potentially duplicated responses
ms_records <- ms_records |>
  dplyr::filter(!dup_drop)

# [Placeholder]
```

We loaded our MedStar subject-level data.

```{r}
#| label: load-ms-records
# Load MedStar Subject Level Data
## Path to data
path <- here::here(
    "data", "cleaned_rds_files", "analysis", 
    "medstar_02_subj-lvl.rds"
    )

## Load
informative_df_import(
    "ms_subjs", path, overwrite = T
  )

# [Placeholder]
```

# Analyses

We set the order and labels for values in categorical variables. [PLACEHOLDER: Delete if not needed]

```{r}
#| label: set-value-orders
# Set order and labels for values in categorical variables that may be used
# in plots

## Sex value order
sex_val_list = list(
    male = 'Male', female = 'Female', uta = 'Unable to Assess', 
    missing = 'Missing (NA)'
    )

## Race value order
race_val_list = list(
  white = "White", black = "Black or African American", asian = "Asian", 
  nhpi = "Native Hawaiian or Other Pacific Islander", 
  aian = "American Indian or Alaska Native", 
  mena = "Middle Eastern or North African", 
  other = "Other Race", multiracial = "Multiracial", missing = "Missing (NA)"
  )

## Hispanic Ethnicity value order
hispanic_val_list = list(
  hispanic = 'Hispanic or Latino', nonhispanic = 'Not Hispanic or Latino', 
  missing = 'Missing (NA)'
  )

## DETECT Tool Variable Item Order
dt_item_list <- list(
  dt_env_odor = "Unusual odor (e.g., urine, feces)", 
  dt_env_hoard = paste0(
    "Inside of the home is in extreme disarray or there is hoarding"
    ), 
  dt_env_concern = paste0(
    "Living environment poses a health or safety concern (e.g., fire hazard,",
    " insect or rodent infestation, or urine or feces present)"
    ), 
  dt_pt_isolated = "Is the patient or older adult isolated in the home?", 
  dt_pt_hygiene = paste0(
    "Does the patient or older adult have poor personal hygiene",
    " (including soiled in urine or feces)?"
    ), 
  dt_pt_clothes = paste0(
    "Is the patient or older adult inadequately clothed or wearing",
    " dirty, torn, or soiled clothing?"
    ), 
  dt_pt_needs = paste0(
    "Does the patient or older adult have unmet needs for assistance",
    " with eating, toileting, transferring, dressing, or bathing?"
    ), 
  dt_pt_depress = paste0(
    "Does the patient or older adult appear depressed, anxious, or ",
    "emotionally distressed for reasons other than their immediate medical",
    " condition?"
    ), 
  dt_pt_med_hoard = paste0(
    "Does the patient or older adult appear to be hoarding or saving old",
    " medications?"), 
  dt_pt_med_diff = paste0(
    "Does the patient or older adult have difficulties taking their",
    " prescribed medications as directed?"
    ), 
  dt_cg_lack = paste0(
    "If caregiver is present, they appear to lack knowledge of the",
    " patient or older adult’s medical needs"
    ), 
  dt_cg_uneng = paste0(
    "If caregiver is present, they appear unengaged and inattentive in",
    " caring for the patient or older adult"
    ), 
  dt_cg_frust = paste0(
    "If caregiver is present, they appear frustrated, tired, angry, or ",
    "burdened by the patient or older adult"
    ), 
  dt_cg_anx = paste0(
    "If caregiver is present, they appear overly concerned ",
    "(e.g., anxious, hovering)")
  )
```

## Section 3: Agreement

### All Screenings

#### Table 1: Agreement of Reporting Intent to DETECT Result (sec3-t1-scr-reslt-intent-all)

We were interested in the agreement between the DETECT Tool's recorded intent to report to the screening result. (Did medic's typically intend to report if a screening was positive, and not if it was negative?) A positive screening was defined as at least one "yes" response, regardless of items selected. We checked this for all screenings.

First, we checked to see if there were any records where one target value was present, but the other was not.

```{r}
#| label: sec3-t1-scr-reslt-intent-all-na-check
# Check if there are any rows where there is a value for one of the 
# variables of interest, but not the other
ms_records |>
  dplyr::filter((is.na(dt_positive) != is.na(dt_aps_reported))) |>
  nrow() == 0
```

We then defined our target variables, and created our summary of counts in the agreement table.

```{r}
#| label: sec3-t1-scr-reslt-intent-summ
# Agreement Table
## Define Variables
### "First Column" or "Top-Down" Value
var_a <- "dt_positive"
var_a_labs <- list(t = "Intent to Report", f = "No Intent to Report")
### "Column-wise", "Across", or "Left-Right" Value
var_b <- "dt_aps_reported"
var_b_labs <- list(t = "Positive Screening", f = "Negative Screening")
### Reduce to desired columns, and modify values to match desired labels
set_df <- ms_records |>
    dplyr::mutate(
      dplyr::across(c(dt_positive, dt_aps_reported), 
                    ~dplyr::case_when(
                      .x ~ 't',
                      !.x ~ 'f',
                      is.na(.x) ~ NA
                    ))
      )

## Get & display summary count table
get_twox_logical_table(
  .var_a = var_a,
  .var_b = var_b,
  .var_a_labs = var_a_labs,
  .var_b_labs = var_b_labs,
  .df = set_df
  )
```

We then calculated our agreement statistics.

```{r}
#| label: sec3-t1-scr-reslt-intent-stats
# Statistics Table
get_agreement_stats_table(
  .var_a = var_a,
  .var_b = var_b,
  .var_a_labs = var_a_labs,
  .var_b_labs = var_b_labs,
  .df = set_df,
  .corr_methods = c("pearson", "kendall", "spearman"), 
  .kappa_methods = c("cohen", "fleiss", "light"), 
  .n_decimal = 4
  )
```

# 🧹 Clean up

```{r}
#| label: end-cleanup
rm(list=ls())
```