---
title: "RPPR Demos"
date: 2025-07-25
format: html
---

# Libraries

```{r}
library(dplyr)
library(stringr)
library(here)
library(readr)
```

# Import Data

```{r}
emr_path <- here::here("data", "cleaned_rds_files", "participant_import.rds")
emr_df <- readRDS(emr_path)
emr_df <- emr_df |> 
  dplyr::select(x_primary_key, medstar_id, medstar_internal_id, dob, age, race, sex) |>
  dplyr::rename(
    age_emr = age,
    race_emr = race,
    gender_emr = sex
  )
```

```{r}
consent_path <- here::here("data", "cleaned_rds_files", "consent_import.rds")
consent_df <- readRDS(consent_path)
consent_df <- consent_df |> 
  dplyr::select(x_primary_key, medstar_id, x_record_status) |>
  dplyr::rename(consent_status = x_record_status)
```

```{r}
demo_path <- here::here("data", "cleaned_rds_files", "sociodemographic_information_import.rds")
demo_df <- readRDS(demo_path)
demo_df <- demo_df |>
  dplyr::select(x_primary_key, medstar_id, sode_age, sode_age_years, sode_hispanic, sode_race, sogi_identity) |>
  dplyr::rename(
    age_sode = sode_age,
    age_sode_years = sode_age_years,
    hispanic_sode = sode_hispanic,
    race_sode = sode_race,
    gender_sode = sogi_identity
  )
```

```{r}
linkage_path <- here::here("data", "cleaned_rds_files", "record_linkage", "maps", "02_medstar-keys-to-id_ms.rds")
linkage_df <- readRDS(linkage_path)
linkage_df <- linkage_df
```

# Process

## Join

```{r}
joined_df <- dplyr::left_join(
  emr_df,
  linkage_df,
  by = c("x_primary_key", "medstar_internal_id")
  ) |>
  dplyr::relocate("id", "id_ms") |>
  dplyr::left_join(
    consent_df,
    by = "medstar_id"
  ) |>
    dplyr::left_join(
      demo_df,
      by = "medstar_id"
    )
```

## All Events (One Row per Interview)

Manual review performed to verify transformations against codebooks and RPPR standards.

```{r}
all_records <- joined_df |>
  dplyr::filter(consent_status == "Consent received/Participating") |>
  dplyr::select(id, medstar_id, race_sode, hispanic_sode, gender_sode, age_sode_years) |>
  dplyr::mutate(
    Race = dplyr::case_when(
      race_sode == "Black or African American" ~ "Black",
      race_sode == "White" ~ "White",
      race_sode == "American Indian or Alaskan Native" ~ "American Indian",
      race_sode == "Asian" ~ "Asian",
      race_sode == "Native Hawaiian or Other Pacific Islander" ~ "Hawaiian",
      race_sode %in% c("Other", "Don't know", "Refused") | is.na(race_sode) ~ 
        "Unknown",
      TRUE ~ "More than one race"
    ),
    Ethnicity = dplyr::case_when(
      hispanic_sode == 0 ~ "Not Hispanic or Latino",
      hispanic_sode == 1 ~ "Hispanic or Latino",
      TRUE ~ "Unknown"
    ),
    Sex = dplyr::case_when(
      gender_sode == 1 ~ "Male",
      gender_sode == 2 ~ "Female",
      TRUE ~ "Unknown"
    ),
    Age.Unit = dplyr::case_when(
      age_sode_years >= 90 ~ "Ninety Plus",
      !is.na(age_sode_years) & age_sode_years < 90 ~ "Years",
      is.na(age_sode_years) ~ "Unknown"
    ),
    Age = dplyr::case_when(
      !is.na(age_sode_years) & age_sode_years < 90 ~ 
        as.integer(age_sode_years),
      TRUE ~ NA_integer_
    )
  ) |>
  dplyr::select(id, medstar_id, Race, Ethnicity, Sex, Age.Unit, Age)
```

## Subject Level (One Row Per Subject)

Manual review was done to check for any discrepancies. Race was assigned based on the most frequent option in multiple records. Lowest age value (first interview) was taken. 

```{r}
single_subj_records <- all_records |> 
  dplyr::select(-medstar_id) |> 
  dplyr::distinct() |> 
  dplyr::mutate(dplyr::across(
    c(Race, Ethnicity, Sex, Age.Unit), 
    ~dplyr::if_else(.x == "Unknown", NA, .x)
    )) |>
  dplyr::group_by(id) |>
  tidyr::fill(c(Race, Ethnicity, Sex, Age.Unit), .direction = "downup") |>
  dplyr::mutate(
    Race = dplyr::case_when(
      id %in% c(1406, 9748, 16068) ~ "White",
      id %in% c(25834, 25891, 36732, 37878) ~ "More than one race",
      TRUE ~ Race
      )
    ) |>
  dplyr::group_by(id) |>
  dplyr::mutate(
    Age = if (all(is.na(Age))) NA_integer_ else min(Age, na.rm = TRUE),
    Age.Unit = ifelse(
      Age.Unit %in% c("Ninety Plus", "Unknown") & !is.na(Age), 
      "Years", 
      Age.Unit
      )
  ) |>
  dplyr::ungroup() |>
  dplyr::distinct() |>
  dplyr::mutate(dplyr::across(
    c(Race, Ethnicity, Sex, Age.Unit), 
    ~dplyr::if_else(is.na(.x), "Unknown", .x)
    )) |>
  dplyr::relocate(Race, Ethnicity, Sex, Age, Age.Unit) |>
  dplyr::select(-id)

single_subj_records
```

# Save Data

```{r}
save_path <- here::here("data", "detect_r01_fu_interview_subj_demos_all_events.csv")
readr::write_csv(all_records, save_path)
```

```{r}
save_path <- here::here("data", "detect_r01_fu_interview_subj_demos_single_row_per_subj.csv")
readr::write_csv(single_subj_records, save_path)
```

